### 2021-03-12 documentation/paper.Rmd
Initial commit

---
title: |
  | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(PollBasePro::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback. We owe particular thanks to Chris Hanretty, Y, and Z. We would also like to extend a special thanks to all of the volunteers who have given their time to maintain such a comprehensive list of British opinion polling data on Wikipedia.}
author: |
  | Jack Bailey\thanks{Research Associate, Department of Politics, University of Manchester, UK. If you have any comments or questions, feel free to contact me either by email (\href{mailto:jack.bailey@manchester.ac.uk}{jack.bailey@manchester.ac.uk}) or on Twitter (\href{https://www.twitter.com/PoliSciJack}{@PoliSciJack}).}, Mark Pack\thanks{President, The Liberal Democrats, UK}, & Luke Mansillo\thanks{PhD Candidate, Department of Government \& International Relations, University of Sydney, Australia}
date: |
  | \small This version compiled `r stringr::str_remove(format(Sys.time(), '%d %B %Y'), "^0")` using PollBasePro `r paste0("v", packageVersion("PollBasePro"))`
abstract: |
  | Political scientists often use public opinion polls to test their theories. Yet these data present some difficulties. First, they are noisy. Second, they occur at irregular intervals. Third, they measure both public preferences and pollsters' survey design choices. We introduce a new dataset, PollBasePro, that accounts for these issues. It includes voting intention estimates for each of Britain's three largest parties on each day between the 1955 general election and the present. Given that the dataset covers `r format(nrow(PollBasePro::pollbasepro), big.mark = ",")` days in total, it is more comprehensive than any existing time series of public opinion in Britain. As a result, we expect PollBasePro to be an important resource for students of British politics in the years to come.
  |
  | \textbf{\textsf{Keywords:}} Opinion polls; public opinion; British politics; Bayesian methods.
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/rmd-preamble.tex
    number_sections: false
    fig_caption: true
---

<!-- Latex setup -->

\doublespacing

```{=tex}
\thispagestyle{empty}
\clearpage
```
\pagebreak

\setcounter{page}{1}

```{r setup, include = F}

# Load packages

library(PollBasePro)
library(kableExtra)
library(tidyverse)
library(lubridate)
library(tidybayes)
library(patchwork)
library(jbmisc)
library(brms)
library(here)

# Load PollBasePro data

data("pollbase")
data("pollbasepro")
load(here("R", "sysdata.rda"))

# Create long-format PollBasePro data

pbp_long <- 
  pollbasepro %>% 
  pivot_longer(
    cols = c(-date, -election, -govt, -week, -month, -quarter, -year, -con_ldr, -lab_ldr, -lib_ldr),
    names_to = c("party", ".value"),
    names_sep = "_",
  ) %>%
  mutate(
    party =
      case_when(
        party == "con" ~ "Conservative Party",
        party == "lab" ~ "Labour Party",
        party == "lib" ~ "Liberals (Various Forms)"
      ) %>% 
      factor(
        levels = 
          c("Conservative Party",
            "Labour Party",
            "Liberals (Various Forms)"
          )
      )
  )

# Load timeline data

timeline <-
  readRDS(here("inst", "extdata", "timeline.rds")) %>%
  select(
    date = polldate,
    elecdate,
    country,
    party = partyid,
    vote = poll_
  ) %>%
  filter(country == "United Kingdom") %>% 
  na.omit()

# Load deaths data

death_dta <- 
read_csv(here("inst", "extdata", "data_2021-Mar-06-deaths.csv")) %>%
      select(
        date,
        deaths = newDeaths28DaysByDeathDate
      )

# Compute time in lead

lead <- 
  pbp_long %>%
  mutate(party = str_remove(party, " .*|s .*")) %>% 
  group_by(date) %>%
  summarise(
    max = party[which.max(est)],
    .groups = "drop"
  ) %>% 
  group_by(max) %>% 
  summarise(
    Leader = paste0(format(round((n()/nrow(pollbasepro))*100, 1), nsmall = 1), "\\% of days"),
    .groups = "drop"
  ) %>% 
  rename(Party = max)

# Define party colours

pty_cols <-
  c(
    "Conservative Party" = "#0087dc",
    "Labour Party" = "#d50000",
    "Liberals (Various Forms)" = "#fdbb30"
  )

# Load coronavirus example model

death_mod <- readRDS(here("models", paste0("death_mod_", packageVersion("PollBasePro"), ".rds")))

# Load correlation models

cor_all <- readRDS(here("models", paste0("cor_all_", packageVersion("PollBasePro"), ".rds")))
cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("PollBasePro"), ".rds")))
cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("PollBasePro"), ".rds")))
cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("PollBasePro"), ".rds")))

# Tell knitr to use Cairo PDF when rendering plots so that it uses nice fonts

knitr::opts_chunk$set(dev = "cairo_pdf")

```

# Introduction

Beleaguered politicians often remark that the "only poll that matters is the election itself". Like much that politicians say, this is not true. Though elections decide who governs, public opinion polls are important too: they let us track how popular parties are in the time between elections. Polling is especially important in Britain. Unlike in many countries, British governments have some control over scheduling elections. As a result, the governing party's standing is often one of the only factors that decides when it will hold an election [@smith2003].

Since the advent of universal suffrage in 1928, Britain has held only 24 general elections. This is not a large sample. Political scientists have, thus, turned to public opinion polls to test their theories. Still, these data present some difficulties. Three issues are most serious. First, that polling data are noisy and may be prone to bias. Second, that they occur at irregular time intervals. And, third, that they measure both real changes in the electorate's preferences *and* the design choices of the companies that run them.

In this paper, we introduce a new dataset---*PollBasePro*---that overcomes these issues. It includes `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of aggregate voting intention for each of Britain's three largest parties on each day between `r format(min(pollbasepro$date), "%d %B %Y")` and `r format(max(pollbasepro$date), "%d %B %Y")`. Covering `r format(nrow(pollbasepro), big.mark = ",")` days in total, PollBasePro permits a degree of specificity and flexibility beyond that of any existing time series data. In the sections that follow, we elaborate on the dataset. First, we describe the methods and the data that we use to derive our estimates. Next, we consider what PollBasePro reveals about British politics since 1955 and show how to use it to test hypotheses. We then provide some initial conclusions and remark on how we might develop PollBasePro in the future.

# Data, Estimation, and Validation

Polling data have long informed political science research. For example, @goodhart1970 used Gallup and NOP polls to show that changes in the economy affect support for the incumbent party, thereby launching economic voting research. Though plentiful, these data come with some problems. As we mention above, three are most important.

First, polling data are noisy. This is an unavoidable consequence of sampling methodologies. As we cannot poll every person in a country, polls cannot provide exact estimates of public opinion. Rather, they represent draws from a distribution of *possible* estimates of public opinion. This noise is a type of measurement error, and failing to account for it can have important consequences. Where we use polls as an outcome, it reduces our statistical power. Where we use them as a predictor, it pulls real and existing effects towards zero.

Second, polling data occur at irregular intervals. What's more, they can cover any period of time from a single day to several weeks. Political scientists often assume that these figures measure public opinion on the poll's last day in the field. Of course, this is almost never true. It can also be a problem when major events occur partway through the data collection process. This is a major practical problem: polls can be difficult to match to other time series.

Third, polls do not only measure changes in aggregate preferences. They also include systematic biases due to the design choices of the companies that run them. In the past, these biases have been so large that they have cast doubt on the efficacy of the polling industry. At the 2015 UK general election, most polls suggested that Labour had a good chance of becoming the largest party. But, on the night, the Conservatives won a small majority instead [@sturgis2018; @prosser2018c, @mellon2017a]. These biases were even more serious at the 2019 Australian Federal Election. As in the British case, Labor had a healthy lead in the polls. Yet, again, the Coalition beat them by around 8 percentage points [@mansillo2020].

Our intention is simple: to produce voting intention estimates that account for these issues. To do so, we adapt the method in @jackman2005. Jackman's model has estimates for a given party start and end at known results from any given pair of elections. It then treats the party's level of support as a random walk between these two points. On any given day, the party's support depends on its support the day before, pollster-specific "house" effects, and random shocks. Jackman and Mansillo [-@mansillo2020; -@jackman2016] have used the model to track voting intention in Australia and @louwerse2016 have used it to estimate aggregate voting intention in Ireland. The full model specification is as follows^[Note that we provide a more in-depth explanation of how the model works and the steps that we have taken to produce our estimates in the user guide that accompanies the data.]:

\begin{align*}
Poll_{i} &\sim \mathrm{Normal}(\mu_{i}, \sqrt{\sigma^2 + S_{i}^2}) \srlab{Likelihood function} \\
\mu_{i} &= \alpha_{Day[i]} + \delta_{Pollster[i]} \srlab{Measurement model on $\mu$} \\
\alpha_{t} &= \alpha_{t-1} + \tau \omega_{t-1} \text{ for } t \text{ in } 2, ..., T-1 \srlab{Dynamic model on $\alpha_{t}$} \\
\alpha_{T} &\sim \mathrm{Normal}(\alpha_{T-1}, \tau) \srlab{Adaptive prior on $\alpha_{T}$} \\
\delta_{j} &\sim \mathrm{Normal}(0, 0.1) \text{ for } j \text{ in } 1, ..., J \srlab{Prior on house effects, $\delta$} \\
\omega_{t} &\sim \mathrm{Normal}(0, 0.1) \text{ for } t \text{ in } 1, ..., T-1 \srlab{Prior on random shocks, $\omega$} \\
\tau &\sim \mathrm{Normal}(0, 0.05)^{+} \srlab{Positive prior on scale of innovations, $\tau$} \\
\sigma &\sim \mathrm{Exponential}(20) \srlab{Prior on residual error, $\sigma$} \\
\end{align*}

Two data sources inform our estimates. The first is the PollBase dataset of historic British voting intention polls [@pack2021]. The second is data compiled by volunteers on Wikipedia [for an example of this data, see @wikipedia2021]. Both are comprehensive, high-quality, and track British public opinion over the past several decades.

The PollBase data come from a range of sources. This includes books published after each general election, polling almanacs, data shared amongst academics and pollsters, contemporary media reports, and figures from polling company websites. The data since the 1983 general election are complete, baring any individual errors. Likewise, data are complete for every general election campaign before 1979. The coverage between elections is more comprehensive for some pollsters than others^[We encourage any readers who might know of polls missing from the PollBase dataset to contact its author via his website (https://www.markpack.org.uk)]. Gallup and NOP data, in particular, are well-covered as the two companies have collated and published their results. The PollBase data start on `r format(min(pollbase$start), "%d %B %Y")`. Yet, consistent polling began only after the 1955 general election. Thus, we take it as our starting point.

```{r val-plot, fig.cap = "In all cases, estimates from PollBasePro appear well-validated when compared to raw polling data from Jennings and Wlezien's 'Timeline of Elections' dataset (2016).", fig.width = 6, fig.height = 2.5, fig.align = "centre", echo = F}

# Load Timeline data, filter to include only UK cases, and split by party

tl <-
  readRDS(here("inst", "extdata", "timeline.rds")) %>%
  select(
    date = polldate,
    elecdate,
    country,
    party = partyid,
    vote = poll_
  ) %>%
  filter(country == "United Kingdom") %>%
  mutate(
    vote = vote/100,
    party = case_when(party == 1 ~ "con", party == 2 ~ "lab", party == 3 ~ "lib"),
    polldate = as_date(date)
  ) %>%
  na.omit()

con <-
  tl %>%
  filter(party == "con") %>%
  left_join(
    pollbasepro,
    c("polldate" = "date")
  ) %>%
  na.omit()

lab <-
  tl %>%
  filter(party == "lab") %>%
  left_join(
    pollbasepro,
    c("polldate" = "date")
  ) %>%
  na.omit()

lib <-
  tl %>%
  filter(party == "lib") %>%
  left_join(
    pollbasepro,
    c("polldate" = "date")
  ) %>%
  na.omit()

# Create correlation plot

ggplot() +
  geom_density_2d(
    data = con %>% mutate(facet = "Conservative"),
    mapping = aes(x = vote, y = con_est),
    colour = pty_cols[1],
    alpha = .4
  ) +
  stat_smooth(
    data = con %>% mutate(facet = "Conservative"),
    mapping = aes(x = vote, y = con_est),
    colour = "black",
    fill = pty_cols[1],
    method = "lm",
    formula = y ~ x
  ) +
  # geom_text(
  #   data = con %>% mutate(facet = "Conservative"),
  #   mapping = 
  #     aes(
  #       x = .6,
  #       y = .05,
  #       label = 
  #         paste0(
  #           in_text(pluck(posterior_samples(cor_con, "rescor"), 1)*100, suffix = "%", inside = F),
  #           "\n",
  #           "MAE = ", round(mae(cor_con$data$con_est, cor_con$data$vote), 2),
  #           ", RMSE = ", round(rmse(cor_con$data$con_est, cor_con$data$vote), 2)
  #           )
  #       ),
  #   hjust = 1,
  #   size = 2,
  #   family = "Cabin Regular"
  # ) +
  geom_density_2d(
    data = lab %>% mutate(facet = "Labour"),
    mapping = aes(x = vote, y = lab_est),
    colour = pty_cols[2],
    alpha = .4
  ) +
  stat_smooth(
    data = lab %>% mutate(facet = "Labour"),
    mapping = aes(x = vote, y = lab_est),
    colour = "black",
    fill = pty_cols[2],
    method = "lm",
    formula = y ~ x
  ) +
  # geom_text(
  #   data = lab %>% mutate(facet = "Labour"),
  #   mapping = 
  #     aes(
  #       x = .6,
  #       y = .05,
  #       label = 
  #         paste0(
  #           in_text(pluck(posterior_samples(cor_lab, "rescor"), 1)*100, suffix = "%", inside = F),
  #           "\n",
  #           "MAE = ", round(mae(cor_lab$data$lab_est, cor_lab$data$vote), 2),
  #           ", RMSE = ", round(rmse(cor_lab$data$lab_est, cor_lab$data$vote), 2)
  #           )
  #     ),
  #   hjust = 1,
  #   size = 2,
  #   family = "Cabin Regular"
  # ) +
  geom_density_2d(
    data = lib %>% mutate(facet = "Liberal (Various Forms)"),
    mapping = aes(x = vote, y = lib_est),
    colour = pty_cols[3],
    alpha = .4
  ) +
  stat_smooth(
    data = lib %>% mutate(facet = "Liberal (Various Forms)"),
    mapping = aes(x = vote, y = lib_est),
    colour = "black",
    fill = pty_cols[3],
    method = "lm",
    formula = y ~ x
  ) +
  # geom_text(
  #   data = lib %>% mutate(facet = "Liberal (Various Forms)"),
  #   mapping = 
  #     aes(
  #       x = .6,
  #       y = .05,
  #       label = 
  #         paste0(
  #           in_text(pluck(posterior_samples(cor_lib, "rescor"), 1)*100, suffix = "%", inside = F),
  #           "\n",
  #           "MAE = ", round(mae(cor_lib$data$lib_est, cor_lib$data$vote), 2),
  #           ", RMSE = ", round(rmse(cor_lib$data$lib_est, cor_lib$data$vote), 2)
  #           )
  #     ),
  #   hjust = 1,
  #   size = 2,
  #   family = "Cabin Regular"
  # ) +
  facet_wrap(~ facet) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .2),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_x_continuous(
    breaks = seq(0, .6, by = .2),
    labels = scales::percent_format(accuracy = 1)
  ) +
  coord_cartesian(
    ylim = c(0, 0.62),
    xlim = c(0, 0.62)
  ) +
  labs(x = "Jennings and Wlezien's 'Timeline of Elections' Data", y = "PollBasePro Estimates") +
  theme_bailey()
```

We use the Wikipedia data to cover the period from 2010 onwards. This is a pragmatic choice. Volunteers update the data in real time and include sample sizes that are missing from PollBase. This is important as our model assumes that we know the sampling error present in each estimate. For the PollBase data, we impute likely sample sizes to allow us to estimate these errors^[Again, see the user guide that accompanies the data for more information on this process.]. But as the Wikipedia data include sample sizes, imputation is not necessary. While some might doubt Wikipedia's reliability, we do not think that it is an issue. Polling figures are verifiable and likely of interest only to a very small group of people. Wikipedia's coverage of public opinion polling since 2010 is also of a very high quality, and almost all figures on the website including links to external data sources that corroborate them.

We validate them against Jennings and Wlezien's "Timeline of Elections" dataset [-@jennings2016a]. These data contain `r format(nrow(timeline[timeline$party == 1, ]), big.mark = ",")` polls from Britain from `r str_remove(format(min(as_date(timeline$date)), "%d %B %Y"), "^0")` to `r str_remove(format(max(as_date(timeline$date)), "%d %B %Y"), "^0")`. Given that our data are so comprehensive, it is likely that most polls appear in both datasets. Still, the Timeline data provide a good test as Jennings and Wlezien compiled them independently. As figure \@ref(fig:val-plot) shows, our estimates are well validated. Correlations between the two series are strong and positive. Their mean absolute error (MAE) and root-mean-square error (RMSE) are also low in all cases. The Conservatives showed a correlation of `r in_text(pluck(posterior_samples(cor_con, "rescor"), 1)*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(mae(cor_con$data$con_est*100, cor_con$data$vote*100), 2), " percentage points")`, and an RMSE of `r round(rmse(cor_con$data$con_est, cor_con$data$vote), 2)`; Labour, a correlation of `r in_text(pluck(posterior_samples(cor_lab, "rescor"), 1)*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(mae(cor_lab$data$lab_est*100, cor_lab$data$vote*100), 2), " points")`, and an RMSE of `r round(rmse(cor_lab$data$lab_est, cor_lab$data$vote), 2)`; and the Liberals, a correlation of `r in_text(pluck(posterior_samples(cor_lib, "rescor"), 1)*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(mae(cor_lib$data$lib_est*100, cor_lib$data$vote*100), 2), " points")`, and an RMSE of `r round(rmse(cor_lib$data$lib_est, cor_lib$data$vote), 2)`.

# PollBasePro and British Politics Since 1955

Figure \@ref(fig:time-plot) shows that our estimates track British political history very well. Between 1955 and 1980, we observe the heyday of the two-party system. Here, around `r scales::percent(median(pollbasepro$lab_est[pollbasepro$date %in% seq.Date(as_date("1955-01-01"), as_date("1980-01-01"), "days")]), accuracy = .1)` of the electorate supported Labour and another `r scales::percent(median(pollbasepro$con_est[pollbasepro$date %in% seq.Date(as_date("1955-01-01"), as_date("1980-01-01"), "days")]), accuracy = .1)` the Conservatives. In the 1980s, we see the rise and fall of the SDP-Liberal alliance. Labour’s slow rise to power in 1997 soon follows, as does their loss of support over the next decade and a half. More recently, the data show a brief “blip” in Liberal support to coincide with “Cleggmania” in 2010, Labour’s surprise surge in 2017, and the Conservative's landslide support in 2019.

Table \@ref(tab:vitals-tab) summarises our estimates. One fact jumps out: that Labour and the Conservatives were almost perfectly matched. Each averaged support from around `r scales::percent(round(mean(c(pollbasepro$lab_est, pollbasepro$con_est)), 1))` of voters, this support varied by around `r scales::percent(round(mean(sd(pollbasepro$lab_est), sd(pollbasepro$con_est)), 2), suffix = " percentage points")`, and each took the lead around `r scales::percent(round(mean(as.numeric(str_remove(lead$Leader[1:2], "\\\\% of days"))), 0), scale = 1)` of the time. The Liberals---Britain's third most popular party for much of the period---were not so fortunate. Their support averaged around `r scales::percent(mean(pollbasepro$lib_est))`, though this figure varied between a low of `r scales::percent(min(pollbasepro$lib_est))` and a high of `r scales::percent(max(pollbasepro$lib_est))`, with the party taking the lead only around `r scales::percent(round(as.numeric(str_remove(lead$Leader[3], "\\\\% of days")), 0), scale = 1)` of the time.

As well as summarising facts about the parties, our estimates also allow us to make general claims about the relationships that exist *between* the parties. As figure \@ref(fig:cor-plot) shows, these are all negative. Consider the effect of rising Liberal support on the Conservatives and Labour. The correlation between the Liberals and the Conservatives is `r in_text(pluck(posterior_samples(cor_all, "rescor__libest__conest"), 1)*100, suffix = "%", inside = F)` and between the Liberals and Labour `r in_text(pluck(posterior_samples(cor_all, "rescor__libest__labest"), 1)*100, suffix = "%", inside = F)`. Contrary to popular arguments that the Liberals serve to split the centre-left vote [e.g. @jenkins2019], our figures suggest that rising Liberal support has tended to hurt the Conservatives more than Labour. Interestingly, the correlation between Labour and the Conservatives is also the smallest, at `r in_text(pluck(posterior_samples(cor_all, "rescor__conest__labest"), 1)*100, suffix = "%", inside = F)`. This is perhaps unsurprising, given that the two parties represent different sides of the left-right spectrum. Even so, that both parties have tended to target the other's vote still makes strategic sense: each party's pool of potential voters is almost always larger than the pool of potential Liberal voters.

\newpage
\begin{landscape}
```{r time-plot, fig.cap = paste("PollBasePro includes", format(nrow(pollbasepro), big.mark = ","), "daily estimates of aggregate voting intention for each of Britain's largest parties: the Conservatives, Labour, and the Liberals in their various forms."), fig.width = 10, fig.height = 6, fig.align = "centre", echo = F}

# Create over time plot

timeplot <- 
pbp_long %>%
  ggplot(
    aes(
      x = date,
      y = est,
      ymin = est - qnorm(0.975)*err,
      ymax = est + qnorm(0.975)*err,
      colour = party,
      fill = party
    )
  ) +
  geom_ribbon(alpha = .3, colour = NA) +
  geom_line() +
  coord_cartesian(ylim = c(0, 0.62)) +
  scale_colour_manual(values = pty_cols) +
  scale_fill_manual(values = pty_cols) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .1),
    labels = scales::percent_format(accuracy = 1)
    ) +
  scale_x_date(
    breaks = seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "5 years"),
    labels = year(seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "5 years"))
    ) +
  jbmisc::theme_bailey() +
  labs(
    colour = "Party",
    fill = "Party",
    y = "Vote Share"
  ) +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    axis.title.x = element_blank()
  )

# Save plot to disk

ggsave(
  filename = "timeplot.png",
  plot = timeplot + theme(legend.position = "none", axis.title.y = element_blank()),
  path = here("documentation", "_assets"),
  width = 6,
  height = 3.5,
  units = "in",
  dpi = 320
)

# Output plot

timeplot

```
\end{landscape}

```{r vitals-table, echo = F}

# Compute vital statistics

vitals <- 
  pbp_long %>% 
  mutate(party = str_remove(party, " .*|s .*")) %>% 
  group_by(party) %>% 
  summarise(
    Median = paste0(format(round(median(est)*100, 1), nsmall = 1), "\\%"),
    Mean = paste0(format(round(mean(est)*100, 1), nsmall = 1), "\\%"),
    Error = paste0(format(round(sd(est)*100, 1), nsmall = 1), "\\%"),
    Lowest = paste0(format(round(min(est)*100, 1), nsmall = 1), "\\%"),
    Highest = paste0(format(round(max(est)*100, 1), nsmall = 1), "\\%"),
    .groups = "drop"
  ) %>% 
  rename(Party = party)

# Merge vital and lead statistics

vitals <- 
  left_join(
    vitals,
    lead,
    by = "Party"
  )

# Add latex code to header names

names(vitals) <- paste0("\\textsf{\\textbf{" ,names(vitals), "}}")

# Output table

kable(
  vitals,
  align = "lrrrrrr",
  format = "latex",
  label = "vitals-tab",
  booktabs = TRUE,
  escape = FALSE,
  caption = paste0("Overall summary of voting intention estimates, ", format(min(pollbasepro$date), "%Y"), " to ", format(max(pollbasepro$date), "%Y"))
  ) %>% 
  kable_styling(position = "center")

```

We can also use our estimates to make specific claims about British politics. For example, we can assert with a reasonable degree of certainty that the `r pbp_long$party[which.max(pbp_long$est)]` received the largest degree of support of any party in Britain between `r format(min(pollbasepro$date), "%Y")` and `r format(max(pollbasepro$date), "%Y")` on `r str_remove(format(pbp_long$date[which.max(pbp_long$est)], "%d %B %Y"), "^0")` when our estimates show that `r scales::percent(pbp_long$est[which.max(pbp_long$est)], accuracy = 0.1)` (95% CI: `r paste(scales::percent(pbp_long$est[which.max(pbp_long$est)] - qnorm(0.975)*pbp_long$err[which.max(pbp_long$est)], accuracy = 0.1), "to", scales::percent(pbp_long$est[which.max(pbp_long$est)] + qnorm(0.975)*pbp_long$err[which.max(pbp_long$est)], accuracy = 0.1))`) of the electorate would vote for them at the next election. Similarly, we can assert that Labour's peak in the polls came on `r str_remove(format(pollbasepro$date[which.max(pollbasepro$lab_est)], "%d %B %Y"), "^0")` when `r scales::percent(max(pollbasepro$lab_est), accuracy = .1)` (95% CI: `r paste(scales::percent(max(pollbasepro$lab_est) - qnorm(0.975)*pollbasepro$lab_err[which.max(pollbasepro$lab_est)], accuracy = 0.1), "to", scales::percent(max(pollbasepro$lab_est) + qnorm(0.975)*pollbasepro$lab_err[which.max(pollbasepro$lab_est)], accuracy = 0.1))`) of the electorate intended to back them.

These data and their summaries raise an interesting question: if Labour and the Conservatives have tended to be so well-matched in the polls, why have the Conservatives done so much better at election time? Despite leading in the polls `r str_remove(lead$Leader[2], " of days")` of the time, Labour has gained the highest share of the vote in only `r pbp_long %>% filter(err == 0) %>% group_by(election) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% summarise(lab = length(winner[winner == "Labour Party"]), .groups = "drop") %>% pluck(1)` of the period's `r pbp_long %>% filter(err == 0) %>% group_by(election) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% nrow()` general elections (`r scales::percent((pbp_long %>% filter(err == 0) %>% group_by(election) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% summarise(lab = length(winner[winner == "Labour Party"]), .groups = "drop") %>% pluck(1))/(pbp_long %>% filter(err == 0) %>% group_by(election) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% nrow()))`). This phenomenon is not entirely unprecedented. @jackman1994 shows that the Australian Labor Party has suffered at elections due to pervasive electoral bias. Though this might also be the case in Britain, our figures reflect *vote* shares, not *seat* shares. As such, electoral bias should be a concern only insofar as it affects the parties' overall popularity. Other factors likely explain Labour's poor performance: Britain's press leans right and tends to support the Conservatives; successive Conservative governments could have scheduled elections to maximise their chances; partisan non-response could have led Conservative voters to drop out of polls in the period between elections; or, most simply, the Conservatives might just be better at campaigning.

```{r cor-plot, fig.cap = paste0("Historic correlations between each of Britain's three largest parties, ", format(min(pollbasepro$date), "%Y"), " to ", format(max(pollbasepro$date), "%Y")), fig.width = 6, fig.height = 2.5, fig.align = "centre", echo = F}

# Create Conservative v. Liberal Plot

plot1 <- 
  pollbasepro %>% 
  ggplot(
    aes(
      x = lib_est,
      y = con_est
    )
  ) +
  geom_density_2d(
    colour = bailey_colours("grey4"),
    alpha = .4
    ) +
  stat_smooth(
    method = "lm",
    formula = "y ~ x",
    colour = bailey_colours("black"),
    se = TRUE
  ) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .2),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_x_continuous(
    breaks = seq(0, .6, by = .2),
    labels = scales::percent_format(accuracy = 1)
  ) +
  coord_cartesian(
    ylim = c(0, 0.62),
    xlim = c(0, 0.62)
  ) +
  labs(x = "Liberal Support", y = "Conservative Support") +
  annotate(
    "text",
    label = 
      in_text(pluck(posterior_samples(cor_all, "rescor__libest__conest"), 1)*100, suffix = "%", inside = F),
    x = .6, y = .1,
    hjust = 1,
    size = 2,
    family = "Cabin"
    ) +
  theme_bailey()

# Create Labour v. Liberal Plot

plot2 <- 
  pollbasepro %>% 
  ggplot(
    aes(
      x = lib_est,
      y = lab_est
    )
  ) +
  geom_density_2d(
    colour = bailey_colours("grey4"),
    alpha = .4
    ) +
  stat_smooth(
    method = "lm",
    formula = "y ~ x",
    colour = bailey_colours("black"),
    se = TRUE
  ) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .2),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_x_continuous(
    breaks = seq(0, .6, by = .2),
    labels = scales::percent_format(accuracy = 1)
  ) +
  coord_cartesian(
    ylim = c(0, 0.62),
    xlim = c(0, 0.62)
  ) +
  labs(x = "Liberal Support", y = "Labour Support") +
  annotate(
    "text",
    label = 
      in_text(pluck(posterior_samples(cor_all, "rescor__libest__labest"), 1)*100, suffix = "%", inside = F),
    x = .6, y = .1,
    hjust = 1,
    size = 2,
    family = "Cabin"
    ) +
  theme_bailey()

# Create Conservative v. Labour Plot

plot3 <- 
  pollbasepro %>% 
  ggplot(
    aes(
      x = lab_est,
      y = con_est
    )
  ) +
  geom_density_2d(
    colour = bailey_colours("grey4"),
    alpha = .4
    ) +
  stat_smooth(
    method = "lm",
    formula = "y ~ x",
    colour = bailey_colours("black"),
    se = TRUE
  ) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .2),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_x_continuous(
    breaks = seq(0, .6, by = .2),
    labels = scales::percent_format(accuracy = 1)
  ) +
  coord_cartesian(
    ylim = c(0, 0.62),
    xlim = c(0, 0.62)
  ) +
  labs(x = "Labour Support", y = "Conservative Support") +
  annotate(
    "text",
    label = 
    in_text(pluck(posterior_samples(cor_all, "rescor__conest__labest"), 1)*100, suffix = "%", inside = F),
    x = .6, y = .1,
    hjust = 1,
    size = 2,
    family = "Cabin"
    ) +
  theme_bailey()

# Stitch plots together

plot1 + plot2 + plot3

```

# Using PollBasePro to Answer Political Questions

It is one thing to show that our estimates are well-validated; it is quite another to show that they can advance our understanding of politics. As we mention above, raw polling data cover irregular time intervals and can be difficult to match to other time series. Our data face no such problem. Instead, as PollBasePro includes daily voting intention estimates, it is simple to merge the data into any other time series, whether they be daily, weekly, monthly, quarterly, or yearly.

To demonstrate their usefulness, we use our data to answer a question of timely importance: how are deaths attributable to COVID-19 related to public support for the governing Conservative Party? To answer this question, we merge our data into the UK Government's tracker of daily COVID-related deaths [-@ukgovernment2021]. These data run from `r str_remove(format(min(death_dta$date), "%d %B %Y"), "^0")` to `r str_remove(format(max(death_dta$date), "%d %B %Y"), "^0")`, though we begin our analysis at the 2019 General Election and mark any deaths before the start of the pandemic as zero. We then compute daily changes in Conservative support and daily changes in COVID-related deaths across a four week window, before modelling the former as a function of the latter using the following error-in-variables model:

\begin{align*}
\Delta C_{t} &\sim \mathrm{Normal}(\mu_{t}, \sqrt{\sigma^2 + S_{t}^2}) \srlab{Likelihood function} \\
\mu_{t} &= \alpha + \beta_{1} T_{t} + \beta_{2} \Delta D_{t} + \beta_{3} T_{t} \times \Delta D_{t} \srlab{Linear model on $\mu$} \\
\alpha &\sim \mathrm{Normal}(0, 0.1) \srlab{Prior on $\alpha$} \\
\beta_{j} &\sim \mathrm{Normal}(0, 0.1) \text{ for } j \text{ in } 1, ..., J \srlab{Prior on $\beta$} \\
\sigma &\sim \mathrm{Exponential}(10) \srlab{Prior on $\sigma$} \\
\end{align*}

This is a simple linear model, where change in Conservative support at time $t$, $\Delta C_{t}$, is a function of the passage of time, $T_{t}$, and change in the number of COVID-related deaths, $\Delta D_{t}$. We also interact the two variables so that the effect of these deaths can change over time. As the intervals in figure \@ref(fig:time-plot) make clear, our data are *probabilistic*. Thus, it is important that we propagate this uncertainty forward so as to maximise our statistical power. This is what differentiates our error-in-variables model from a standard linear model: rather than include only the residual error, $\sigma$, we also include any known uncertainty in our estimates at time $t$, $S_{t}$.

According to the literature, there are good reasons why the relationship between the two variables might be positive and good reasons why it might be negative. The literature on "rally 'round the flag" effects would favour a *positive* relationship. Here, voters rush to support the governing party in times of crisis, such as wars [@kuijpers2019; @mueller1970]. The literature on retrospective voting [@healy2013; @fiorina1981], instead, would favour a *negative* relationship. It holds that voters reward governments for positive policy outcomes and punish them for negative ones.

Figure \@ref(fig:death-plot) shows that the effect is more "rally 'round the flag" than "reward and punishment". That said, our model suggests at least some preliminary evidence of a transition from one mechanism to the other. In March 2020, when the pandemic started to gain pace in Britain, there was a strong positive relationship between change in the number of deaths attributable to COVID-19 and change in support for the governing Conservative Party. For every 100 extra COVID-related deaths over the past 4 weeks, Conservative support over the same period increased on average by `r in_text((pluck(posterior_samples(death_mod, "b_deaths"), 1) + pluck(posterior_samples(death_mod, "b_time:deaths"), 1)*2)*100, inside = F, text = " points")`. Six months later, in September 2020, this relationship had weakened markedly. Though still positive, it had fallen to only `r in_text((pluck(posterior_samples(death_mod, "b_deaths"), 1) + pluck(posterior_samples(death_mod, "b_time:deaths"), 1)*8)*100, inside = F, text = " points")`. A year after the pandemic began, the relationship had reversed. In March 2021, every 100 additional COVID-related deaths over the past 4 weeks led Conservative support to fall on average by `r in_text((pluck(posterior_samples(death_mod, "b_deaths"), 1) + pluck(posterior_samples(death_mod, "b_time:deaths"), 1)*14)*100, inside = F, text = " points")`.

```{r death-plot, fig.cap = "At the start of the COVID-19 pandemic, more deaths were related to greater support for the incumbent Conservative Party. As time has passed, this relationship has reversed.", fig.width = 6, fig.height = 2.5, fig.align = "centre", echo = F}

# Get conditional effects

cond_fx <- 
  conditional_effects(
    death_mod,
    "deaths",
    conditions =
      tibble(
        time = seq(2, 14, by = 6),
        cond__ = c("Mar. 2020", "Sep. 2020", "Mar. 2021")
      )
  )$deaths

# Create plot

cond_fx %>% 
  ggplot(
    aes(
      x = deaths,
      y = estimate__,
      ymin = estimate__ - qnorm(.975)*se__,
      ymax = estimate__ + qnorm(.975)*se__
    )
  ) +
  facet_wrap(~ cond__) +
  geom_vline(
    xintercept = 0,
    colour = bailey_colours("grey4"),
    linetype = "dotted"
  ) +
  geom_ribbon(
    colour = NA,
    fill = bailey_colours("red"),
    alpha = .2) +
  geom_line(colour = bailey_colours("red")) +
  scale_y_continuous(
    breaks = seq(-.1, .1, by = .05),
    labels = scales::percent_format(suffix = "pts", accuracy = 1)
  ) +
  scale_x_continuous(
    breaks = seq(-10, 10, by = 5),
    labels = scales::number_format(scale = 100)
  ) +
  coord_cartesian(
    ylim = c(-.1, .1),
    xlim = c(-10, 10)
  ) +
  labs(
    y = "Change in Con. Support, Past 4 Weeks",
    x = "Change in Deaths Attributable to COVID-19, Past 4 Weeks"
  ) +
  theme_bailey()
```

It is clear then that PollBasePro has allowed us to reveal an important---if surprising---answer to the question that we posed above: despite Britain having one of the world's highest levels of COVID-related deaths per capita [@ritchie2021], these untimely deaths appear to have *benefited* the fortunes of the governing Conservative Party. Still, the relationship has changed over time and, a year into the pandemic, has reversed direction. We might, thus, expect any further deaths attributable to COVID-19 to erode the Conservative's ample base of support. Yet given the pace of Britain's vaccination programme [@ukgovernment2021a], it is possible that the Conservatives have reaped the rewards without facing any punishment.

# Conclusions

In this paper, we introduce PollBasePro: the most comprehensive time series of British voting intention data assembled to date. The dataset contains `r format(nrow(PollBasePro::pollbasepro), big.mark = ",")` daily voting intention estimates for each of Britain's three largest parties, beginning at the 1955 General Election on `r format(min(pollbasepro$date), "%d %B %Y")` and ending on `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`. Furthermore, our data are well validated and follow the course of British political history. We therefore expect PollBasePro to become a valuable resource for students of British politics in the years to come.

It is important to stress that PollBasePro is a *living dataset*. As a result, we expect to incorporate new estimates into the data as time goes by. Users should, therefore, endeavour to use the most recent data in any of their analyses. It is also important to stress that---like any project of this nature---our data pipeline might contain minor errors or inefficiencies. To guard against this, we have hosted all of our materials online for others to inspect. If our users find any errors in our code or wish to make recommendations for future updates, we invite them to raise an issue on the project's GitHub repository or to contact the authors directly.

Though we believe that our data can help to answer all manner of questions, PollBasePro still has room to grow. Three new features would be most useful. First, to estimate aggregate support for the UK leaving the European Union and for Scotland leaving the UK. Both time series would be long-ranging and benefit from having known outcomes to which we could anchor our estimates. Second, to expand the data beyond the three main parties. This would be particularly useful for those who study, for example, the rise of the SNP in Scotland or the influence of UKIP. Third, to collect and incorporate known sample sizes into all of our polling data. At the moment, we use the Timeline of Elections dataset [@jennings2016a] to impute sample sizes for all polls that occurred before the 2010 general election. This is a pragmatic but reasonable decision given that these data do not include sample sizes. Still, were we to have the necessary resources, it would be good to collect the sample sizes associated with these polls to ensure that our estimates are as precise as possible.

\pagebreak

# References

::: {#refs}

:::

```{r session-info, include = FALSE, echo = F}

# Save session information to the "sessions" folder

save_info(path = here("sessions", "006_paper.txt"))

```

### 2021-03-12 documentation/readme.Rmd
Initial commit

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}

# Load packages

library(PollBasePro)
library(tidyverse)
library(lubridate)
library(here)

# Set knitr options

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PollBasePro

PollBasePro is a data package for the `R` programming language. It includes two datasets: `pollbase` and `pollbasepro`. The first provides a long-format and ready-to-analyse version of Mark Pack's dataset of historic British public opinion polls combined with more recent polling data from Wikipedia. The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.

To install the latest version of PollBasePro, run the following code in `R`:

``` r
devtools::install_github("jackobailey/PollBasePro")
```

We also provide `pollbase` and `pollbasepro` as .dta and .sav files for Stata and SPSS users. These files include all necessary value and variable labels and should work seamlessly with both software packages. Click here to download them.

## Latest Polling Estimates

```{r figs, include = FALSE}

# Get most recent pollbasepro estimates

txt_dta <-
  pollbasepro[pollbasepro$date == max(pollbasepro$date), ] %>%
  pivot_longer(
    cols = c(-date, -election, -govt, -matches("_ldr"), -week, -month, -quarter, -year),
    names_to = c("party", ".value"),
    names_sep = "_"
    ) %>%
  arrange(desc(est)) %>%
  select(
    party,
    est,
    err
  ) %>% 
  mutate(
    party =
      case_when(
        party == "con" ~ "Conservative Party",
        party == "lab" ~ "Labour Party",
        party == "lib" ~ "Liberal Democrats"
        ),
    lower = scales::percent(est - stats::qnorm(.975)*err, accuracy = 1),
    upper = scales::percent(est + stats::qnorm(.975)*err, accuracy = 1),
    share = scales::percent(est, accuracy = 1)
    )

```

```{r time-plot, fig.width = 9, fig.height = 5, fig.align = "centre", echo = F}

# Define party colours

pty_cols <-
  c(
    "Conservative Party" = "#0087dc",
    "Labour Party" = "#d50000",
    "Liberals (Various Forms)" = "#fdbb30"
  )

# Create over time plot

timeplot <- 
pollbasepro %>% 
  pivot_longer(
    cols = c(-date, -election, -govt, -week, -month, -quarter, -year, -con_ldr, -lab_ldr, -lib_ldr),
    names_to = c("party", ".value"),
    names_sep = "_",
  ) %>%
  mutate(
    party =
      case_when(
        party == "con" ~ "Conservative Party",
        party == "lab" ~ "Labour Party",
        party == "lib" ~ "Liberals (Various Forms)"
      ) %>% 
      factor(
        levels = 
          c("Conservative Party",
            "Labour Party",
            "Liberals (Various Forms)"
          )
      )
  ) %>%
  ggplot(
    aes(
      x = date,
      y = est,
      ymin = est - qnorm(0.975)*err,
      ymax = est + qnorm(0.975)*err,
      colour = party,
      fill = party
    )
  ) +
  geom_ribbon(alpha = .3, colour = NA) +
  geom_line() +
  scale_colour_manual(values = pty_cols) +
  scale_fill_manual(values = pty_cols) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .1),
    labels = scales::percent_format(accuracy = 1)
    ) +
  scale_x_date(
    breaks = seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"),
    labels = format(seq.Date(as.Date("1955-01-01"), max(pollbasepro$date), by = "3 months"), "%b %y")
    ) +
  coord_cartesian(
    ylim = c(0, 0.62),
    xlim = c(as_date("2019-12-12"), Sys.Date())
    ) +
  jbmisc::theme_bailey() +
  labs(
    colour = "Party",
    fill = "Party",
    y = "Vote Share",
    caption = "Based on data from PollBasePro, created by Jack Bailey, Mark Pack, and Luke Mansillo: www.github.com/jackobailey/PollBasePro"
  ) +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    axis.title.x = element_blank()
  )

# Output plot

ggsave(
  filename = "timeplot_gh.png",
  plot = timeplot,
  path = here("documentation", "_assets"),
  width = 6,
  height = 3.5,
  units = "in",
  dpi = 320
)

```

<center><img src="https://raw.githubusercontent.com/jackobailey/econ_half_life/master/documentation/_assets/timeplot_gh.png"></center>

As of `r str_remove(format(Sys.Date(), "%d %B %Y"), "^0")`, we estimate that **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "has", "have")` the largest base of support** with `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")` of the electorate intending to vote for them at the next election. **They hold a lead over the `r txt_dta$party[2]`** of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`. **This puts the `r txt_dta$party[2]` in second place** on `r paste0(txt_dta$share[2], " (95% CI: ", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")` of the vote. **In third place is the `r txt_dta$party[3]`**, who gain the support of around `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")` of voters.

## Notes, Usage, and Attribution

Both `pollbase` and `pollbasepro` are living datasets. As such, users should try to use only the most recent version of the data when conducting their analyses. Like any project of this size, we cannot rule out the possibility that minor mistakes might have crept into our data processing pipeline. If you think that you have found an error in our code or wish to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/PollBasePro/issues) or [contact us directly](mailto:jack.bailey@manchester.ac.uk).

We are happy for others to use our code for their own purposes, but ask that they do so *with attribution*. That is, you may reproduce, reuse, and change the code here as you see fit, but must state in each case that you based your analysis on our work. The citations for each item in PollBasePro are as follows:

- **Data:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("PollBasePro")` [computer file], `r format(Sys.Date(), format = "%B %Y")`. Retrieved from doi.

- **Documentation:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro v`r packageVersion("PollBasePro")`: User Guide and Codebook. Retrieved from doi.

- **Paper:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")`. Retrieved from doi.

### 2021-03-12 documentation/userguide.Rmd
Initial commit

---
title: |
  | PollBasePro v`r packageVersion("PollBasePro")` (Beta)
  | User Guide and Codebook
date: |
  | This version: `r stringr::str_remove(format(Sys.time(), "%d %B %Y"), "^0")`
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/cb-preamble.tex
    number_sections: false
    fig_caption: true
---

<!-- Latex setup -->

\doublespacing

```{=tex}
\thispagestyle{empty}
\clearpage
```
\pagebreak

\setcounter{page}{1}
\setcounter{tocdepth}{2}  <!-- Set table of contents depth -->
\tableofcontents          <!-- Print table of contents -->
\pagebreak                <!-- Space between table of contents and content -->

```{r setup, include = F}

# Icons made by [Freepik](https://www.freepik.com) from [Flaticon](https://www.flaticon.com/).

# Load packages

library(PollBasePro)
library(kableExtra)
library(tidyverse)
library(lubridate)
library(jbmisc)
library(brms)
library(here)

# Load PollBasePro data

data("pollbase")
data("pollbasepro")

# Load imputed sample sizes

load(here("R", "sysdata.rda"))

# Load timeline data

timeline <-
  readRDS(here("inst", "extdata", "timeline.rds")) %>%
  select(
    date = polldate,
    elecdate,
    country,
    party = partyid,
    vote = poll_
  ) %>%
  filter(country == "United Kingdom") %>% 
  na.omit()

# Load correlation models

cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("PollBasePro"), ".rds")))
cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("PollBasePro"), ".rds")))
cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("PollBasePro"), ".rds")))

# Tell knitr to use Cairo PDF when rendering plots so that it uses nice fonts

knitr::opts_chunk$set(dev = "cairo_pdf")

```

# About PollBasePro

PollBasePro is a data package for the `R` programming language. It includes two datasets: `pollbase` and `pollbasepro`. The first provides a long-format and ready-to-analyse version of Mark Pack's [-@pack2021] dataset of historic British public opinion polls combined with more recent polling data from Wikipedia. The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.

Both `pollbase` and `pollbasepro` are *living datasets*. Thus, users should endeavour to use only the most recent version of the data when conducting their analyses. This will become more important in the future, as we intend to add new polls and estimates over time. Likewise, we cannot rule out that minor mistakes might have crept into our data processing pipeline. To guard against this, we have made all of our materials available for others to inspect. If you find an error in the code or wish to make a recommendation for a future update, we invite you to raise an issue on the PollBasePro GitHub repository.

# Citing PollBasePro

If you use PollBasePro, you should also cite it. This is good practice and also allows the PollBasePro team to monitor how the data have been used. The project comprises three items: the data, this user guide, and a companion paper. The citations for each item are as follows:

- **Data:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("PollBasePro")` [computer file], `r format(Sys.Date(), format = "%B %Y")`. Retrieved from doi.

- **Documentation:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro v`r packageVersion("PollBasePro")`: User Guide and Codebook. Retrieved from doi.

- **Paper:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")`. Retrieved from doi.

# Using PollBasePro

Getting started with PollBasePro in `R` is simple. It requires only three short steps: first, to install the package; second, to load the package; and, third, to load the data. Once you have taken these three steps, you can then begin analysing the data. Note that PollBasePro is not yet available on CRAN, the service that hosts most `R` packages. As such, it is not yet possible to install PollBasePro with `R`'s standard `install.packages()` function. Instead, we must install it directly from its GitHub repository. Thankfully this is straightforward and requires only that you run the following code in your `R` console:

```{r install-pbp, eval = FALSE}
# 1. Install the PollBasePro package from GitHub
devtools::install_github("jackobailey/PollBasePro")

# 2. Load the PollBasePro package in R
library(PollBasePro)

# 3. Load the pollbase and pollbasepro datasets
data("pollbase")
data("pollbasepro")
```

Though PollBasePro is first and foremost an `R` data package, we have sought to accommodate those who use Stata and SPSS too. To make this as easy as possible, we have made both the `pollbase` and `pollbasepro` datasets available as .dta and .sav files. These include all necessary value and variable labels and should work seamlessly with both software packages. You can download the latest version of the data by clicking the links below:

- ``r paste0("pollbase_", packageVersion("PollBasePro"), ".dta")``
- ``r paste0("pollbasepro_", packageVersion("PollBasePro"), ".dta")``
- ``r paste0("pollbase_", packageVersion("PollBasePro"), ".sav")``
- ``r paste0("pollbasepro_", packageVersion("PollBasePro"), ".sav")``

```{r error-plot, fig.cap = "The posterior uncertainty in the estimates that we include in the pollbasepro dataset are correlated with time. This is because polls have become more frequent and have included larger sample sizes as time has passed. Thus, our estimates also become more precise.", fig.width = 6, fig.height = 2.5, fig.align = "centre", echo = F}

ggplot() +
  geom_density_2d(
    data = pollbasepro %>% mutate(facet = "Conservative"),
    mapping = 
      aes(
        x = date,
        y = qnorm(.975)*con_err
        ),
    colour = "#0087dc",
    alpha = .4
  ) +
  stat_smooth(
    data = pollbasepro %>% mutate(facet = "Conservative"),
    mapping = aes(
      x = date,
      y = qnorm(.975)*con_err
    ),
    method = "lm",
    formula = y ~ x,
    se = TRUE,
    colour = "black"
  ) +
  geom_density_2d(
    data = pollbasepro %>% mutate(facet = "Labour"),
    mapping = 
      aes(
        x = date,
        y = qnorm(.975)*lab_err
        ),
    colour = "#d50000",
    alpha = .4
  ) +
  stat_smooth(
    data = pollbasepro %>% mutate(facet = "Labour"),
    mapping = aes(
      x = date,
      y = qnorm(.975)*lab_err
    ),
    method = "lm",
    formula = y ~ x,
    se = TRUE,
    colour = "black"
  ) +
  geom_density_2d(
    data = pollbasepro %>% mutate(facet = "Liberal"),
    mapping = 
      aes(
        x = date,
        y = qnorm(.975)*lib_err
        ),
    colour = "#fdbb30",
    alpha = .4
  ) +
  stat_smooth(
    data = pollbasepro %>% mutate(facet = "Liberal"),
    mapping = aes(
      x = date,
      y = qnorm(.975)*lib_err
    ),
    method = "lm",
    formula = y ~ x,
    se = TRUE,
    colour = "black"
  ) +
  facet_wrap(~facet) +
  scale_y_continuous(
    breaks = seq(0, 0.05, by = .01),
    labels = scales::percent_format(suffix = "pts", accuracy = .1)
  ) +
  scale_x_date(
    breaks = seq.Date(as.Date("1960-01-01"), as.Date("2020-01-01"), by = "10 years"),
    labels = year(seq.Date(as.Date("1960-01-01"), as.Date("2020-01-01"), by = "10 years"))
  ) +
  coord_cartesian(ylim = c(0, 0.05)) +
  jbmisc::theme_bailey() +
  labs(y = "Posterior Uncertainty (95%)") +
  theme(axis.title.x = element_blank())

```

Note that the estimates that we include in the `pollbasepro` dataset are *probabilistic*. As such, we include in the dataset both an estimate of the posterior mean of aggregate voting intention for each party on each day *and* the posterior uncertainty in these estimates. As figure \@ref(fig:error-plot) makes clear, our uncertainty estimates are not random. Instead, they are correlated with time. This occurs because polls have become more numerous and have tended to include larger sample sizes as time has passed. Thus, our estimates for more recent years are more certain than our estimates for years long far into the past.

We advise all those who use the `pollbasepro` dataset to include this uncertainty in their analyses wherever possible. This is important both because propagating our uncertainty forward is good practice and because such uncertainty serves both to reduce statistical power and to attenuate real and existing relationships in the data. This is possible using "errors-in-variables models". These models work much like regular generalised linear models, though account for measurement error in either the dependent variable, the independent variables, or both. @mcelreath2020 provides a good introduction to the intuition behind error-in-variable models. Similarly, Bürkner [-@burkner2017] provides an easy-to-use interface for fitting such models in `R` using the `brms` package [see also chapter 15.1 in @kurz2020 for an applied example].

\pagebreak

# Technical Details: Estimating Daily Voting Intention

We adapt Jackman's [-@jackman2005] method to derive our daily estimates. Still, there are issues specific to our case that we must first overcome. We elaborate on our choices below.

## Imputating Missing Sample Sizes

Our data do not include sample sizes before the 2010 general election. This is a problem, as our model requires that we know this information. To solve this problem, we use data from Jennings and Wlezien's [-@jennings2016a] "Timeline of Elections" dataset. Though less comprehensive than PollBase, these data do include information on sample sizes. What's more, they also include data from countries other than Britain. This lets us pool all available information to improve our estimates.

Sample sizes are count data. As such, we use the following multilevel Poisson regression model to impute likely sample sizes for all of our pre-2010 polling data:

\begin{align*}
n_{i} &\sim \mathrm{Poisson}(\lambda_{i}) \srlab{Likelihood function} \\
log(\lambda_{i}) &= \alpha_{Country[i]} + \beta_{Country[i]} T_{i} \srlab{Linear model on $\lambda$} \\
\begin{bmatrix} \alpha_{Country} \\ \beta_{Country} \end{bmatrix} &\sim \mathrm{MVNormal}(\begin{bmatrix} \alpha \\ \beta \end{bmatrix}, \textbf{S}) \srlab{Multivariate prior on varying effects} \\
\textbf{S} &= \begin{pmatrix} \sigma_{\alpha} & 0 \\ 0 & \sigma_{\beta} \end{pmatrix} \textbf{R} \begin{pmatrix} \sigma_{\alpha} & 0 \\ 0 & \sigma_{\beta} \end{pmatrix} \srlab{Covariance matrix on varying effects} \\
\alpha &\sim \mathrm{Normal}(7, 0.5) \srlab{Prior on average intercept, $\alpha$} \\
\beta &\sim \mathrm{Normal}(0, 0.1) \srlab{Prior on average slope, $\beta$} \\
\sigma_{\alpha} &\sim \mathrm{Exponential}(10) \srlab{Prior on uncertainty in the intercepts, $\sigma_{\alpha}$} \\
\sigma_{\beta} &\sim \mathrm{Exponential}(10) \srlab{Prior on uncertainty in the slopes, $\sigma_{\beta}$} \\
\textbf{R} &\sim \mathrm{LKJ}(2) \srlab{Prior on correlation matrix, $\textbf{\textrm{R}}$} \\
\end{align*}

```{r n-plot, fig.cap = paste0("Imputed sample sizes in Britain between ", format(min(samplesizes$date), "%Y"), " and ", format(max(samplesizes$date), "%Y"), ", estimated using sample size data from Jennings and Wlezien's \"Timeline of Elections\" dataset (2016)."), fig.width = 6, fig.height = 3, fig.align = "centre", echo = F}

# Create sample size plot

samplesizes %>%
  ggplot(
    aes(
      x = date,
      y = n_est,
      ymin = qpois(0.025, n_est),
      ymax = qpois(0.975, n_est)
    )
  ) +
  geom_ribbon(alpha = .3, colour = NA) +
  geom_line() +
  scale_y_continuous(breaks = seq(0, 2500, by = 500)) +
  scale_x_date(
    breaks = seq.Date(as.Date("1945-01-01"), as.Date("2020-01-01"), by = "5 years"),
    labels = year(seq.Date(as.Date("1945-01-01"), as.Date("2020-01-01"), by = "5 years"))
    ) +
  coord_cartesian(ylim = c(0, 2600)) +
  jbmisc::theme_bailey() +
  labs(
    y = "Imputed Sample Size"
  ) +
  theme(axis.title.x = element_blank())

```

We assume that the sample size associated with poll $i$ in the Timeline data, $n_{i}$, is distributed as Poisson according to some rate parameter, $\lambda_{i}$. We then model the logarithm of this parameter using a simple linear function that includes an intercept, $\alpha_{Country}$, and a slope on the effect of time, $\beta_{Country}$, which we allow to vary over countries. We then relate these two parameters to one another by modelling them as though they come from a multivariate normal distribution. In effect, this allows the parameters to be correlated and, thus, to share information.

While our data concern Britain alone, we use all available data in the Timeline dataset. This is for good reason. The dataset does not contain reliable sample size values for British polls conducted before the early 1960s. But it does contain reliable values for other countries as early as the mid-1940s. Pooling all available information for all countries across the entire time series, thus, allows us to impute reliable estimates of likely sample sizes in Britain across the full range of dates by drawing on persistent differences between British polls and those from other countries.

Figure \@ref(fig:n-plot) shows the model's best estimate of the likely sample size of the average British voting intention poll between `r year(min(samplesizes$date))` and `r year(max(samplesizes$date))`. These imputed values seem sensible and conform to our expection that sample sizes should increase over time. The model estimates that the average British voting intention poll included around `r format(round(samplesizes$n_est[samplesizes$date == min(samplesizes$date)], 0), big.mark = ",")` respondents in `r year(min(samplesizes$date))`. By `r year(max(samplesizes$date))`, the model suggests that this value had increased by `r format(round(samplesizes$n_est[samplesizes$date == max(samplesizes$date)] - samplesizes$n_est[samplesizes$date == min(samplesizes$date)], 0), big.mark = ",")` to `r format(round(samplesizes$n_est[samplesizes$date == max(samplesizes$date)], 0), big.mark = ",")` respondents per poll on average.

We use the model to produce a time series of estimates sample sizes between `r year(min(samplesizes$date))` and `r year(max(samplesizes$date))`. This includes all dates for which we intend to produce a voting intention estimate. Where our polling data come from before the 2010 general election, or are otherwise missing, will fill in the gaps with these imputed values. To do so we match our polling data to the imputed values from the model based on their respective dates.

## Estimating Daily Voting Intention Figures

As we mention above and in the accompanying paper, we adapt the model in @jackman2005 to compute our daily British voting intention estimates. The model is complex and has many moving parts, so we will build it up step by step.

We assume that each poll in our underlying data, $Poll_{i}$, is generated from some normal distribution. This distribution has two parameters. The first is some mean, $\mu_{i}$. The second is some error that leads the estimates to be higher or lower than the expected value, $\mu_{i}$. In many models with a normal likelihood function, this error parameter would measure only random residual error and be represented by the Greek letter $\sigma$. But, in our case, we have additional information that we can use. We know that each poll is a proportion and represents a draw from some random distribution. Thus, we can use the equation for the standard error of a proportion to calculate the uncertainty in each estimate, where $S_{i} = \sqrt{\frac{Poll_{i} (1 - Poll_{i})}{\nu_{i}}}$. Note that $\nu_{i}$ is the sample size of $Poll_{i}$, $n_{i}$, divided by the number of days the poll spent in the field, $k_{i}$. In effect, this implies that we assume an equal number of people were polled on each day that the model was in the field. We can then include both in our model to account for any known error, $S_{i}$, and any random residual error, $\sigma$. So far, our model is as follows:

\begin{align*}
Poll_{i} &\sim \mathrm{Normal}(\mu_{i}, \sqrt{\sigma^2 + S_{i}^2}) \srlab{Likelihood function} \\
\end{align*}

The next step is to fit a model to $\mu_{i}$. This will be a measurement model, as it will allow us to produce an estimate of the electorate's *latent* voting intention on each day. We assume that $\mu_{i}$ is a linear function of two variables: $\alpha_{Day[i]}$, the electorate's latent voting intention for $Poll_{i}$ on the day that it was fielded, and $\delta_{Pollster[i]}$, the persistent "house effects" that arise due to the methodological and design choices that inform how the company that ran the poll collected its data. If we update our model specification to include these assumptions, we get the following:

\begin{align*}
Poll_{i} &\sim \mathrm{Normal}(\mu_{i}, \sqrt{\sigma^2 + S_{i}^2}) \srlab{Likelihood function} \\
\mu_{i} &= \alpha_{Day[i]} + \delta_{Pollster[i]} \srlab{Measurement model on $\mu$} \\
\end{align*}

At present, all values of $\alpha_{Day}$ are independent. This is a problem. First, we want estimates closer together to be more similar. Second, some days have no polling data to inform them. To address this problem, we constrain $\alpha_{1}$ to be equal to the vote share that a given party received at a given election. We also constrain $\alpha_{T}$ to be equal to the vote share that the same party received at the following election. Next, we fit a dynamic model to $\alpha_{t}$ for all days in our time series except for the first and last. This acts as a sort of "chain" that links together all values of $\alpha$. Because these values are now linked, they can then share information amongst themselves. This means that when the value of one estimate changes during the model estimation process, so too do the values of all others. The model assumes that $\alpha_{t}$ is equal to $\alpha_{t-1}$, plus any random shocks that take place between the two days, $\omega_{t-1}$. These random shock parameters are themselves scaled according to $\tau$, the scale of innovations parameter. This [DOES WHATEVER IT DOES]. Updating our model specification again, we get:

\begin{align*}
Poll_{i} &\sim \mathrm{Normal}(\mu_{i}, \sqrt{\sigma^2 + S_{i}^2}) \srlab{Likelihood function} \\
\mu_{i} &= \alpha_{Day[i]} + \delta_{Pollster[i]} \srlab{Measurement model on $\mu$} \\
\alpha_{t} &= \alpha_{t-1} + \tau \omega_{t-1} \text{ for } t \text{ in } 2, ..., T-1 \srlab{Dynamic model on $\alpha_{t}$} \\
\end{align*}

As we rely on Bayesian methods, our final step is to provide the model with a set of prior distributions.

\begin{align*}
Poll_{i} &\sim \mathrm{Normal}(\mu_{i}, \sqrt{\sigma^2 + S_{i}^2}) \srlab{Likelihood function} \\
\mu_{i} &= \alpha_{Day[i]} + \delta_{Pollster[i]} \srlab{Measurement model on $\mu$} \\
\alpha_{t} &= \alpha_{t-1} + \tau \omega_{t-1} \text{ for } t \text{ in } 2, ..., T-1 \srlab{Dynamic model on $\alpha_{t}$} \\
\alpha_{T} &\sim \mathrm{Normal}(\alpha_{T-1}, \tau) \srlab{Adaptive prior on $\alpha_{T}$} \\
\delta_{j} &\sim \mathrm{Normal}(0, 0.1) \text{ for } j \text{ in } 1, ..., J \srlab{Prior on house effects, $\delta$} \\
\omega_{t} &\sim \mathrm{Normal}(0, 0.1) \text{ for } t \text{ in } 1, ..., T-1 \srlab{Prior on random shocks, $\omega$} \\
\tau &\sim \mathrm{Normal}(0, 0.05)^{+} \srlab{Positive prior on scale of innovations, $\tau$} \\
\sigma &\sim \mathrm{Exponential}(20) \srlab{Prior on residual error, $\sigma$} \\
\end{align*}

Model pinned at both ends and includes only one set of polling figures -- loop over each pair of elections and each party between 1955 and the present day.

## Validating Our Estimates

```{r val-plot, fig.cap = "Estimates for each party from the pollbasepro data appear well-validated against raw polling data from Jennings and Wlezien's 'Timeline of Elections' dataset (2016).", fig.width = 6, fig.height = 2.5, fig.align = "centre", echo = F}

# Define party colours

pty_cols <-
  c(
    "Conservative Party" = "#0087dc",
    "Labour Party" = "#d50000",
    "Liberals (Various Forms)" = "#fdbb30"
  )

# Load Timeline data, filter to include only UK cases, and split by party

tl <-
  readRDS(here("inst", "extdata", "timeline.rds")) %>%
  select(
    date = polldate,
    elecdate,
    country,
    party = partyid,
    vote = poll_
  ) %>%
  filter(country == "United Kingdom") %>%
  mutate(
    vote = vote/100,
    party = case_when(party == 1 ~ "con", party == 2 ~ "lab", party == 3 ~ "lib"),
    polldate = as_date(date)
  ) %>%
  na.omit()

con <-
  tl %>%
  filter(party == "con") %>%
  left_join(
    pollbasepro,
    c("polldate" = "date")
  ) %>%
  na.omit()

lab <-
  tl %>%
  filter(party == "lab") %>%
  left_join(
    pollbasepro,
    c("polldate" = "date")
  ) %>%
  na.omit()

lib <-
  tl %>%
  filter(party == "lib") %>%
  left_join(
    pollbasepro,
    c("polldate" = "date")
  ) %>%
  na.omit()

# Create correlation plot

ggplot() +
  geom_density_2d(
    data = con %>% mutate(facet = "Conservative"),
    mapping = aes(x = vote, y = con_est),
    colour = pty_cols[1],
    alpha = .4
  ) +
  stat_smooth(
    data = con %>% mutate(facet = "Conservative"),
    mapping = aes(x = vote, y = con_est),
    colour = "black",
    fill = pty_cols[1],
    method = "lm",
    formula = y ~ x
  ) +
  # geom_text(
  #   data = con %>% mutate(facet = "Conservative"),
  #   mapping = 
  #     aes(
  #       x = .6,
  #       y = .05,
  #       label = 
  #         paste0(
  #           in_text(pluck(posterior_samples(cor_con, "rescor"), 1)*100, suffix = "%", inside = F),
  #           "\n",
  #           "MAE = ", round(mae(cor_con$data$con_est, cor_con$data$vote), 2),
  #           ", RMSE = ", round(rmse(cor_con$data$con_est, cor_con$data$vote), 2)
  #           )
  #       ),
  #   hjust = 1,
  #   size = 2,
  #   family = "Cabin Regular"
  # ) +
  geom_density_2d(
    data = lab %>% mutate(facet = "Labour"),
    mapping = aes(x = vote, y = lab_est),
    colour = pty_cols[2],
    alpha = .4
  ) +
  stat_smooth(
    data = lab %>% mutate(facet = "Labour"),
    mapping = aes(x = vote, y = lab_est),
    colour = "black",
    fill = pty_cols[2],
    method = "lm",
    formula = y ~ x
  ) +
  # geom_text(
  #   data = lab %>% mutate(facet = "Labour"),
  #   mapping = 
  #     aes(
  #       x = .6,
  #       y = .05,
  #       label = 
  #         paste0(
  #           in_text(pluck(posterior_samples(cor_lab, "rescor"), 1)*100, suffix = "%", inside = F),
  #           "\n",
  #           "MAE = ", round(mae(cor_lab$data$lab_est, cor_lab$data$vote), 2),
  #           ", RMSE = ", round(rmse(cor_lab$data$lab_est, cor_lab$data$vote), 2)
  #           )
  #     ),
  #   hjust = 1,
  #   size = 2,
  #   family = "Cabin Regular"
  # ) +
  geom_density_2d(
    data = lib %>% mutate(facet = "Liberal (Various Forms)"),
    mapping = aes(x = vote, y = lib_est),
    colour = pty_cols[3],
    alpha = .4
  ) +
  stat_smooth(
    data = lib %>% mutate(facet = "Liberal (Various Forms)"),
    mapping = aes(x = vote, y = lib_est),
    colour = "black",
    fill = pty_cols[3],
    method = "lm",
    formula = y ~ x
  ) +
  # geom_text(
  #   data = lib %>% mutate(facet = "Liberal (Various Forms)"),
  #   mapping = 
  #     aes(
  #       x = .6,
  #       y = .05,
  #       label = 
  #         paste0(
  #           in_text(pluck(posterior_samples(cor_lib, "rescor"), 1)*100, suffix = "%", inside = F),
  #           "\n",
  #           "MAE = ", round(mae(cor_lib$data$lib_est, cor_lib$data$vote), 2),
  #           ", RMSE = ", round(rmse(cor_lib$data$lib_est, cor_lib$data$vote), 2)
  #           )
  #     ),
  #   hjust = 1,
  #   size = 2,
  #   family = "Cabin Regular"
  # ) +
  facet_wrap(~ facet) +
  scale_y_continuous(
    breaks = seq(0, .6, by = .2),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_x_continuous(
    breaks = seq(0, .6, by = .2),
    labels = scales::percent_format(accuracy = 1)
  ) +
  coord_cartesian(
    ylim = c(0, 0.62),
    xlim = c(0, 0.62)
  ) +
  labs(x = "Jennings and Wlezien's 'Timeline of Elections' Data", y = "PollBasePro Estimates") +
  theme_bailey()
```

To validate our estimates, we compare them against raw polling data from Jennings and Wlezien's "Timeline of Elections" dataset [-@jennings2016a]. These data contain `r format(nrow(timeline[timeline$party == 1, ]), big.mark = ",")` polls from Britain between `r str_remove(format(min(as_date(timeline$date)), "%d %B %Y"), "^0")` and `r str_remove(format(max(as_date(timeline$date)), "%d %B %Y"), "^0")`. Given that the data we use to produce our estimates are so comprehensive, it is likely that most polls appear in both datasets. Still, the Timeline data provide a good test as Jennings and Wlezien compiled them independently. As figure \@ref(fig:val-plot) shows, our estimates are well validated. Correlations between the two series are strong and positive, as we would expect. Their mean absolute error (MAE) and root-mean-square error (RMSE) are also low in all cases. The Conservatives showed a correlation of `r in_text(pluck(posterior_samples(cor_con, "rescor"), 1)*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(mae(cor_con$data$con_est*100, cor_con$data$vote*100), 2), " percentage points")`, and an RMSE of `r round(rmse(cor_con$data$con_est, cor_con$data$vote), 2)`; Labour, a correlation of `r in_text(pluck(posterior_samples(cor_lab, "rescor"), 1)*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(mae(cor_lab$data$lab_est*100, cor_lab$data$vote*100), 2), " points")`, and an RMSE of `r round(rmse(cor_lab$data$lab_est, cor_lab$data$vote), 2)`; and the Liberals, a correlation of `r in_text(pluck(posterior_samples(cor_lib, "rescor"), 1)*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(mae(cor_lib$data$lib_est*100, cor_lib$data$vote*100), 2), " points")`, and an RMSE of `r round(rmse(cor_lib$data$lib_est, cor_lib$data$vote), 2)`.

## Open-Source Data Pipeline

We recognise that some users will find understanding our modelling decisions more simple if they were able to see our code^[Note that we estimate all of our models using `R` `r str_remove(R.Version()$version.string, "^R*.")` and either version `r packageVersion("brms")` of the `brms` package [@burkner2017] or version `r cmdstanr::cmdstan_version()` of `cmdstan`, an interface to the Stan probabilistic programming language [@carpenter2017]]. This transparency also has other benefits: it allows our users to identify mistakes in our code. After all---and like any project of this nature---our data pipeline likely contains minor errors or inefficiencies that could affect the estimates that we obtain. To guard against this, and provide our users with a more in-depth look at our modelling process, we have hosted our entire data pipeline online for others to inspect. If our users find any errors in our code or wish to make recommendations for future updates, we invite them to raise an issue on the project's GitHub repository or to contact the authors directly.

\pagebreak

# Variable List: PollBase (Historical British Election Polls from `r format(min(pollbase$start), "%Y")` to `r format(max(pollbase$end), "%Y")`)

```{r pollbase-details, echo = F}

make_table(pollbase)

```

\pagebreak

# Variable List: PollBasePro (Daily British Voting Intention from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")`)

```{r pollbasepro-details, echo = F}

make_table(pollbasepro)

```

\pagebreak

# Change Log

For the sake of openness and transparency, we provide a change log that lists all updates and changes made to the PollBasePro datasets and documentation over time. If you think that you have found a problem with either, please raise an issue on the project's GitHub repository.

```{r change-log, echo = FALSE, message = FALSE, results = "asis"}

# Read change log

change_log <- readLines(here("documentation", "change-log.txt"), warn = F)

# Output change log

cat(paste0(change_log, collapse = "\n"))

```

\pagebreak

# References

::: {#refs}

:::

```{r session-info, include = FALSE, echo = F}

# Save session information to the "sessions" folder

save_info(path = here("sessions", "007_codebook.txt"))

```

### 2021-03-12 R/fit_model.R

@@ -1,0 +1,158 @@
+#' Fit Poll Pooling Model
+#'
+#' This function provides a simple way to fit a variant of Simon Jackman's "polling the polls" model.
+#'
+#' @param data Raw pollbase data.
+#' @param init Initial election date.
+#' @param final Final election date.
+#' @param party A string reflecting a party. Either "con", "lab", or "lib".
+#' @param alpha_init The party's vote share at the initial election.
+#' @param alpha_final The party's vote share at the final election.
+#' @export
+
+fit_model <- function(data, init, final, party, alpha_init, alpha_final){
+
+  # Get pipe from Magrittr
+
+  `%>%` <- magrittr::`%>%`
+
+
+  # Print party and election
+
+  print(paste0("Fitting model: ", party, " ", init))
+
+
+  # Subset data
+
+  data <- data[data$election == init, ]
+
+
+  # Run model
+
+  if(init < "2019-12-12"){
+
+    # Compile Stan model
+
+    model <-
+      cmdstanr::cmdstan_model(
+        here::here("models", "model_2anchors.stan"),
+        cpp_options = list(stan_threads = TRUE)
+      )
+
+
+    # Create data for Stan
+
+    stan_data <-
+      list(
+        N = nrow(data),
+        T = (lubridate::interval(init, final)/lubridate::days(1)) + 1,
+        P = length(unique(data$pollster)),
+        y = data[[party]],
+        s = sqrt((data[[party]]*(1 - data[[party]]))/(ifelse(is.na(data$n) == T, data$n_est, data$n)/data$days)),
+        index = data$index,
+        pollster = as.numeric(factor(data$pollster)),
+        alpha_init = alpha_init,
+        alpha_final = alpha_final
+      )
+
+
+    # Sample from model
+
+    fit <-
+      model$sample(
+        data = stan_data,
+        seed = 666,
+        chains = 4,
+        parallel_chains = 4,
+        threads_per_chain = 3,
+        refresh = 0,
+        show_messages = FALSE,
+        init =
+          list(
+            list(alpha = rep(alpha_init, nrow(data))),
+            list(alpha = rep(alpha_init, nrow(data))),
+            list(alpha = rep(alpha_init, nrow(data))),
+            list(alpha = rep(alpha_init, nrow(data)))
+          ),
+        adapt_delta = 0.99,
+        max_treedepth = 15
+      )
+
[…]

### 2021-03-12 R/get_2015_polls.R

@@ -1,0 +1,202 @@
+#' Get Voting Intention Polls, 2010-2015
+#'
+#' This function downloads and tidies polling data for the 2010 to 2015 period from Wikipedia.
+#'
+#' @export
+
+get_2015_polls <- function(){
+
+  # Get pipe from Magrittr
+
+  `%>%` <- magrittr::`%>%`
+
+
+  # We'll get the data we need from Wikipedia. This is useful because there
+  # are a whole host of people who keep these pages up to date and it means
+  # that we don't have to manage data collection ourselves.
+
+  url1 <- "https://en.wikipedia.org/wiki/Opinion_polling_for_the_2015_United_Kingdom_general_election_(2010–2012)"
+  url2 <- "https://en.wikipedia.org/wiki/Opinion_polling_for_the_2015_United_Kingdom_general_election"
+
+
+  # Now, we'll use the htmltab() function to scrape the contents of the tables
+  # on the page.
+
+  dta_10 <-
+    htmltab::htmltab(url1, 3) %>%
+    dplyr::select(
+      date = `Date(s)conducted`,
+      pollster = `Polling organisation/client`,
+      n = `Sample size`,
+      con = Con,
+      lab = Lab,
+      lib = `Lib Dem`
+    ) %>%
+    dplyr::mutate(date = paste(date, "2010"))
+
+  dta_11 <-
+    htmltab::htmltab(url1, 2) %>%
+    dplyr::select(
+      date = `Date(s)conducted`,
+      pollster = `Polling organisation/client`,
+      n = `Sample size`,
+      con = Con,
+      lab = Lab,
+      lib = `Lib Dem`
+    ) %>%
+    dplyr::mutate(date = paste(date, "2011"))
+
+  dta_12 <-
+    htmltab::htmltab(url1, 1) %>%
+    dplyr::select(
+      date = `Date(s)conducted`,
+      pollster = `Polling organisation/client`,
+      n = `Sample size`,
+      con = Con,
+      lab = Lab,
+      lib = `Lib Dem`
+    ) %>%
+    dplyr::mutate(date = paste(date, "2012"))
+
+  dta_13 <-
+    htmltab::htmltab(url2, 5) %>%
+    dplyr::select(
+      date = `Date(s)conducted`,
+      pollster = `Polling organisation/client`,
+      n = `Sample size`,
+      con = Con,
+      lab = Lab,
+      lib = `Lib Dem`
+    ) %>%
+    dplyr::mutate(date = paste(date, "2013"))
+
+  dta_14 <-
[…]

### 2021-03-12 R/get_2017_polls.R

@@ -1,0 +1,165 @@
+#' Get Voting Intention Polls, 2015-2017
+#'
+#' This function downloads and tidies polling data for the 2015 to 2017 period from Wikipedia.
+#'
+#' @export
+
+get_2017_polls <- function(){
+
+  # Get pipe from Magrittr
+
+  `%>%` <- magrittr::`%>%`
+
+
+  # We'll get the data we need from Wikipedia. This is useful because there
+  # are a whole host of people who keep these pages up to date and it means
+  # that we don't have to manage data collection ourselves.
+
+  url <- "https://en.wikipedia.org/wiki/Opinion_polling_for_the_2017_United_Kingdom_general_election"
+
+
+  # Now, we'll use the htmltab() function to scrape the contents of the tables
+  # on the page.
+
+  dta_15 <-
+    htmltab::htmltab(url, 4) %>%
+    dplyr::select(
+      date = `Date(s)conducted`,
+      pollster = `Polling organisation/client`,
+      n = `Sample size`,
+      con = Con,
+      lab = Lab,
+      lib = `Lib Dem`
+    ) %>%
+    dplyr::mutate(date = paste(date, "2015"))
+
+  dta_16 <-
+    htmltab::htmltab(url, 3) %>%
+    dplyr::select(
+      date = `Date(s)conducted`,
+      pollster = `Polling organisation/client`,
+      n = `Sample size`,
+      con = Con,
+      lab = Lab,
+      lib = `Lib Dem`
+    ) %>%
+    dplyr::mutate(date = paste(date, "2016"))
+
+  dta_17 <-
+    htmltab::htmltab(url, 2) %>%
+    dplyr::select(
+      date = `Date(s)conducted`,
+      pollster = `Polling organisation/client`,
+      n = `Sample size`,
+      con = Con,
+      lab = Lab,
+      lib = `Lib Dem`
+    ) %>%
+    dplyr::mutate(date = paste(date, "2017"))
+
+
+  # Now we'll merge the data together
+
+  dta <- rbind(dta_15, dta_16, dta_17)
+
+
+  # At the moment, the data contain rows that include only information on the
+  # events that came to pass in UK politics. We don't need these, so we will
+  # remove them from the data.
+
+  dta <-
+    dta %>%
+    dplyr::filter(!(pollster == con))
+
+
+  # We'll also remove the actual election results themselves.
+
+  dta <-
+    dta %>%
[…]

### 2021-03-12 R/get_2019_polls.R

@@ -1,0 +1,165 @@
+#' Get Voting Intention Polls, 2017-2019
+#'
+#' This function downloads and tidies polling data for the 2017 to 2019 period from Wikipedia.
+#'
+#' @export
+
+get_2019_polls <- function(){
+
+  # Get pipe from Magrittr
+
+  `%>%` <- magrittr::`%>%`
+
+
+  # We'll get the data we need from Wikipedia. This is useful because there
+  # are a whole host of people who keep these pages up to date and it means
+  # that we don't have to manage data collection ourselves.
+
+  url <- "https://en.wikipedia.org/wiki/Opinion_polling_for_the_2019_United_Kingdom_general_election"
+
+
+  # Now, we'll use the htmltab() function to scrape the contents of the tables
+  # on the page.
+
+  dta_17 <-
+    htmltab::htmltab(url, 4) %>%
+    dplyr::select(
+      date = `Date(s)conducted`,
+      pollster = `Pollster/client(s)`,
+      n = `Samplesize`,
+      con = Con,
+      lab = Lab,
+      lib = `Lib Dem`
+    ) %>%
+    dplyr::mutate(date = paste(date, "2017"))
+
+  dta_18 <-
+    htmltab::htmltab(url, 3) %>%
+    dplyr::select(
+      date = `Date(s)conducted`,
+      pollster = `Pollster/client(s)`,
+      n = `Samplesize`,
+      con = Con,
+      lab = Lab,
+      lib = `Lib Dem`
+    ) %>%
+    dplyr::mutate(date = paste(date, "2018"))
+
+  dta_19 <-
+    htmltab::htmltab(url, 2) %>%
+    dplyr::select(
+      date = `Date(s)conducted`,
+      pollster = `Pollster/client(s)`,
+      n = `Samplesize`,
+      con = Con,
+      lab = Lab,
+      lib = `Lib Dem`
+    ) %>%
+    dplyr::mutate(date = paste(date, "2019"))
+
+
+  # Now we'll merge the data together
+
+  dta <- rbind(dta_17, dta_18, dta_19)
+
+
+  # At the moment, the data contain rows that include only information on the
+  # events that came to pass in UK politics. We don't need these, so we will
+  # remove them from the data.
+
+  dta <-
+    dta %>%
+    dplyr::filter(!(pollster == con))
+
+
+  # We'll also remove the actual election results themselves.
+
+  dta <-
+    dta %>%
+    dplyr::filter(stringr::str_detect(pollster, "election|Election") == F)
+
+
[…]

### 2021-03-12 R/get_last_election.R

@@ -1,0 +1,48 @@
+#' Get Previous Election Based on Date
+#'
+#' Given a vector of dates, this function provides a vector of the same length that corresponds to the date of the last election for each element in the vector. Applies only to the 1935 election onwards.
+#'
+#' @param x A vector of dates.
+#' @export
+
+get_last_election <- function(x){
+
+  # Get date
+
+  x <- dplyr::case_when(
+    x >= "1935-11-14" & x < "1945-07-05" ~ "1935-11-14",
+    x >= "1945-07-05" & x < "1950-02-23" ~ "1945-07-05",
+    x >= "1950-02-23" & x < "1951-10-25" ~ "1950-02-23",
+    x >= "1951-10-25" & x < "1955-05-26" ~ "1951-10-25",
+    x >= "1955-05-26" & x < "1959-10-08" ~ "1955-05-26",
+    x >= "1959-10-08" & x < "1964-10-15" ~ "1959-10-08",
+    x >= "1964-10-15" & x < "1966-03-31" ~ "1964-10-15",
+    x >= "1966-03-31" & x < "1970-06-18" ~ "1966-03-31",
+    x >= "1970-06-18" & x < "1974-02-28" ~ "1970-06-18",
+    x >= "1974-02-28" & x < "1974-10-10" ~ "1974-02-28",
+    x >= "1974-10-10" & x < "1979-05-03" ~ "1974-10-10",
+    x >= "1979-05-03" & x < "1983-06-09" ~ "1979-05-03",
+    x >= "1983-06-09" & x < "1987-06-11" ~ "1983-06-09",
+    x >= "1987-06-11" & x < "1992-04-09" ~ "1987-06-11",
+    x >= "1992-04-09" & x < "1997-05-01" ~ "1992-04-09",
+    x >= "1997-05-01" & x < "2001-06-07" ~ "1997-05-01",
+    x >= "2001-06-07" & x < "2005-05-05" ~ "2001-06-07",
+    x >= "2005-05-05" & x < "2010-05-06" ~ "2005-05-05",
+    x >= "2010-05-06" & x < "2015-05-07" ~ "2010-05-06",
+    x >= "2015-05-07" & x < "2017-06-08" ~ "2015-05-07",
+    x >= "2017-06-08" & x < "2019-12-12" ~ "2017-06-08",
+    x >= "2019-12-12" ~ "2019-12-12",
+  )
+
+
+  # Convert to date format
+
[…]

### 2021-03-12 R/get_new_polls.R

@@ -1,0 +1,153 @@
+#' Get Voting Intention Polls, 2019-Present
+#'
+#' This function downloads and tidies polling data for the 2019-Present period from Wikipedia.
+#'
+#' @export
+
+get_new_polls <- function(){
+
+  # Get pipe from Magrittr
+
+  `%>%` <- magrittr::`%>%`
+
+
+  # We'll get the data we need from Wikipedia. This is useful because there
+  # are a whole host of people who keep these pages up to date and it means
+  # that we don't have to manage data collection ourselves.
+
+  url <- "https://en.wikipedia.org/wiki/Opinion_polling_for_the_next_United_Kingdom_general_election"
+
+
+  # Now, we'll use the htmltab() function to scrape the contents of the tables
+  # on the page.
+
+  dta_20 <-
+    htmltab::htmltab(url, 3) %>%
+    dplyr::select(
+      date = Datesconducted,
+      pollster = Pollster,
+      n = Samplesize,
+      con = Con,
+      lab = Lab,
+      lib = `Lib Dem`
+    ) %>%
+    dplyr::mutate(date = paste(date, "2020"))
+
+  dta_21 <-
+    htmltab::htmltab(url, 2) %>%
+    dplyr::select(
+      date = Datesconducted,
+      pollster = Pollster,
+      n = Samplesize,
+      con = Con,
+      lab = Lab,
+      lib = `Lib Dem`
+    ) %>%
+    dplyr::mutate(date = paste(date, "2021"))
+
+
+  # Now we'll merge the data together
+
+  dta <- rbind(dta_20, dta_21)
+
+
+  # At the moment, the data contain rows that include only information on the
+  # events that came to pass in UK politics. We don't need these, so we will
+  # remove them from the data.
+
+  dta <-
+    dta %>%
+    dplyr::filter(!(pollster == con))
+
+
+  # We'll also remove the actual election results themselves.
+
+  dta <-
+    dta %>%
+    dplyr::filter(stringr::str_detect(pollster, "election|Election") == F)
+
+
+  # Likewise we'll remove the clients from the pollster column and
+  # convert the pollsters to lower case
+
+  dta <-
+    dta %>%
+    dplyr::mutate(
+      pollster =
+        pollster %>%
+        stringr::str_remove("/.*") %>%
+        stringr::str_remove("-|\u2014") %>%
+        tolower()
+    )
+
+
[…]

### 2021-03-12 R/get_result.R

@@ -1,0 +1,94 @@
+#' Get Election Result Based on Party and Election
+#'
+#' Given a vector of dates, this function provides a vector of the same length that corresponds to the date of the last election for each element in the vector. Applies only to the 1935 election onwards.
+#'
+#' @param election A date corresponding to a UK election.
+#' @param party A string reflecting a party. Either "con", "lab", or "lib".
+#' @export
+
+get_result <- function(election = "1997-05-01", party = "lab"){
+
+  # Get date
+
+  result <- dplyr::case_when(
+    # 1955
+    election == "1955-05-26" & party == "con" ~ 49.3/100,
+    election == "1955-05-26" & party == "lab" ~ 47.4/100,
+    election == "1955-05-26" & party == "lib" ~ 2.8/100,
+    # 1959
+    election == "1959-10-08" & party == "con" ~ 48.8/100,
+    election == "1959-10-08" & party == "lab" ~ 44.6/100,
+    election == "1959-10-08" & party == "lib" ~ 6.0/100,
+    # 1964
+    election == "1964-10-15" & party == "con" ~ 42.9/100,
+    election == "1964-10-15" & party == "lab" ~ 44.8/100,
+    election == "1964-10-15" & party == "lib" ~ 11.4/100,
+    # 1966
+    election == "1966-03-31" & party == "con" ~ 41.4/100,
+    election == "1966-03-31" & party == "lab" ~ 48.8/100,
+    election == "1966-03-31" & party == "lib" ~ 8.6/100,
+    # 1970
+    election == "1970-06-18" & party == "con" ~ 46.2/100,
+    election == "1970-06-18" & party == "lab" ~ 43.8/100,
+    election == "1970-06-18" & party == "lib" ~ 7.6/100,
+    # 1974 Feb
+    election == "1974-02-28" & party == "con" ~ 38.6/100,
+    election == "1974-02-28" & party == "lab" ~ 38.0/100,
+    election == "1974-02-28" & party == "lib" ~ 19.8/100,
+    # 1974 Oct
+    election == "1974-10-10" & party == "con" ~ 36.6/100,
+    election == "1974-10-10" & party == "lab" ~ 40.2/100,
+    election == "1974-10-10" & party == "lib" ~ 18.8/100,
+    # 1979
+    election == "1979-05-03" & party == "con" ~ 44.9/100,
[…]

### 2021-03-12 R/global.R

@@ -1,0 +1,38 @@
+utils::globalVariables(
+  c(
+    "con",
+    "con_ldr",
+    "election",
+    "end",
+    "govt",
+    "id",
+    "lab",
+    "lab_ldr",
+    "lib",
+    "lib_ldr",
+    "n",
+    "pollster",
+    "start",
+    "con_err",
+    "con_est",
+    "date",
+    "lab_err",
+    "lab_est",
+    "week",
+    "month",
+    "quarter",
+    "year",
+    "sd",
+    "Date(s)conducted",
+    "Polling organisation/client",
+    "Sample size",
+    "Con",
+    "Lab",
+    "Lib Dem",
+    "Pollster/client(s)",
+    "Samplesize",
+    "Datesconducted",
+    "Pollster",
+    "variable"
+    )
+)

### 2021-03-12 R/mae.R

@@ -1,0 +1,13 @@
+#' Mean Absolute Error
+#'
+#' This function provides a simple way to compute MAE.
+#'
+#' @param y1 A numeric vector.
+#' @param y2 A numeric vector.
+#'
+#' @export
+
+mae <- function(y1, y2){
+  mean(abs(y1 - y2))
+}
+

### 2021-03-12 R/make_table.R

@@ -1,0 +1,61 @@
+#' Generate Variable Tables
+#'
+#' Provided a data frame of labelled vectors, this function returns a formatted summary table.
+#'
+#' @param data A data frame of labelled vectors
+#' @export
+
+make_table <- function(data = NULL){
+
+  # Get pipe from Magrittr
+
+  `%>%` <- magrittr::`%>%`
+
+
+  # Get list of variable names
+
+  var_names <- paste0("\\texttt{" , stringr::str_replace(names(data), "_", "\\\\_"), "}")
+
+
+  # Get list of variable labels
+
+  var_labels <- paste0(unlist(labelled::var_label(data)))
+
+
+  # Convert to a data frame
+
+  var_dta <-
+    data.frame(
+      `Name` = var_names,
+      `Description` = var_labels
+    )
+
+
+  # Make data frame names use sans font
+
+  names(var_dta) <- paste0("\\textsf{\\textbf{" , names(var_dta), "}}")
+
+
+  # Convert to latex table
+
+  var_tab <-
+    kableExtra::kable(
+      var_dta,
+      align = "ll",
+      format = "latex",
+      booktabs = TRUE,
+      escape = FALSE,
+      linesep = ""
+    ) %>%
+    kableExtra::kable_styling(
+      position = "center",
+      latex_options = "hold_position"
+    )
+
+
+  # Return table to user
+
+  return(var_tab)
+
+}
+

### 2021-03-12 R/pollbase.R

@@ -1,0 +1,21 @@
+#' Raw PollBase data in long-format
+#'
+#' A dataset containing Mark Pack's raw pollbase figures for each of Britain's three main parties, tidied and converted to long-format for easy analysis.
+#'
+#' @format A data frame with 6,124 rows and 12 variables:
+#' \describe{
+#'   \item{id}{Unique poll identification number}
+#'   \item{election}{Date of last general election}
+#'   \item{govt}{Largest party in government after the last general election}
+#'   \item{start}{First day of fieldwork}
+#'   \item{end}{Last day of fieldwork}
+#'   \item{pollster}{Polling company that conducted the poll}
+#'   \item{n}{Sample size}
+#'   \item{con}{Voting intention: Conservative}
+#'   \item{lab}{Voting intention: Labour}
+#'   \item{lib}{Voting intention: Liberal}
+#'   \item{con_ldr}{Leader of the Conservative Party}
+#'   \item{lab_ldr}{Leader of the Labour Party}
+#'   \item{lib_ldr}{Leader of the Liberals (various forms)}
+#' }
+"pollbase"

### 2021-03-12 R/pollbasepro.R

@@ -1,0 +1,24 @@
+#' Daily Estimates of British Voting Intention, 1955 to Present
+#'
+#' A dataset containing daily estimates of aggregate voting intention in Britain for each of the country's three largest parties between 1955 and the present.
+#'
+#' @format A data frame with 23,577 rows and 15 variables:
+#' \describe{
+#'   \item{date}{Date}
+#'   \item{election}{Date of last general election}
+#'   \item{govt}{Largest party in government after the last general election}
+#'   \item{con_est}{Posterior mean: Conservative voting intention}
+#'   \item{con_err}{Posterior error: Conservative voting intention}
+#'   \item{lab_est}{Posterior mean: Labour voting intention}
+#'   \item{lab_err}{Posterior error: Labour voting intention}
+#'   \item{lib_est}{Posterior mean: Liberal voting intention}
+#'   \item{lib_err}{Posterior error: Liberal voting intention}
+#'   \item{con_ldr}{Leader of the Conservative Party}
+#'   \item{lab_ldr}{Leader of the Labour Party}
+#'   \item{lib_ldr}{Leader of the Liberals (various forms)}
+#'   \item{week}{Weekly subset indicator}
+#'   \item{month}{Monthly subset indicator}
+#'   \item{quarter}{Quarterly subset indicator}
+#'   \item{year}{Yearly subset indicator}
+#' }
+"pollbasepro"

### 2021-03-12 R/rmse.R

@@ -1,0 +1,13 @@
+#' Root-Mean-Square Error
+#'
+#' This function provides a simple way to compute RMSE.
+#'
+#' @param y1 A numeric vector.
+#' @param y2 A numeric vector.
+#'
+#' @export
+
+rmse <- function(y1, y2){
+  sqrt(sum(((y1 - y2)^2)/length(y1)))
+}
+

### 2021-03-12 R/save_info.R

@@ -1,0 +1,20 @@
+#' Quicky and Easy Session Info .txt Files
+#'
+#' This function provides a simple way to export session information.
+#'
+#' @param path The file path to where you would like to save your session information.
+#' @examples
+#' \dontrun{
+#' save_info()
+#' }
+#' @export
+
+save_info <- function(path = "session_info.txt"){
+
+  sink(file = path)
+  cat(paste0("Analysis completed: ", Sys.time(), "\n\n"))
+  print(utils::sessionInfo())
+  sink()
+
+}
+

### 2021-03-12 R/update_pollbasepro.R

@@ -1,0 +1,488 @@
+#' Update Voting Intention Polls, 2019-Present
+#'
+#' This function updates PollBasePro to include the latest polling data and outputs Twitter content.
+#'
+#'
+#' @export
+
+update_pollbasepro <- function(){
+
+  # Get pipe from Magrittr
+
+  `%>%` <- magrittr::`%>%`
+
+
+  # Make list object
+
+  dta <-
+    tibble::tibble(
+      init = "2019-12-12",
+      final = NA,
+      con = NA,
+      lab = NA,
+      lib = NA
+    ) %>%
+    tidyr::pivot_longer(
+      cols = c(con, lab, lib),
+      names_to = "party",
+      values_to = "estimates"
+    ) %>%
+    dplyr::mutate(
+      alpha_init = PollBasePro::get_result(election = init, party = party),
+      alpha_final = NA,
+      estimates = as.list(rep(NA, dplyr::n()))
+    )
+
+
+  # Get wiki data and mutate
+
+  wiki <-
+    PollBasePro::get_new_polls() %>%
+    dplyr::mutate(
+      election = "2019-12-12",
+      id =
+        paste0(
+          "poll-",
+          seq(
+            as.numeric(
+              stringr::str_remove(
+                PollBasePro::pollbase$id[PollBasePro::pollbase$end > "2019-12-12"][1], ".*-"
+              )
+            ),
+            as.numeric(
+              stringr::str_remove(
+                PollBasePro::pollbase$id[PollBasePro::pollbase$end > "2019-12-12"][1], ".*-"
+              )
+            ) + nrow(.) - 1,
+            by = 1
+          )
+        ),
+      days =
+        lubridate::interval(start, end) %>%
+        magrittr::divide_by(lubridate::days(1)) %>%
+        magrittr::add(1)
+    ) %>%
+    tidyr::uncount(days) %>%
+    dplyr::group_by(id) %>%
+    dplyr::mutate(
+      date = lubridate::`%m+%`(start, lubridate::days(dplyr::row_number() - 1)),
+      days = dplyr::n()
+    ) %>%
+    dplyr::ungroup() %>%
+    dplyr::select(-start, -end) %>%
+    dplyr::mutate(
+      index = (lubridate::interval(election, date)/lubridate::days(1)) + 1
+    ) %>%
+    dplyr::select(
+      id,
+      days,
+      election,
+      date,
+      pollster,
+      n,
+      con,
[…]

### 2021-03-12 data-raw/000_compile.R

@@ -1,0 +1,79 @@
+
+# Compile PollBasePro
+
+# 1. Housekeeping ---------------------------------------------------------
+
+# Load packages
+
+library(PollBasePro)
+library(rmarkdown)
+library(here)
+
+
+
+# 2. Compile data and models ----------------------------------------------
+
+# Fit sample size imputation model
+
+source(here("data-raw", "001_samplesizes.R"))
+
+
+# Format raw pollbase data
+
+source(here("data-raw", "002_pollbase.R"))
+
+
+# Derive daily pollbasepro estimates
+
+source(here("data-raw", "003_pollbasepro.R"))
+
+
+# Validate the resulting estimates
+
+source(here("data-raw", "004_validation.R"))
+
+
+# Use data to fit applied example model for the paper
+
+source(here("data-raw", "005_example.R"))
+
+
+
+# 3. Compile documentation ------------------------------------------------
+
+# Render paper
+
+render(
+  input = here("documentation", "paper.Rmd"),
+  output_file = here("download", paste0("paper_", packageVersion("PollBasePro"), ".pdf"))
+)
+
+
+# Generate random cover image
+
+source(here("documentation", "_assets", "cover.R"))
+
+
+# Render user guide and codebook
+
+render(
+  input = here("documentation", "userguide.Rmd"),
+  output_file = here("download", paste0("userguide_", packageVersion("PollBasePro"), ".pdf"))
+)
+
+
+# Render GitHub README file
+
+render(
+  input = here("documentation", "readme.Rmd"),
+  output_file = here("download", "README.md")
+)
+
+
+
+# 4. Produce replication materials ----------------------------------------
+
+# Save session information to the "sessions" folder
+
+save_info(path = here("sessions", "000_compile.txt"))
+

### 2021-03-12 data-raw/001_samplesizes.R

@@ -1,0 +1,172 @@
+
+# Impute missing sample sizes
+
+
+# 1. Housekeeping ---------------------------------------------------------
+
+# Load packages
+
+library(PollBasePro)
+library(tidyverse)
+library(lubridate)
+library(brms)
+library(here)
+
+
+# Load timeline of elections data
+
+timeline <-
+  readRDS(here("inst", "extdata", "timeline.rds")) %>%
+  select(
+    polldate,
+    elecdate,
+    country,
+    sample
+  ) %>%
+  na.omit()
+
+
+
+# 2. Transform data -------------------------------------------------------
+
+# The data transformation here is pretty limited. All we need to do is to
+# create a timing variable that counts up from some date. We'll count up
+# from 1950-01-01 and scale the variable by decade so that it's easier for
+# the model to handle.
+
+timeline <-
+  timeline %>%
+  mutate(
+    time = interval(as_date("1950-01-01"), as_date(polldate))/years(10)
+  )
+
+
+# There are a few cases that have absurdly large sample sizes, likely due
+# to including MRP polls, etc. We'll make the decision here to remove any
+# cases with sample sizes over 10k, which probably don't reflect the sample
+# sizes of a typical poll and serve to bias upwards later sample estimates.
+
+timeline <-
+  timeline %>%
+  filter(sample < 10000)
+
+
+# Likewise, there are many cases where the sample size seems to have been
+# input as 1000 in the absence of any other information. As we can't tell
+# which are real and which are not, we'll remove all of them.
+
+timeline <-
+  timeline %>%
+  filter(
+    sample != 1000,
+    sample != 0
+  )
+
+
+# We also need to subset the data to include only distinct cases, as each
+# is currently repeated three times -- one for each of the UK's three
+# main parties.
+
+timeline <-
+  timeline %>%
+  distinct()
+
+
+# Finally, there are some countries that have only a handful of cases. These
+# cause issues when fitting the model, so we'll also get rid of any that
+# have less than 100 cases.
+
+timeline <-
+  timeline %>%
+  group_by(country) %>%
+  add_count() %>%
+  ungroup() %>%
+  filter(n >= 100) %>%
+  select(-n)
+
+
+
+# 3. Fit model and impute sample sizes ------------------------------------
+
+# We'll now fit our model. As the sample size data are counts, we'll model
+# them as poisson-distributed according to some constant and some spline
[…]

### 2021-03-12 data-raw/002_pollbase.R

@@ -1,0 +1,674 @@
+
+# Compile long-format PollBase data
+
+
+# 1. Housekeeping ---------------------------------------------------------
+
+# Load packages
+
+library(PollBasePro)
+library(tidyverse)
+library(magrittr)
+library(lubridate)
+library(labelled)
+library(janitor)
+library(readxl)
+library(jbmisc)
+library(haven)
+library(here)
+
+
+# Get index of first sheet to start with a number
+
+start <-
+  here("inst", "extdata", "PollBase-Q4-2020.xlsx") %>%
+  excel_sheets() %>%
+  str_detect("^[:digit:]") %>%
+  which() %>%
+  pluck(1)
+
+
+# Get count of sheets in the raw data that start with a number
+
+sheets <-
+  here("inst", "extdata", "PollBase-Q4-2020.xlsx") %>%
+  excel_sheets() %>%
+  str_detect("^[:digit:]") %>%
+  sum()
+
+
+
+# Load raw data from Mark Pack's website
+
+pollbase <-
+  tibble(n = start:sheets) %>%
+  mutate(
+    data =
+      map(
+        .x = n,
+        .f = function(x){
+          read_xlsx(
+            here("inst", "extdata", "PollBase-Q4-2020.xlsx"),
+            sheet = x,
+            col_types = "text",
+            .name_repair = "minimal"
+          )
+        }
+      )
+  )
+
+
+# Load sample size data
+
+load(here("R", "sysdata.rda"))
+
+
+
+# 2. Transform PollBase data ----------------------------------------------
+
+# Before we get started, we'll make our life easier by cleaning the column
+# titles for each sheet of data in our list.
+
+pollbase <-
+  pollbase %>%
+  mutate(
+    data =
+      map(
+        .x = data,
+        .f = function(x){
+          x %>%
+            clean_names() %>%
+            select(-matches("^x.*"),
+                   -ends_with("lead"),
+                   -ends_with("net"),
+                   -ends_with("good"),
+                   -ends_with("bad"),
+                   -ends_with("best_pm"),
+                   -ends_with("_38"),
+                   -ends_with("_47"),
+                   -ends_with("_48"),
+                   -ends_with("_49"),
+                   -ends_with("_50"),
+                   -ends_with("_51"),
+                   -matches("question"),
+                   -matches("leader"),
+                   -matches("^m_$"),
+                   -matches("^f_$"),
[…]

### 2021-03-12 data-raw/003_pollbasepro.R

@@ -1,0 +1,430 @@
+
+# Fit Model to Data
+
+
+# 1. Housekeeping ---------------------------------------------------------
+
+
+# Load packages
+
+library(PollBasePro)
+library(tidyverse)
+library(lubridate)
+library(labelled)
+library(magrittr)
+library(cmdstanr)
+library(haven)
+library(here)
+
+
+# Load pollbase data
+
+data("pollbase")
+
+
+# Load imputed sample sizes
+
+load(here("R", "sysdata.rda"))
+
+
+# Get election dates
+
+elec_dates <-
+  c(
+    "1955-05-26",
+    "1959-10-08",
+    "1964-10-15",
+    "1966-03-31",
+    "1970-06-18",
+    "1974-02-28",
+    "1974-10-10",
+    "1979-05-03",
+    "1983-06-09",
+    "1987-06-11",
+    "1992-04-09",
+    "1997-05-01",
+    "2001-06-07",
+    "2005-05-05",
+    "2010-05-06",
+    "2015-05-07",
+    "2017-06-08",
+    "2019-12-12"
+  )
+
+
+
+# 2. Transform data -------------------------------------------------------
+
+# Before we fit the model to estimate daily voting intention estimates, we
+# first need to transform the raw pollbase data. The first thing that we
+# need to do is to count how many days each poll was in the field duplicate
+# it that many times, and then record the number of field days.
+
+pollbase <-
+  pollbase %>%
+  mutate(
+    days =
+      interval(start, end) %>%
+      divide_by(days(1)) %>%
+      add(1)
+  ) %>%
+  uncount(days) %>%
+  group_by(id) %>%
+  mutate(
+    date =
+      start %m+%
+      days(row_number() - 1),
+    days = n()
+  ) %>%
+  ungroup() %>%
+  select(-start, -end) %>%
+  relocate(date, .before = "pollster") %>%
+  relocate(days, .before = "election")
+
+
+# Next, we need to add an index variable that counts the days that have
+# passed since the last election took place
+
+pollbase <-
+  pollbase %>%
+  mutate(
+    index =
+      interval(election, date) %>%
+      divide_by(days(1)) %>%
+      add(1)
+  )
+
+
+# Next, we'll remove any polls that took place on the day of an election,
+# as we have perfect information on these days
+
+pollbase <-
+  pollbase %>%
+  filter(!(date %in% as_date(elec_dates)))
+
+
[…]

### 2021-03-12 data-raw/004_validation.R

@@ -1,0 +1,197 @@
+
+# Validate data
+
+
+# 1. Housekeeping ---------------------------------------------------------
+
+# Load packages
+
+library(PollBasePro)
+library(tidyverse)
+library(lubridate)
+library(brms)
+library(here)
+
+
+# Load pollbasepro data
+
+data("pollbasepro")
+
+
+# Load Timeline data, filter to include only UK cases, and split by party
+
+timeline <-
+  readRDS(here("inst", "extdata", "timeline.rds")) %>%
+  select(
+    date = polldate,
+    elecdate,
+    country,
+    party = partyid,
+    vote = poll_
+  ) %>%
+  filter(country == "United Kingdom") %>%
+  mutate(
+    vote = vote/100,
+    party = case_when(party == 1 ~ "con", party == 2 ~ "lab", party == 3 ~ "lib"),
+    polldate = as_date(date)
+  ) %>%
+  na.omit()
+
+con <-
+  timeline %>%
+  filter(party == "con") %>%
+  left_join(
+    pollbasepro,
+    c("polldate" = "date")
+  ) %>%
+  na.omit()
+
+lab <-
+  timeline %>%
+  filter(party == "lab") %>%
+  left_join(
+    pollbasepro,
+    c("polldate" = "date")
+  ) %>%
+  na.omit()
+
+lib <-
+  timeline %>%
+  filter(party == "lib") %>%
+  left_join(
+    pollbasepro,
+    c("polldate" = "date")
+  ) %>%
+  na.omit()
+
+
+
+# 3. Fit correlation models -----------------------------------------------
+
+# We're going to validate the PollBasePro data by calculating the correlation
+# between them and another data source: the "Timeline of Elections" data
+# from Jennings and Wlezien's (2015). As our estimates include known error,
+# we can't just use a run-of-the-mill correlation. Instead, we'll fit some
+# simple models in brms to calculate the correlation for us while accounting
+# for uncertainty.
+
+cor_con <-
+  brm(
+    formula =
+      bf(vote ~ 1) +
+      bf(con_est | se(con_err, sigma = TRUE) ~ 1) +
+      set_rescor(rescor = TRUE),
+    prior =
+      prior(normal(0.4, 0.07), class = "Intercept", resp = "vote") +
+      prior(exponential(5), class = "sigma", resp = "vote") +
+      prior(normal(0.4, 0.07), class = "Intercept", resp = "conest") +
[…]

### 2021-03-12 data-raw/005_example.R

@@ -1,0 +1,133 @@
+
+# Applied example
+
+
+# 1. Housekeeping ---------------------------------------------------------
+
+# Load packages
+
+library(PollBasePro)
+library(tidyverse)
+library(lubridate)
+library(brms)
+library(here)
+
+
+# Load pollbasepro data
+
+data("pollbasepro")
+
+
+# Merge in coronavirus deaths data
+
+pollbasepro <-
+  pollbasepro %>%
+  left_join(
+    read_csv(here("inst", "extdata", "data_2021-Mar-06-deaths.csv")) %>%
+      select(
+        date,
+        deaths = newDeaths28DaysByDeathDate
+      ),
+    by = "date"
+  )
+
+
+
+# 2. Transform data -------------------------------------------------------
+
+# We've matched the vaccines and deaths data to the pollbase time series,
+# but we need to transform everything a little. First, we'll select the
+# variables that we need.
+
+pollbasepro <-
+  pollbasepro %>%
+  select(
+    date,
+    con_est,
+    con_err,
+    deaths
+  )
+
+
+# Next, we'll fill any missing deaths data with zeroes to mark out that
+# the coronavirus had not yet occurred.
+
+pollbasepro <-
+  pollbasepro %>%
+  mutate(deaths = ifelse(is.na(deaths) == T, 0, deaths))
+
+
+# We'll then convert our data from raw figures to changes over the past
+# 4 weeks.
+
+pollbasepro <-
+  pollbasepro %>%
+  mutate(
+    con_est = con_est - lag(con_est, 28),
+    con_err = sqrt(con_err^2 + lag(con_err, 28)^2),
+    deaths = (deaths - lag(deaths, 28))/100
+  )
+
+
+# Now, we'll filter out all cases pre-2019 election and the one case on
+# 2021-03-06 where there is no coronavirus data
+
+pollbasepro <-
+  pollbasepro %>%
+  filter(
+    date >= "2019-12-12",
+    date != "2021-03-06"
+  )
+
+
+# Finally, we also need to create a time index variable so that we can deal
+# with any time-varying variation not due to death or vaccine rates.
+
+pollbasepro <-
+  pollbasepro %>%
+  mutate(time = interval(min(date), date)/months(1))
+
+
+
+# 3. Fit model ------------------------------------------------------------
+
+# Now that we have transformed our data, we can now fit our model. This is
+# a simple linear model, but we'll also include an interaction between the
[…]

### 2021-03-12 documentation/_assets/cover.R

@@ -1,0 +1,112 @@
+
+# Create user guide cover image
+
+
+# 1. Housekeeping ---------------------------------------------------------
+
+# Load packages
+
+library(tidyverse)
+library(magrittr)
+library(ggimage)
+library(here)
+
+
+# Load pollbasepro data
+
+data("pollbasepro")
+
+
+
+# 2. Create plot ----------------------------------------------------------
+
+# We're going to create a simple plot to use as the user guide cover. The
+# neat thing about it is that we can use randomisation to make the cover be
+# different each day. We'll set it up so that the proportion of blue, red,
+# and orange graphics on the cover are roughly proportional to the normalised
+# vote shares of the Conservatives, Labour, and the Liberals according to
+# our most recent estimate.
+
+# First, we'll get today's date and convert to numeric
+
+date_now <- as.numeric(Sys.Date())
+
+
+# Second, we'll use the date to set the random seed
+
+set.seed(date_now)
+
+
+# Next, we'll get the most recent estimates from pollbasepro and normalise
+# them to sum to 1.
+
+props <-
+  pollbasepro %>%
+  filter(date == max(date)) %>%
+  select(matches("_est")) %>%
+  mutate_all(function(x) x/rowSums(.)) %>%
+  t() %>%
+  rep(5) %>%
+  divide_by(5)
+
+
+# Next, we'll get  icon file paths and shuffle them according to the different
+# normalised proportions that we estimated.
+
+paths <- dir(here("documentation", "_assets", "icons"), full.names = T)
+paths <- sample(paths, size = 169, replace = T, prob = props)
+
+
+# Then, we'll generate some basic data
+
+dta <-
+  tibble(
+    x = rep(seq(0, 6, by = .5), each = 13),
+    y = rep(seq(0, 6, by = .5), 13),
+    image = paths
+  )
+
+
+# And, finally, we'll generate today's cover plot
+
+cover <-
+  dta %>%
+  ggplot(
+    aes(
+      x = x,
+      y = y
+    )
+  ) +
+  geom_image(
+    aes(
+      x = x,
+      y = y,
+      image = paths
+    ),
+    size = 0.04,
+    by = "width",
+    asp = 1
+  ) +
+  coord_cartesian(
+    xlim = c(0, 6),
+    ylim = c(0, 6)
+  ) +
+  theme_void() +
+  theme(legend.position = "none")
+
+
+
+# 3. Render plot ----------------------------------------------------------
+
[…]

### 2021-03-12 tests/testthat/tests.pollbase.R

@@ -1,0 +1,78 @@
+
+# Tests: pollbase dataset
+
+
+# 1. Housekeeping ---------------------------------------------------------
+
+# Load packages
+
+library(PollBasePro)
+library(dplyr)
+library(purrr)
+library(here)
+
+
+# Load data
+
+data("pollbase")
+
+
+# 2. Data tests -----------------------------------------------------------
+
+# Test 1: Ensure that there are no duplicated IDs
+
+test_that("There are no duplicated IDs", {
+  expect_equal(
+    length(table(pollbase$id)[table(pollbase$id) > 1]),
+    0
+  )
+})
+
+
+# Test 2: Ensure all values are between 0 and 1
+
+test_that("All voting intention figures are between 0 and 1", {
+  expect_gte(
+    min(pollbase$con),
+    0
+  )
+  expect_lte(
+    max(pollbase$con),
+    1
+  )
+  expect_gte(
+    min(pollbase$lab),
+    0
+  )
+  expect_lte(
+    max(pollbase$lab),
+    1
+  )
+  expect_gte(
+    min(pollbase$lib),
+    0
+  )
+  expect_lte(
+    max(pollbase$lib),
+    1
+  )
+})
+
+
+# Test 3: Ensure correlations between parties are negative
+
+test_that("Correlations between voting intention figures are negative", {
+  expect_lt(
+    cor.test(pollbase$con, pollbase$lab)$estimate,
+    0
+  )
+  expect_lt(
+    cor.test(pollbase$con, pollbase$lib)$estimate,
+    0
+  )
+  expect_lt(
+    cor.test(pollbase$lab, pollbase$lib)$estimate,
+    0
+  )
+})
+

### 2021-03-12 tests/testthat/tests.pollbasepro.R

@@ -1,0 +1,142 @@
+
+# Tests: pollbasepro dataset
+
+
+# 1. Housekeeping ---------------------------------------------------------
+
+# Load packages
+
+library(PollBasePro)
+library(dplyr)
+library(purrr)
+library(brms)
+library(here)
+
+
+# Load data
+
+data("pollbasepro")
+
+
+# Load validation/correlation models
+
+cor_all <- readRDS(here("models", paste0("cor_all_", packageVersion("PollBasePro"), ".rds")))
+cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("PollBasePro"), ".rds")))
+cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("PollBasePro"), ".rds")))
+cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("PollBasePro"), ".rds")))
+
+
+
+# 2. Data tests -----------------------------------------------------------
+
+# Test 1: Ensure that there are no missing dates
+
+test_that("There are no missing dates", {
+  expect_equal(
+    length(setdiff(seq.Date(min(pollbasepro$date), max(pollbasepro$date), "days"), pollbasepro$date)),
+    0
+  )
+})
+
+
+# Test 2: Ensure all voting intention estimates are between 0 and 1
+
+test_that("All voting intention estimates are between 0 and 1", {
+  expect_gte(
+    min(pollbasepro$con_est),
+    0
+  )
+  expect_lte(
+    max(pollbasepro$con_est),
+    1
+  )
+  expect_gte(
+    min(pollbasepro$lab_est),
+    0
+  )
+  expect_lte(
+    max(pollbasepro$lab_est),
+    1
+  )
+  expect_gte(
+    min(pollbasepro$lib_est),
+    0
+  )
+  expect_lte(
+    max(pollbasepro$lib_est),
+    1
+  )
+})
+
+
+# Test 3: Ensure correlations between parties are negative
+
+test_that("Correlations between voting intention figures are negative", {
+  expect_lt(
+    median(pluck(posterior_samples(cor_all, "rescor__libest__conest"), 1)),
+    0
+  )
+  expect_lt(
+    median(pluck(posterior_samples(cor_all, "rescor__libest__labest"), 1)),
+    0
+  )
+  expect_lt(
+    median(pluck(posterior_samples(cor_all, "rescor__conest__labest"), 1)),
[…]

### 2021-03-12 data-raw/000_compile.R
Changed paper and userguide names

@@ -45,7 +45,7 @@ source(here("data-raw", "005_example.R"))
 
 render(
   input = here("documentation", "paper.Rmd"),
-  output_file = here("download", paste0("paper_", packageVersion("PollBasePro"), ".pdf"))
+  output_file = here("download", "paper.pdf")
 )
 
 
@@ -58,7 +58,7 @@ source(here("documentation", "_assets", "cover.R"))
 
 render(
   input = here("documentation", "userguide.Rmd"),
-  output_file = here("download", paste0("userguide_", packageVersion("PollBasePro"), ".pdf"))
+  output_file = here("download", "userguide.pdf")
 )
 
 

### 2021-03-12 documentation/readme.Rmd
Changed paper and userguide names
Update README

@@
 The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.
+The user guide and codebook is available [here](https://github.com/jackobailey/PollBasePro/blob/master/download/userguide.pdf) and the accompanying paper is available [here](https://github.com/jackobailey/PollBasePro/blob/master/download/paper.pdf).
 
@@
 These files include all necessary value and variable labels and should work seamlessly with both software packages.
-Click here to download them.
+[Click here to download them](https://github.com/jackobailey/PollBasePro/tree/master/download).
 
@@
 
-<center><img src="https://raw.githubusercontent.com/jackobailey/econ_half_life/master/documentation/_assets/timeplot_gh.png"></center>
+<center><img src="https://raw.githubusercontent.com/jackobailey/PollBasePro/master/documentation/_assets/timeplot_gh.png"></center>
 

### 2021-03-12 documentation/readme.Rmd
Added image token to README
Amended README text

@@
 
-<center><img src="https://raw.githubusercontent.com/jackobailey/PollBasePro/master/documentation/_assets/timeplot_gh.png"></center>
+<center><img src="https://raw.githubusercontent.com/jackobailey/PollBasePro/master/documentation/_assets/timeplot_gh.png?token=AI2VF2PMPYJQ277S7LBU4ILAJOPVI"></center>
 
@@
 **This puts the `r txt_dta$party[2]` in second place** on `r paste0(txt_dta$share[2], " (95% CI: ", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")` of the vote.
-**In third place is the `r txt_dta$party[3]`**, who gain the support of around `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")` of voters.
+**In third place is the `r txt_dta$party[3]`**, with support from `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")` of voters.
 

### 2021-03-12 documentation/readme.Rmd
Added title to README plot

@@
   labs(
+    title = paste0("British Poll of Polls, ", str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")),
     colour = "Party",

### 2021-03-12 documentation/readme.Rmd
Remove token from README image
Prepared for clean compilation

@@
 ---
-output: github_document
+output:
+  github_document:
+    html_preview: false
 ---
@@
 
-<center><img src="https://raw.githubusercontent.com/jackobailey/PollBasePro/master/documentation/_assets/timeplot_gh.png?token=AI2VF2PMPYJQ277S7LBU4ILAJOPVI"></center>
+<center><img src="https://raw.githubusercontent.com/jackobailey/PollBasePro/master/documentation/_assets/timeplot_gh.png"></center>
 

### 2021-03-12 R/get_2015_polls.R

@@ -15,7 +15,7 @@ get_2015_polls <- function(){
   # are a whole host of people who keep these pages up to date and it means
   # that we don't have to manage data collection ourselves.
 
-  url1 <- "https://en.wikipedia.org/wiki/Opinion_polling_for_the_2015_United_Kingdom_general_election_(2010–2012)"
+  url1 <- "https://en.wikipedia.org/wiki/Opinion_polling_for_the_2015_United_Kingdom_general_election_(2010\u20142012)"
   url2 <- "https://en.wikipedia.org/wiki/Opinion_polling_for_the_2015_United_Kingdom_general_election"
 
 
@@ -164,7 +164,7 @@ get_2015_polls <- function(){
     dta %>%
     tidyr::separate(
       col = date,
-      sep = "-|–",
+      sep = "-|\u2014",
       into = c("start", "end")
     )
 

### 2021-03-12 R/get_2017_polls.R

@@ -127,7 +127,7 @@ get_2017_polls <- function(){
     dta %>%
     tidyr::separate(
       col = date,
-      sep = "-|–",
+      sep = "-|\u2014",
       into = c("start", "end")
     )
 

### 2021-03-12 R/get_2019_polls.R

@@ -127,7 +127,7 @@ get_2019_polls <- function(){
     dta %>%
     tidyr::separate(
       col = date,
-      sep = "-|–",
+      sep = "-|\u2014",
       into = c("start", "end")
     )
 

### 2021-03-12 R/get_new_polls.R

@@ -115,7 +115,7 @@ get_new_polls <- function(){
     dta %>%
     tidyr::separate(
       col = date,
-      sep = "-|–",
+      sep = "-|\u2014",
       into = c("start", "end")
     )
 

### 2021-03-12 R/global.R

@@ -33,6 +33,19 @@ utils::globalVariables(
     "Samplesize",
     "Datesconducted",
     "Pollster",
-    "variable"
+    "variable",
+    "init",
+    "party",
+    ".",
+    "days",
+    "index",
+    "est",
+    "err",
+    "est_con",
+    "sd_con",
+    "est_lab",
+    "sd_lab",
+    "est_lib",
+    "sd_lib"
     )
 )

### 2021-03-12 data-raw/000_compile.R

@@ -71,10 +71,21 @@ render(
 )
 
 
+# 44 Check and install ----------------------------------------------------
 
-# 4. Produce replication materials ----------------------------------------
-
-# Save session information to the "sessions" folder
+# We'll save session information to the "sessions" folder
 
 save_info(path = here("sessions", "000_compile.txt"))
+
+
+# Now, we'll run our unit tests to check that nothing weird is happening or
+# that the data don't contain any obvious errors.
+
+devtools::check()
+
+
+# Then, we'll reinstall the package in full.
+
+devtools::install()
+
 

### 2021-03-12 data-raw/005_example.R

@@ -23,7 +23,7 @@ data("pollbasepro")
 pollbasepro <-
   pollbasepro %>%
   left_join(
-    read_csv(here("inst", "extdata", "data_2021-Mar-06-deaths.csv")) %>%
+    read_csv(here("inst", "extdata", "data_2021-Mar-12.csv")) %>%
       select(
         date,
         deaths = newDeaths28DaysByDeathDate

### 2021-03-12 tests/testthat/tests.pollbase.R

@@ -76,3 +76,13 @@ test_that("Correlations between voting intention figures are negative", {
   )
 })
 
+
+# Test 4: Ensure no start dates are after end dates
+
+test_that("No start dates are after end dates", {
+  expect_equal(
+    sum(pollbase$start > pollbase$end),
+    0
+  )
+})
+

### 2021-03-12 documentation/readme.Rmd
Amend README plotting code to use Twitter handles

@@
     y = "Vote Share",
-    caption = "Based on data from PollBasePro, created by Jack Bailey, Mark Pack, and Luke Mansillo: www.github.com/jackobailey/PollBasePro"
+    caption = "Based on data from PollBasePro, created by @PoliSciJack, @markpack, and @mansillo: www.github.com/jackobailey/PollBasePro"
   ) +
@@
 Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("PollBasePro")` [computer file], `r format(Sys.Date(), format = "%B %Y")`.
-Retrieved from doi.
+Retrieved from https://doi.org/10.7910/DVN/3POIQW.
 

### 2021-03-13 documentation/paper.Rmd
Remove reliance on jbmisc functions and download Timeline data remotely

@@
 library(patchwork)
-library(jbmisc)
 library(brms)
@@
 timeline <-
-  readRDS(here("inst", "extdata", "timeline.rds")) %>%
+  load_timeline() %>%
   select(
@@
 \alpha_{T} &\sim \mathrm{Normal}(\alpha_{T-1}, \tau) \srlab{Adaptive prior on $\alpha_{T}$} \\
-\delta_{j} &\sim \mathrm{Normal}(0, 0.1) \text{ for } j \text{ in } 1, ..., J \srlab{Prior on house effects, $\delta$} \\
+\delta_{j} &\sim \mathrm{Normal}(0, 0.05) \text{ for } j \text{ in } 1, ..., J \srlab{Prior on house effects, $\delta$} \\
 \omega_{t} &\sim \mathrm{Normal}(0, 0.1) \text{ for } t \text{ in } 1, ..., T-1 \srlab{Prior on random shocks, $\omega$} \\
@@
 tl <-
-  readRDS(here("inst", "extdata", "timeline.rds")) %>%
+  load_timeline() %>%
   select(
@@
     ) +
-  jbmisc::theme_bailey() +
+   theme_minimal() +
+    theme(
+      legend.position = "bottom",
+      legend.title = element_blank(),
+      text = element_text(family = "Cabin", color = "black", size = 8),
+      plot.title = element_text(family = "Cabin", face = "bold", size = rel(1.4), hjust = 0),
+      plot.subtitle = element_text(family = "Cabin", size = rel(1), hjust = 0, margin = margin(b = 10)),
+      axis.line = element_line(lineend = "round"),
+      axis.title.x = element_blank(),
+      axis.text.x = element_text(color = "black", size = rel(1)),
+      axis.ticks.x = element_line(lineend = "round"),
+      axis.title.y = element_text(family = "Cabin", face = "bold", size = rel(1)),
+      axis.text.y = element_text(color = "black", size = rel(1)),
+      strip.text = element_text(family = "Cabin", face = "bold", size = rel(1)),
+      panel.spacing = unit(.3, "cm"),
+      panel.grid.major.y = element_line(size = .5, lineend = "round"),
+      panel.grid.minor.y = element_blank(),
+      panel.grid.major.x = element_blank(),
+      panel.grid.minor.x = element_blank()
+    ) +
   labs(
@@
     y = "Vote Share"
-  ) +
-  theme(
-    legend.position = "bottom",
-    legend.title = element_blank(),
-    axis.title.x = element_blank()
   )

### 2021-03-13 documentation/readme.Rmd
Remove reliance on jbmisc functions and download Timeline data remotely

@@
     ) +
-  jbmisc::theme_bailey() +
+  theme_minimal() +
+    theme(
+      legend.position = "bottom",
+      legend.title = element_blank(),
+      text = element_text(family = "Cabin", color = "black", size = 8),
+      plot.title = element_text(family = "Cabin", face = "bold", size = rel(1.4), hjust = 0),
+      plot.subtitle = element_text(family = "Cabin", size = rel(1), hjust = 0, margin = margin(b = 10)),
+      axis.line = element_line(lineend = "round"),
+      axis.title.x = element_blank(),
+      axis.text.x = element_text(color = "black", size = rel(1)),
+      axis.ticks.x = element_line(lineend = "round"),
+      axis.title.y = element_text(family = "Cabin", face = "bold", size = rel(1)),
+      axis.text.y = element_text(color = "black", size = rel(1)),
+      strip.text = element_text(family = "Cabin", face = "bold", size = rel(1)),
+      panel.spacing = unit(.3, "cm"),
+      panel.grid.major.y = element_line(size = .5, lineend = "round"),
+      panel.grid.minor.y = element_blank(),
+      panel.grid.major.x = element_blank(),
+      panel.grid.minor.x = element_blank()
+    ) +
   labs(
@@
     caption = "Based on data from PollBasePro, created by @PoliSciJack, @markpack, and @mansillo: www.github.com/jackobailey/PollBasePro"
-  ) +
-  theme(
-    legend.position = "bottom",
-    legend.title = element_blank(),
-    axis.title.x = element_blank()
   )

### 2021-03-13 documentation/userguide.Rmd
Add data DOI
Remove reliance on jbmisc functions and download Timeline data remotely

@@
 library(lubridate)
-library(jbmisc)
 library(brms)
@@
   coord_cartesian(ylim = c(0, 0.05)) +
-  jbmisc::theme_bailey() +
-  labs(y = "Posterior Uncertainty (95%)") +
-  theme(axis.title.x = element_blank())
+   theme_minimal() +
+    theme(legend.title = element_text(family = "Cabin", face = "bold", size = rel(1)),
+                   text = element_text(family = "Cabin", color = "black", size = 8),
+                   plot.title = element_text(family = "Cabin", face = "bold", size = rel(1.4), hjust = 0),
+                   plot.subtitle = element_text(family = "Cabin", size = rel(1), hjust = 0, margin = margin(b = 10)),
+                   axis.line = element_line(lineend = "round"),
+                   axis.title.x = element_blank(),
+                   axis.text.x = element_text(color = "black", size = rel(1)),
+                   axis.ticks.x = element_line(lineend = "round"),
+                   axis.title.y = element_text(family = "Cabin", face = "bold", size = rel(1)),
+                   axis.text.y = element_text(color = "black", size = rel(1)),
+                   strip.text = element_text(family = "Cabin", face = "bold", size = rel(1)),
+                   panel.spacing = unit(.3, "cm"),
+                   panel.grid.major.y = element_line(size = .5, lineend = "round"),
+                   panel.grid.minor.y = element_blank(),
+                   panel.grid.major.x = element_blank(),
+                   panel.grid.minor.x = element_blank()
+    ) +
+  labs(y = "Posterior Uncertainty (95%)")
 
@@
   coord_cartesian(ylim = c(0, 2600)) +
-  jbmisc::theme_bailey() +
+  theme_minimal() +
+    theme(legend.title = element_text(family = "Cabin", face = "bold", size = rel(1)),
+                   text = element_text(family = "Cabin", color = "black", size = 8),
+                   plot.title = element_text(family = "Cabin", face = "bold", size = rel(1.4), hjust = 0),
+                   plot.subtitle = element_text(family = "Cabin", size = rel(1), hjust = 0, margin = margin(b = 10)),
+                   axis.line = element_line(lineend = "round"),
+                   axis.title.x = element_blank(),
+                   axis.text.x = element_text(color = "black", size = rel(1)),
+                   axis.ticks.x = element_line(lineend = "round"),
+                   axis.title.y = element_text(family = "Cabin", face = "bold", size = rel(1)),
+                   axis.text.y = element_text(color = "black", size = rel(1)),
+                   strip.text = element_text(family = "Cabin", face = "bold", size = rel(1)),
+                   panel.spacing = unit(.3, "cm"),
+                   panel.grid.major.y = element_line(size = .5, lineend = "round"),
+                   panel.grid.minor.y = element_blank(),
+                   panel.grid.major.x = element_blank(),
+                   panel.grid.minor.x = element_blank()
+    ) +
   labs(
     y = "Imputed Sample Size"
-  ) +
-  theme(axis.title.x = element_blank())
+  )
 

### 2021-03-13 R/get_2015_polls.R

@@ -15,7 +15,7 @@ get_2015_polls <- function(){
   # are a whole host of people who keep these pages up to date and it means
   # that we don't have to manage data collection ourselves.
 
-  url1 <- "https://en.wikipedia.org/wiki/Opinion_polling_for_the_2015_United_Kingdom_general_election_(2010\u20142012)"
+  url1 <- "https://en.wikipedia.org/wiki/Opinion_polling_for_the_2015_United_Kingdom_general_election_(2010–2012)"
   url2 <- "https://en.wikipedia.org/wiki/Opinion_polling_for_the_2015_United_Kingdom_general_election"
 
 
@@ -125,7 +125,7 @@ get_2015_polls <- function(){
       pollster =
         pollster %>%
         stringr::str_remove("/.*") %>%
-        stringr::str_remove("-|\u2014") %>%
+        stringr::str_remove("-|–") %>%
         tolower()
     )
 
@@ -164,7 +164,7 @@ get_2015_polls <- function(){
     dta %>%
     tidyr::separate(
       col = date,
-      sep = "-|\u2014",
+      sep = "-|–",
       into = c("start", "end")
     )
 

### 2021-03-13 R/get_2017_polls.R

@@ -88,7 +88,7 @@ get_2017_polls <- function(){
       pollster =
         pollster %>%
         stringr::str_remove("/.*") %>%
-        stringr::str_remove("-|\u2014") %>%
+        stringr::str_remove("-|–") %>%
         tolower()
     )
 
@@ -127,7 +127,7 @@ get_2017_polls <- function(){
     dta %>%
     tidyr::separate(
       col = date,
-      sep = "-|\u2014",
+      sep = "-|–",
       into = c("start", "end")
     )
 

### 2021-03-13 R/get_2019_polls.R

@@ -88,7 +88,7 @@ get_2019_polls <- function(){
       pollster =
         pollster %>%
         stringr::str_remove("/.*") %>%
-        stringr::str_remove("-|\u2014") %>%
+        stringr::str_remove("-|–") %>%
         tolower()
     )
 
@@ -127,7 +127,7 @@ get_2019_polls <- function(){
     dta %>%
     tidyr::separate(
       col = date,
-      sep = "-|\u2014",
+      sep = "-|–",
       into = c("start", "end")
     )
 

### 2021-03-13 R/get_new_polls.R

@@ -76,7 +76,7 @@ get_new_polls <- function(){
       pollster =
         pollster %>%
         stringr::str_remove("/.*") %>%
-        stringr::str_remove("-|\u2014") %>%
+        stringr::str_remove("-|–") %>%
         tolower()
     )
 
@@ -115,7 +115,7 @@ get_new_polls <- function(){
     dta %>%
     tidyr::separate(
       col = date,
-      sep = "-|\u2014",
+      sep = "-|–",
       into = c("start", "end")
     )
 

### 2021-03-13 R/update_pollbasepro.R

@@ -384,7 +384,25 @@ update_pollbasepro <- function(){
       ylim = c(0, 0.62),
       xlim = c(max(dta$date) - 365, max(dta$date))
     ) +
-    jbmisc::theme_bailey() +
+    ggplot2::theme_minimal() +
+    ggplot2::theme(
+      legend.position = "none",
+      text = ggplot2::element_text(family = "Cabin", color = "black", size = 8),
+      plot.title = ggplot2::element_text(family = "Cabin", face = "bold", size = ggplot2::rel(1.4), hjust = 0),
+      plot.subtitle = ggplot2::element_text(family = "Cabin", size = ggplot2::rel(1), hjust = 0, margin = ggplot2::margin(b = 10)),
+      axis.line = ggplot2::element_line(lineend = "round"),
+      axis.title.x = ggplot2::element_blank(),
+      axis.text.x = ggplot2::element_text(color = "black", size = ggplot2::rel(1)),
+      axis.ticks.x = ggplot2::element_line(lineend = "round"),
+      axis.title.y = ggplot2::element_blank(),
+      axis.text.y = ggplot2::element_text(color = "black", size = ggplot2::rel(1)),
+      strip.text = ggplot2::element_text(family = "Cabin", face = "bold", size = ggplot2::rel(1)),
+      panel.spacing = ggplot2::unit(.3, "cm"),
+      panel.grid.major.y = ggplot2::element_line(size = .5, lineend = "round"),
+      panel.grid.minor.y = ggplot2::element_blank(),
+      panel.grid.major.x = ggplot2::element_blank(),
+      panel.grid.minor.x = ggplot2::element_blank()
+    ) +
     ggplot2::labs(
       title =
         paste0(
@@ -394,11 +412,6 @@ update_pollbasepro <- function(){
           " Points Ahead"
         ),
       caption = "@PoliSciJack"
-    ) +
-    ggplot2::theme(
-      legend.position = "none",
-      axis.title.x = ggplot2::element_blank(),
-      axis.title.y = ggplot2::element_blank()
     )
 
 
@@ -481,7 +494,7 @@ update_pollbasepro <- function(){
 
   # Finally, we'll update the replication information
 
-  jbmisc::save_info(here::here("sessions", "003_pollbasepro.txt"))
+  PollBasePro::save_info(here::here("sessions", "003_pollbasepro.txt"))
 
 
 }

### 2021-03-13 data-raw/001_samplesizes.R

@@ -16,7 +16,7 @@ library(here)
 # Load timeline of elections data
 
 timeline <-
-  readRDS(here("inst", "extdata", "timeline.rds")) %>%
+  load_timeline() %>%
   select(
     polldate,
     elecdate,

### 2021-03-13 data-raw/002_pollbase.R

@@ -13,7 +13,6 @@ library(lubridate)
 library(labelled)
 library(janitor)
 library(readxl)
-library(jbmisc)
 library(haven)
 library(here)
 
@@ -320,9 +319,9 @@ pollbase <-
   mutate(
     start =
       start %>%
-      mark_na("c.6") %>%
-      mark_na("?") %>%
-      mark_na("") %>%
+      na_if("c.6") %>%
+      na_if("?") %>%
+      na_if("") %>%
       str_remove("/.*") %>%
       str_remove(" ") %>%
       as.numeric() %>%
@@ -337,8 +336,8 @@ pollbase <-
   mutate(
     end =
       end %>%
-      mark_na("?") %>%
-      mark_na("") %>%
+      na_if("?") %>%
+      na_if("") %>%
       as.numeric() %>%
       ifelse(is.na(.) == T,
              paste(year, month, "01", sep = "-") %>%

### 2021-03-13 data-raw/004_validation.R

@@ -21,7 +21,7 @@ data("pollbasepro")
 # Load Timeline data, filter to include only UK cases, and split by party
 
 timeline <-
-  readRDS(here("inst", "extdata", "timeline.rds")) %>%
+  load_timeline() %>%
   select(
     date = polldate,
     elecdate,

### 2021-03-14 documentation/paper.Rmd
Remove references to "PollBasePro"

@@
 title: |
-  | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(PollBasePro::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback.
+  | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(BritPol::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback.
 We owe particular thanks to Chris Hanretty, Y, and Z.
@@
 date: |
-  | \small This version compiled `r stringr::str_remove(format(Sys.time(), '%d %B %Y'), "^0")` using PollBasePro `r paste0("v", packageVersion("PollBasePro"))`
+  | \small This version compiled `r stringr::str_remove(format(Sys.time(), '%d %B %Y'), "^0")` using PollBasePro `r paste0("v", packageVersion("BritPol"))`
 abstract: |
@@
 It includes voting intention estimates for each of Britain's three largest parties on each day between the 1955 general election and the present.
-Given that the dataset covers `r format(nrow(PollBasePro::pollbasepro), big.mark = ",")` days in total, it is more comprehensive than any existing time series of public opinion in Britain.
+Given that the dataset covers `r format(nrow(BritPol::pollbasepro), big.mark = ",")` days in total, it is more comprehensive than any existing time series of public opinion in Britain.
 As a result, we expect PollBasePro to be an important resource for students of British politics in the years to come.
@@
 
-library(PollBasePro)
+library(BritPol)
 library(kableExtra)
@@
 
-death_mod <- readRDS(here("models", paste0("death_mod_", packageVersion("PollBasePro"), ".rds")))
+death_mod <- readRDS(here("models", paste0("death_mod_", packageVersion("BritPol"), ".rds")))
 
@@
 
-cor_all <- readRDS(here("models", paste0("cor_all_", packageVersion("PollBasePro"), ".rds")))
-cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("PollBasePro"), ".rds")))
-cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("PollBasePro"), ".rds")))
-cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("PollBasePro"), ".rds")))
+cor_all <- readRDS(here("models", paste0("cor_all_", packageVersion("BritPol"), ".rds")))
+cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("BritPol"), ".rds")))
+cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("BritPol"), ".rds")))
+cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("BritPol"), ".rds")))
 
@@
 In this paper, we introduce PollBasePro: the most comprehensive time series of British voting intention data assembled to date.
-The dataset contains `r format(nrow(PollBasePro::pollbasepro), big.mark = ",")` daily voting intention estimates for each of Britain's three largest parties, beginning at the 1955 General Election on `r format(min(pollbasepro$date), "%d %B %Y")` and ending on `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.
+The dataset contains `r format(nrow(BritPol::pollbasepro), big.mark = ",")` daily voting intention estimates for each of Britain's three largest parties, beginning at the 1955 General Election on `r format(min(pollbasepro$date), "%d %B %Y")` and ending on `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.
 Furthermore, our data are well validated and follow the course of British political history.

### 2021-03-14 documentation/readme.Rmd
Remove references to "PollBasePro"

--- 2021-03-12 documentation/readme.Rmd
@@
 
-library(PollBasePro)
+library(BritPol)
 library(tidyverse)
@@
 
-# PollBasePro
+# BritPol
 
-PollBasePro is a data package for the `R` programming language.
+BritPol is a data package for the `R` programming language.
 It includes two datasets: `pollbase` and `pollbasepro`.
@@
 The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.
-The user guide and codebook is available [here](https://github.com/jackobailey/PollBasePro/blob/master/download/userguide.pdf) and the accompanying paper is available [here](https://github.com/jackobailey/PollBasePro/blob/master/download/paper.pdf).
+A user guide and codebook is available for `pollbasepro` [here](https://github.com/jackobailey/BritPol/blob/master/download/userguide.pdf) and an accompanying paper is available [here](https://github.com/jackobailey/BritPol/blob/master/download/paper.pdf).
 
-To install the latest version of PollBasePro, run the following code in `R`:
+To install the latest version of BritPol, run the following code in `R`:
 
 ``` r
-devtools::install_github("jackobailey/PollBasePro")
+devtools::install_github("jackobailey/BritPol")
 ```
@@
 These files include all necessary value and variable labels and should work seamlessly with both software packages.
-[Click here to download them](https://github.com/jackobailey/PollBasePro/tree/master/download).
+[Click here to download them](https://github.com/jackobailey/BritPol/tree/master/download).
 
@@
     y = "Vote Share",
-    caption = "Based on data from PollBasePro, created by @PoliSciJack, @markpack, and @mansillo: www.github.com/jackobailey/PollBasePro"
-  ) +
-  theme(
-    legend.position = "bottom",
-    legend.title = element_blank(),
-    axis.title.x = element_blank()
+    caption = "Based on data from BritPol, created by @PoliSciJack, @markpack, and @mansillo: www.github.com/jackobailey/BritPol"
   )
@@
 
-<center><img src="https://raw.githubusercontent.com/jackobailey/PollBasePro/master/documentation/_assets/timeplot_gh.png"></center>
+<center><img src="https://raw.githubusercontent.com/jackobailey/BritPol/master/documentation/_assets/timeplot_gh.png"></center>
 
@@
 Like any project of this size, we cannot rule out the possibility that minor mistakes might have crept into our data processing pipeline.
-If you think that you have found an error in our code or wish to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/PollBasePro/issues) or [contact us directly](mailto:jack.bailey@manchester.ac.uk).
+If you think that you have found an error in our code or wish to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/BritPol/issues) or [contact us directly](mailto:jack.bailey@manchester.ac.uk).
 
@@
 That is, you may reproduce, reuse, and change the code here as you see fit, but must state in each case that you based your analysis on our work.
-The citations for each item in PollBasePro are as follows:
+The citations for each item in BritPol are as follows:
 
@@
 Pack, and L.
-Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("PollBasePro")` [computer file], `r format(Sys.Date(), format = "%B %Y")`.
+Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("BritPol")` [computer file], `r format(Sys.Date(), format = "%B %Y")`.
 Retrieved from https://doi.org/10.7910/DVN/3POIQW.
 
-- **Documentation:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro v`r packageVersion("PollBasePro")`: User Guide and Codebook. Retrieved from doi.
+- **Documentation:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro v`r packageVersion("BritPol")`: User Guide and Codebook. Retrieved from doi.
 

### 2021-03-14 documentation/userguide.Rmd
Remove references to "PollBasePro"

@@
 title: |
-  | PollBasePro v`r packageVersion("PollBasePro")` (Beta)
+  | PollBasePro v`r packageVersion("BritPol")` (Beta)
   | User Guide and Codebook
@@
 
-cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("PollBasePro"), ".rds")))
-cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("PollBasePro"), ".rds")))
-cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("PollBasePro"), ".rds")))
+cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("BritPol"), ".rds")))
+cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("BritPol"), ".rds")))
+cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("BritPol"), ".rds")))
 
@@
 
-- ``r paste0("pollbase_", packageVersion("PollBasePro"), ".dta")``
-- ``r paste0("pollbasepro_", packageVersion("PollBasePro"), ".dta")``
-- ``r paste0("pollbase_", packageVersion("PollBasePro"), ".sav")``
-- ``r paste0("pollbasepro_", packageVersion("PollBasePro"), ".sav")``
+- ``r paste0("pollbase_", packageVersion("BritPol"), ".dta")``
+- ``r paste0("pollbasepro_", packageVersion("BritPol"), ".dta")``
+- ``r paste0("pollbase_", packageVersion("BritPol"), ".sav")``
+- ``r paste0("pollbasepro_", packageVersion("BritPol"), ".sav")``
 

### 2021-03-14 R/pollbase.R

@@ -2,7 +2,7 @@
 #'
 #' A dataset containing Mark Pack's raw pollbase figures for each of Britain's three main parties, tidied and converted to long-format for easy analysis.
 #'
-#' @format A data frame with 6,124 rows and 12 variables:
+#' @format A data frame:
 #' \describe{
 #'   \item{id}{Unique poll identification number}
 #'   \item{election}{Date of last general election}

### 2021-03-14 R/update_pollbasepro.R

@@ -28,7 +28,7 @@ update_pollbasepro <- function(){
       values_to = "estimates"
     ) %>%
     dplyr::mutate(
-      alpha_init = PollBasePro::get_result(election = init, party = party),
+      alpha_init = BritPol::get_result(election = init, party = party),
       alpha_final = NA,
       estimates = as.list(rep(NA, dplyr::n()))
     )
@@ -37,7 +37,7 @@ update_pollbasepro <- function(){
   # Get wiki data and mutate
 
   wiki <-
-    PollBasePro::get_new_polls() %>%
+    BritPol::get_new_polls() %>%
     dplyr::mutate(
       election = "2019-12-12",
       id =
@@ -46,12 +46,12 @@ update_pollbasepro <- function(){
           seq(
             as.numeric(
               stringr::str_remove(
-                PollBasePro::pollbase$id[PollBasePro::pollbase$end > "2019-12-12"][1], ".*-"
+                BritPol::pollbase$id[BritPol::pollbase$end > "2019-12-12"][1], ".*-"
               )
             ),
             as.numeric(
               stringr::str_remove(
-                PollBasePro::pollbase$id[PollBasePro::pollbase$end > "2019-12-12"][1], ".*-"
+                BritPol::pollbase$id[BritPol::pollbase$end > "2019-12-12"][1], ".*-"
               )
             ) + nrow(.) - 1,
             by = 1
@@ -96,7 +96,7 @@ update_pollbasepro <- function(){
         purrr::map(
           .x = dplyr::row_number(),
           .f = function(x){
-            PollBasePro::fit_model(
+            BritPol::fit_model(
               data = wiki,
               init = dta$init[x],
               final = dta$final[x],
@@ -116,7 +116,7 @@ update_pollbasepro <- function(){
     dplyr::mutate(
       election =
         date %>%
-        PollBasePro::get_last_election()
+        BritPol::get_last_election()
     ) %>%
     dplyr::distinct() %>%
     tidyr::pivot_wider(
@@ -464,7 +464,7 @@ update_pollbasepro <- function(){
 
   pollbasepro <-
     rbind(
-      PollBasePro::pollbasepro[PollBasePro::pollbasepro$date < "2019-12-12", ],
+      BritPol::pollbasepro[BritPol::pollbasepro$date < "2019-12-12", ],
       dta
     )
 
@@ -494,7 +494,7 @@ update_pollbasepro <- function(){
 
[…]

### 2021-03-14 documentation/userguide.Rmd
Amended documentation to apply to the package and not the dataset

@@
 title: |
-  | PollBasePro v`r packageVersion("BritPol")` (Beta)
-  | User Guide and Codebook
+  | BritPol v`r packageVersion("BritPol")` (Beta)
+  | User Guide and Data Codebook
 date: |
@@
 
-# About PollBasePro
+# About BritPol
 
-PollBasePro is a data package for the `R` programming language.
+BritPol is a data package for the `R` programming language.
 It includes two datasets: `pollbase` and `pollbasepro`.
@@
 To guard against this, we have made all of our materials available for others to inspect.
-If you find an error in the code or wish to make a recommendation for a future update, we invite you to raise an issue on the PollBasePro GitHub repository.
+If you find an error in the code or wish to make a recommendation for a future update, we invite you to raise an issue on the BritPol GitHub repository.
 
-# Citing PollBasePro
+# Citing the Data
 
-If you use PollBasePro, you should also cite it.
-This is good practice and also allows the PollBasePro team to monitor how the data have been used.
-The project comprises three items: the data, this user guide, and a companion paper.
+If you use the `pollbasepro` data, you should also cite it.
+This is good practice and also allows us monitor how the data have been used.
+The `pollbasepro` project comprises three items: the data, this user guide, and a companion paper.
 The citations for each item are as follows:
@@
 
-- **Documentation:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro v`r packageVersion("BritPol")`: User Guide and Codebook. Retrieved from doi.
+- **Documentation:** Bailey, J. (`r format(Sys.Date(), format = "%Y")`) BritPol v`r packageVersion("BritPol")`: User Guide and Data Codebook. Retrieved from doi.
 
@@
 
-# Using PollBasePro
+# Using BritPol
 
-Getting started with PollBasePro in `R` is simple.
+Getting started with BritPol in `R` is simple.
 It requires only three short steps: first, to install the package; second, to load the package; and, third, to load the data.
 Once you have taken these three steps, you can then begin analysing the data.
-Note that PollBasePro is not yet available on CRAN, the service that hosts most `R` packages.
-As such, it is not yet possible to install PollBasePro with `R`'s standard `install.packages()` function.
+Note that BritPol is not yet available on CRAN, the service that hosts most `R` packages.
+As such, it is not yet possible to install BritPol with `R`'s standard `install.packages()` function.
 Instead, we must install it directly from its GitHub repository.
@@
 ```{r install-pbp, eval = FALSE}
-# 1. Install the PollBasePro package from GitHub
-devtools::install_github("jackobailey/PollBasePro")
+# 1. Install the BritPol package from GitHub
+devtools::install_github("jackobailey/BritPol")
 
-# 2. Load the PollBasePro package in R
-library(PollBasePro)
+# 2. Load the BritPol package in R
+library(BritPol)
 
@@
 
-Though PollBasePro is first and foremost an `R` data package, we have sought to accommodate those who use Stata and SPSS too.
+Though BritPol is first and foremost an `R` data package, we have sought to accommodate those who use Stata and SPSS too.
 To make this as easy as possible, we have made both the `pollbase` and `pollbasepro` datasets available as .dta and .sav files.
@@
 
-For the sake of openness and transparency, we provide a change log that lists all updates and changes made to the PollBasePro datasets and documentation over time.
-If you think that you have found a problem with either, please raise an issue on the project's GitHub repository.
+For the sake of openness and transparency, we provide a change log that lists all updates and changes made to BritPol over time.
+If you think that you have found a problem with either the data, code, or documentation, please raise an issue on the project's GitHub repository.
 

### 2021-03-14 documentation/paper.Rmd
Fixed references to PollBasePro

@@
 death_dta <- 
-read_csv(here("inst", "extdata", "data_2021-Mar-06-deaths.csv")) %>%
+read_csv(here("inst", "extdata", "death_dta.csv")) %>%
       select(
@@
 cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("BritPol"), ".rds")))
+
+# Create custom ggplot theme
+
+theme_bailey <- function(){
+  theme_minimal() +
+    theme(legend.title = element_text(family = "Cabin", face = "bold", size = rel(1)),
+                   text = element_text(family = "Cabin", color = "black", size = 8),
+                   plot.title = element_text(family = "Cabin", face = "bold", size = rel(1.4), hjust = 0),
+                   plot.subtitle = element_text(family = "Cabin", size = rel(1), hjust = 0, margin = margin(b = 10)),
+                   axis.line = element_line(lineend = "round"),
+                   axis.title.x = element_text(family = "Cabin", face = "bold", margin = margin(t = 10), size = rel(1)),
+                   axis.text.x = element_text(color = "black", size = rel(1)),
+                   axis.ticks.x = element_line(lineend = "round"),
+                   axis.title.y = element_text(family = "Cabin", face = "bold", size = rel(1)),
+                   axis.text.y = element_text(color = "black", size = rel(1)),
+                   strip.text = element_text(family = "Cabin", face = "bold", size = rel(1)),
+                   panel.spacing = unit(.3, "cm"),
+                   panel.grid.major.y = element_line(size = .5, lineend = "round"),
+                   panel.grid.minor.y = element_blank(),
+                   panel.grid.major.x = element_blank(),
+                   panel.grid.minor.x = element_blank()
+    )
+}
 
@@
 To guard against this, we have hosted all of our materials online for others to inspect.
-If our users find any errors in our code or wish to make recommendations for future updates, we invite them to raise an issue on the project's GitHub repository or to contact the authors directly.
+If our users find any errors in our code or wish to make recommendations for future updates, we invite them to raise an issue on the project's [GitHub repository](https://github.com/jackobailey/BritPol/issues) or to [contact the authors directly](mailto:jack.bailey@manchester.ac.uk).
 

### 2021-03-14 documentation/userguide.Rmd
Fixed references to PollBasePro

@@
 To guard against this, we have made all of our materials available for others to inspect.
-If you find an error in the code or wish to make a recommendation for a future update, we invite you to raise an issue on the BritPol GitHub repository.
+If you find an error in the code or wish to make a recommendation for a future update, we invite you to [raise an issue on the BritPol GitHub repository](https://github.com/jackobailey/BritPol/issues).
 
@@
 As such, it is not yet possible to install BritPol with `R`'s standard `install.packages()` function.
-Instead, we must install it directly from its GitHub repository.
+Instead, we must install it directly from its [GitHub repository](https://github.com/jackobailey/BritPol).
 Thankfully this is straightforward and requires only that you run the following code in your `R` console:
@@
 To guard against this, and provide our users with a more in-depth look at our modelling process, we have hosted our entire data pipeline online for others to inspect.
-If our users find any errors in our code or wish to make recommendations for future updates, we invite them to raise an issue on the project's GitHub repository or to contact the authors directly.
+If our users find any errors in our code or wish to make recommendations for future updates, we invite them to [raise an issue on the project's GitHub repository](https://github.com/jackobailey/BritPol/issues) or to [contact the authors directly](mailto:jack.bailey@manchester.ac.uk).
 
@@
 For the sake of openness and transparency, we provide a change log that lists all updates and changes made to BritPol over time.
-If you think that you have found a problem with either the data, code, or documentation, please raise an issue on the project's GitHub repository.
+If you think that you have found a problem with either the data, code, or documentation, please [raise an issue on the project's GitHub repository](https://github.com/jackobailey/BritPol/issues).
 

### 2021-03-14 data-raw/000_compile.R

@@ -1,11 +1,11 @@
 
-# Compile PollBasePro
+# Compile BritPol
 
 # 1. Housekeeping ---------------------------------------------------------
 
 # Load packages
 
-library(PollBasePro)
+library(BritPol)
 library(rmarkdown)
 library(here)
 
@@ -71,7 +71,7 @@ render(
 )
 
 
-# 44 Check and install ----------------------------------------------------
+# 4. Check and install ----------------------------------------------------
 
 # We'll save session information to the "sessions" folder
 

### 2021-03-14 data-raw/002_pollbase.R

@@ -6,7 +6,7 @@
 
 # Load packages
 
-library(PollBasePro)
+library(BritPol)
 library(tidyverse)
 library(magrittr)
 library(lubridate)

### 2021-03-14 data-raw/003_pollbasepro.R

@@ -7,7 +7,7 @@
 
 # Load packages
 
-library(PollBasePro)
+library(BritPol)
 library(tidyverse)
 library(lubridate)
 library(labelled)

### 2021-03-14 data-raw/004_validation.R

@@ -6,7 +6,7 @@
 
 # Load packages
 
-library(PollBasePro)
+library(BritPol)
 library(tidyverse)
 library(lubridate)
 library(brms)

### 2021-03-14 data-raw/005_example.R

@@ -6,7 +6,7 @@
 
 # Load packages
 
-library(PollBasePro)
+library(BritPol)
 library(tidyverse)
 library(lubridate)
 library(brms)
@@ -23,7 +23,7 @@ data("pollbasepro")
 pollbasepro <-
   pollbasepro %>%
   left_join(
-    read_csv(here("inst", "extdata", "data_2021-Mar-12.csv")) %>%
+    read_csv(here("inst", "extdata", "death_dta.csv")) %>%
       select(
         date,
         deaths = newDeaths28DaysByDeathDate
@@ -117,7 +117,7 @@ death_mod <-
     file =
       here(
         "models",
-        paste0("death_mod_", packageVersion("PollBasePro"))
+        paste0("death_mod_", packageVersion("BritPol"))
       )
   )
 

### 2021-03-14 documentation/readme.Rmd
Removed second person language/PollBasePro references

@@
 As such, users should try to use only the most recent version of the data when conducting their analyses.
-Like any project of this size, we cannot rule out the possibility that minor mistakes might have crept into our data processing pipeline.
-If you think that you have found an error in our code or wish to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/BritPol/issues) or [contact us directly](mailto:jack.bailey@manchester.ac.uk).
+Like any project of this size, some minor mistakes might have crept into the data processing pipeline.
+If you think that you have found an error in the code or wish to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/BritPol/issues).
 
-We are happy for others to use our code for their own purposes, but ask that they do so *with attribution*.
-That is, you may reproduce, reuse, and change the code here as you see fit, but must state in each case that you based your analysis on our work.
+Your may use any BritPol code for your own purposes, but you must do so *with attribution*.
+That is, you may reproduce, reuse, and change the code here as you see fit, but must state in each case that you used BritPol to produce your work.
 The citations for each item in BritPol are as follows:
+
+### BritPol
+
+- **Documentation:** Bailey, J. (`r format(Sys.Date(), format = "%Y")`) BritPol v`r packageVersion("BritPol")`: User Guide and Data Codebook. Retrieved from doi.
+
+### PollBasePro
 
@@
 
-- **Documentation:** Bailey, J., M. Pack, and L. Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro v`r packageVersion("BritPol")`: User Guide and Codebook. Retrieved from doi.
-
 - **Paper:** Bailey, J., M.

### 2021-03-14 documentation/readme.Rmd
Fixed reference to data in plot

@@
     y = "Vote Share",
-    caption = "Based on data from BritPol, created by @PoliSciJack, @markpack, and @mansillo: www.github.com/jackobailey/BritPol"
+    caption = "Based on data from PollBasePro, created by @PoliSciJack, @markpack, and @mansillo"
   )

### 2021-03-15 documentation/paper.Rmd
Lower case project name and new documentation doi

@@
 title: |
-  | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(BritPol::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback.
+  | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(britpol::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback.
 We owe particular thanks to Chris Hanretty, Y, and Z.
@@
 date: |
-  | \small This version compiled `r stringr::str_remove(format(Sys.time(), '%d %B %Y'), "^0")` using PollBasePro `r paste0("v", packageVersion("BritPol"))`
+  | \small This version compiled `r stringr::str_remove(format(Sys.time(), '%d %B %Y'), "^0")` using PollBasePro `r paste0("v", packageVersion("britpol"))`
 abstract: |
@@
 It includes voting intention estimates for each of Britain's three largest parties on each day between the 1955 general election and the present.
-Given that the dataset covers `r format(nrow(BritPol::pollbasepro), big.mark = ",")` days in total, it is more comprehensive than any existing time series of public opinion in Britain.
+Given that the dataset covers `r format(nrow(britpol::pollbasepro), big.mark = ",")` days in total, it is more comprehensive than any existing time series of public opinion in Britain.
 As a result, we expect PollBasePro to be an important resource for students of British politics in the years to come.
@@
 classoption: a4paper
+linkcolor: black
+urlcolor: violet
+citecolor: black
 output: 
@@
 
-library(BritPol)
+library(britpol)
 library(kableExtra)
@@
 
-death_mod <- readRDS(here("models", paste0("death_mod_", packageVersion("BritPol"), ".rds")))
+death_mod <- readRDS(here("models", paste0("death_mod_", packageVersion("britpol"), ".rds")))
 
@@
 
-cor_all <- readRDS(here("models", paste0("cor_all_", packageVersion("BritPol"), ".rds")))
-cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("BritPol"), ".rds")))
-cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("BritPol"), ".rds")))
-cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("BritPol"), ".rds")))
+cor_all <- readRDS(here("models", paste0("cor_all_", packageVersion("britpol"), ".rds")))
+cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("britpol"), ".rds")))
+cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("britpol"), ".rds")))
+cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("britpol"), ".rds")))
 
@@
 In this paper, we introduce PollBasePro: the most comprehensive time series of British voting intention data assembled to date.
-The dataset contains `r format(nrow(BritPol::pollbasepro), big.mark = ",")` daily voting intention estimates for each of Britain's three largest parties, beginning at the 1955 General Election on `r format(min(pollbasepro$date), "%d %B %Y")` and ending on `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.
+The dataset contains `r format(nrow(britpol::pollbasepro), big.mark = ",")` daily voting intention estimates for each of Britain's three largest parties, beginning at the 1955 General Election on `r format(min(pollbasepro$date), "%d %B %Y")` and ending on `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.
 Furthermore, our data are well validated and follow the course of British political history.
@@
 To guard against this, we have hosted all of our materials online for others to inspect.
-If our users find any errors in our code or wish to make recommendations for future updates, we invite them to raise an issue on the project's [GitHub repository](https://github.com/jackobailey/BritPol/issues) or to [contact the authors directly](mailto:jack.bailey@manchester.ac.uk).
+If our users find any errors in our code or wish to make recommendations for future updates, we invite them to raise an issue on the project's [GitHub repository](https://github.com/jackobailey/britpol/issues) or to [contact the authors directly](mailto:jack.bailey@manchester.ac.uk).
 

### 2021-03-15 documentation/readme.Rmd
Lower case project name and new documentation doi

@@
 
-library(BritPol)
+library(britpol)
 library(tidyverse)
@@
 
-# BritPol
+# britpol
 
-BritPol is a data package for the `R` programming language.
+`britpol` is a data package for the `R` programming language.
 It includes two datasets: `pollbase` and `pollbasepro`.
@@
 The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.
-A user guide and codebook is available for `pollbasepro` [here](https://github.com/jackobailey/BritPol/blob/master/download/userguide.pdf) and an accompanying paper is available [here](https://github.com/jackobailey/BritPol/blob/master/download/paper.pdf).
+A user guide and codebook is available for `pollbasepro` [here](https://github.com/jackobailey/britpol/blob/master/download/userguide.pdf) and an accompanying paper is available [here](https://github.com/jackobailey/britpol/blob/master/download/paper.pdf).
 
-To install the latest version of BritPol, run the following code in `R`:
+To install the latest version of `britpol`, run the following code in `R`:
 
 ``` r
-devtools::install_github("jackobailey/BritPol")
+devtools::install_github("jackobailey/britpol")
 ```
@@
 These files include all necessary value and variable labels and should work seamlessly with both software packages.
-[Click here to download them](https://github.com/jackobailey/BritPol/tree/master/download).
+[Click here to download them](https://github.com/jackobailey/britpol/tree/master/download).
 
@@
 
-<center><img src="https://raw.githubusercontent.com/jackobailey/BritPol/master/documentation/_assets/timeplot_gh.png"></center>
+<center><img src="https://raw.githubusercontent.com/jackobailey/britpol/master/documentation/_assets/timeplot_gh.png"></center>
 
@@
 Like any project of this size, some minor mistakes might have crept into the data processing pipeline.
-If you think that you have found an error in the code or wish to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/BritPol/issues).
+If you think that you have found an error in the code or wish to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/britpol/issues).
 
-Your may use any BritPol code for your own purposes, but you must do so *with attribution*.
-That is, you may reproduce, reuse, and change the code here as you see fit, but must state in each case that you used BritPol to produce your work.
-The citations for each item in BritPol are as follows:
+Your may use the `britpol` codebase for your own purposes, but you must do so *with attribution*.
+That is, you may reproduce, reuse, and change the code here as you see fit, but must state in each case that you used britpol to produce your work.
+The citations for each item in `britpol` are as follows:
 
-### BritPol
+### britpol
 
-- **Documentation:** Bailey, J. (`r format(Sys.Date(), format = "%Y")`) BritPol v`r packageVersion("BritPol")`: User Guide and Data Codebook. Retrieved from doi.
+- **Documentation:** Bailey, J. (`r format(Sys.Date(), format = "%Y")`) britpol v`r packageVersion("britpol")`: User Guide and Data Codebook. Retrieved from https://doi.org/10.17605/OSF.IO/2M9GB.
 
@@
 Pack, and L.
-Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("BritPol")` [computer file], `r format(Sys.Date(), format = "%B %Y")`.
+Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("britpol")` [computer file], `r format(Sys.Date(), format = "%B %Y")`.
 Retrieved from https://doi.org/10.7910/DVN/3POIQW.

### 2021-03-15 documentation/userguide.Rmd
Lower case project name and new documentation doi

--- 2021-03-14 documentation/userguide.Rmd
@@
 title: |
-  | BritPol v`r packageVersion("BritPol")` (Beta)
+  | britpol v`r packageVersion("britpol")` (Beta)
   | User Guide and Data Codebook
@@
 
-cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("BritPol"), ".rds")))
-cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("BritPol"), ".rds")))
-cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("BritPol"), ".rds")))
+cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("britpol"), ".rds")))
+cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("britpol"), ".rds")))
+cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("britpol"), ".rds")))
 
@@
 
-# About BritPol
+# About britpol
 
-BritPol is a data package for the `R` programming language.
+`britpol` is a data package for the `R` programming language.
 It includes two datasets: `pollbase` and `pollbasepro`.
@@
 To guard against this, we have made all of our materials available for others to inspect.
-If you find an error in the code or wish to make a recommendation for a future update, we invite you to raise an issue on the BritPol GitHub repository.
+If you find an error in the code or wish to make a recommendation for a future update, we invite you to [raise an issue on the `britpol` GitHub repository](https://github.com/jackobailey/britpol/issues).
 
@@
 Pack, and L.
-Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("BritPol")` [computer file], `r format(Sys.Date(), format = "%B %Y")`.
+Mansillo (`r format(Sys.Date(), format = "%Y")`) PollBasePro: Daily Estimates of Aggregate Voting Intention in Great Britain from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")` v.`r packageVersion("britpol")` [computer file], `r format(Sys.Date(), format = "%B %Y")`.
 Retrieved from https://doi.org/10.7910/DVN/3POIQW.
 
-- **Documentation:** Bailey, J. (`r format(Sys.Date(), format = "%Y")`) BritPol v`r packageVersion("BritPol")`: User Guide and Data Codebook. Retrieved from doi.
+- **Documentation:** Bailey, J. (`r format(Sys.Date(), format = "%Y")`) britpol v`r packageVersion("britpol")`: User Guide and Data Codebook. Retrieved from https://doi.org/10.17605/OSF.IO/2M9GB.
 
@@
 
-# Using BritPol
+# Using britpol
 
-Getting started with BritPol in `R` is simple.
+Getting started with `britpol` in `R` is simple.
 It requires only three short steps: first, to install the package; second, to load the package; and, third, to load the data.
 Once you have taken these three steps, you can then begin analysing the data.
-Note that BritPol is not yet available on CRAN, the service that hosts most `R` packages.
-As such, it is not yet possible to install BritPol with `R`'s standard `install.packages()` function.
-Instead, we must install it directly from its GitHub repository.
+Note that `britpol` is not yet available on CRAN, the service that hosts most `R` packages.
+As such, it is not yet possible to install `britpol` with `R`'s standard `install.packages()` function.
+Instead, we must install it directly from its [GitHub repository](https://github.com/jackobailey/britpol).
 Thankfully this is straightforward and requires only that you run the following code in your `R` console:
@@
 ```{r install-pbp, eval = FALSE}
-# 1. Install the BritPol package from GitHub
-devtools::install_github("jackobailey/BritPol")
+# 1. Install the britpol package from GitHub
+devtools::install_github("jackobailey/britpol")
 
-# 2. Load the BritPol package in R
-library(BritPol)
+# 2. Load the britpol package in R
+library(britpol)
 
@@
 
-Though BritPol is first and foremost an `R` data package, we have sought to accommodate those who use Stata and SPSS too.
+Though `britpol` is first and foremost an `R` data package, we have sought to accommodate those who use Stata and SPSS too.
 To make this as easy as possible, we have made both the `pollbase` and `pollbasepro` datasets available as .dta and .sav files.
@@
 
-- ``r paste0("pollbase_", packageVersion("BritPol"), ".dta")``
-- ``r paste0("pollbasepro_", packageVersion("BritPol"), ".dta")``
-- ``r paste0("pollbase_", packageVersion("BritPol"), ".sav")``
-- ``r paste0("pollbasepro_", packageVersion("BritPol"), ".sav")``
+- ``r paste0("pollbase_", packageVersion("britpol"), ".dta")``
+- ``r paste0("pollbasepro_", packageVersion("britpol"), ".dta")``
+- ``r paste0("pollbase_", packageVersion("britpol"), ".sav")``
+- ``r paste0("pollbasepro_", packageVersion("britpol"), ".sav")``
 
@@
 To guard against this, and provide our users with a more in-depth look at our modelling process, we have hosted our entire data pipeline online for others to inspect.
-If our users find any errors in our code or wish to make recommendations for future updates, we invite them to raise an issue on the project's GitHub repository or to contact the authors directly.
+If our users find any errors in our code or wish to make recommendations for future updates, we invite them to [raise an issue on the project's GitHub repository](https://github.com/jackobailey/britpol/issues) or to [contact the authors directly](mailto:jack.bailey@manchester.ac.uk).
 
@@
 
-For the sake of openness and transparency, we provide a change log that lists all updates and changes made to BritPol over time.
-If you think that you have found a problem with either the data, code, or documentation, please raise an issue on the project's GitHub repository.
+For the sake of openness and transparency, we provide a change log that lists all updates and changes made to `britpol` over time.
+If you think that you have found a problem with either the data, code, or documentation, please [raise an issue on the project's GitHub repository](https://github.com/jackobailey/britpol/issues).
 

### 2021-03-15 data-raw/000_compile.R

@@ -5,7 +5,7 @@
 
 # Load packages
 
-library(BritPol)
+library(britpol)
 library(rmarkdown)
 library(here)
 

### 2021-03-15 documentation/readme.Rmd
Updated pollbasepro, fixed some references

@@
 
-As of `r str_remove(format(Sys.Date(), "%d %B %Y"), "^0")`, we estimate that **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "has", "have")` the largest base of support** with `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")` of the electorate intending to vote for them at the next election.
+As of `r str_remove(format(max(pollbasepro$date) "%d %B %Y"), "^0")`, we estimate that **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "has", "have")` the largest base of support** with `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")` of the electorate intending to vote for them at the next election.
 **They hold a lead over the `r txt_dta$party[2]`** of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`.

### 2021-03-15 documentation/readme.Rmd
Recompiled documentation after latest data update

--- 2021-03-15 documentation/readme.Rmd
@@
 
-As of `r str_remove(format(Sys.Date(), "%d %B %Y"), "^0")`, we estimate that **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "has", "have")` the largest base of support** with `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")` of the electorate intending to vote for them at the next election.
+As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, we estimate that **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "has", "have")` the largest base of support** with `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")` of the electorate intending to vote for them at the next election.
 **They hold a lead over the `r txt_dta$party[2]`** of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`.

### 2021-03-15 R/update_pollbasepro.R

@@ -1,6 +1,6 @@
 #' Update Voting Intention Polls, 2019-Present
 #'
-#' This function updates britpol to include the latest polling data and outputs Twitter content.
+#' This function updates the pollbasepro data to include the latest polling data and outputs Twitter content.
 #'
 #'
 #' @export

### 2021-03-17 documentation/paper.Rmd
Updated model to deal with errant end points and recompiled

@@
   | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(britpol::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback.
-We owe particular thanks to Chris Hanretty, Y, and Z.
-We would also like to extend a special thanks to all of the volunteers who have given their time to maintain such a comprehensive list of British opinion polling data on Wikipedia.}
+We owe particular thanks to Chris Hanretty, who inspired this project and provided much useful feedback.
+We would also like to thank X, Y, and Z for offering their time to review the manuscript.
+Finally, we would like to extend a special thanks to all of the volunteers who work to maintain such a comprehensive list of British opinion polling data on Wikipedia.}
 author: |

### 2021-03-17 documentation/readme.Rmd
Amended README text
Updated model to deal with errant end points and recompiled

--- 2021-03-15 documentation/readme.Rmd
@@
 
-`britpol` is a data package for the `R` programming language.
-It includes two datasets: `pollbase` and `pollbasepro`.
-The first provides a long-format and ready-to-analyse version of Mark Pack's dataset of historic British public opinion polls combined with more recent polling data from Wikipedia.
-The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.
-A user guide and codebook is available for `pollbasepro` [here](https://github.com/jackobailey/britpol/blob/master/download/userguide.pdf) and an accompanying paper is available [here](https://github.com/jackobailey/britpol/blob/master/download/paper.pdf).
+`{britpol}` is an `R` package that makes analysing British political data quick and simple.
+It contains two pre-formatted datasets, plus a host of useful functions.
+The first dataset, `pollbase`, is a long-format version of Mark Pack's dataset of historic British public opinion polls combined with more recent data from Wikipedia.
+The second dataset, `pollbasepro`, provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.
+[Stata and SPSS versions of the data are also available too](https://github.com/jackobailey/britpol/tree/master/download).
 
-To install the latest version of `britpol`, run the following code in `R`:
+To install the latest version of `{britpol}`, run the following code in `R`:
 
@@
 devtools::install_github("jackobailey/britpol")
-```
 
-We also provide `pollbase` and `pollbasepro` as .dta and .sav files for Stata and SPSS users.
-These files include all necessary value and variable labels and should work seamlessly with both software packages.
-[Click here to download them](https://github.com/jackobailey/britpol/tree/master/download).
-
-## Latest Polling Estimates
+## Latest Polling Estimates from PollBasePro
 
@@
 
-As of `r str_remove(format(Sys.Date(), "%d %B %Y"), "^0")`, we estimate that **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "has", "have")` the largest base of support** with `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")` of the electorate intending to vote for them at the next election.
+As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "has", "have")` the largest base of support** at around `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")` of the electorate.
 **They hold a lead over the `r txt_dta$party[2]`** of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`.
 **This puts the `r txt_dta$party[2]` in second place** on `r paste0(txt_dta$share[2], " (95% CI: ", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")` of the vote.
-**In third place is the `r txt_dta$party[3]`**, with support from `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")` of voters.
+**The `r txt_dta$party[3]` are in third place** with support from `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")` of voters.
 
@@
 
-Both `pollbase` and `pollbasepro` are living datasets.
-As such, users should try to use only the most recent version of the data when conducting their analyses.
-Like any project of this size, some minor mistakes might have crept into the data processing pipeline.
-If you think that you have found an error in the code or wish to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/britpol/issues).
+{britpol}, `pollbase`, and `pollbasepro` will change over time as elections come and go.
+Users should use only the most recent version of the package when conducting their analyses.
+Like any project, some minor mistakes might have crept into the code.
+If you think that you have found an error or would like to make a recommendation for a future update, please [raise an issue](https://github.com/jackobailey/britpol/issues).
 
-Your may use the `britpol` codebase for your own purposes, but you must do so *with attribution*.
-That is, you may reproduce, reuse, and change the code here as you see fit, but must state in each case that you used britpol to produce your work.
-The citations for each item in `britpol` are as follows:
+You may also use the `{britpol}` codebase for your own purposes in line with our license.
+But you must do so *with attribution*.
+That is, you may reproduce, reuse, and adapt the code as you see fit, but must state in each case that you used `{britpol}` to produce your work.
+The relevant citations are as follows:
 

### 2021-03-17 R/fit_model.R

@@ -79,6 +79,34 @@ fit_model <- function(data, init, final, party, alpha_init, alpha_final, refresh
         max_treedepth = 15
       )
 
+
+    # Get model summary
+
+    mod_sum <-
+      fit$summary(variables = "alpha") %>%
+      dplyr::filter(stringr::str_detect(variable, "alpha") == T) %>%
+      dplyr::mutate(
+        index =
+          variable %>%
+          stringr::str_remove("alpha\\[") %>%
+          stringr::str_remove("\\]"),
+        date = lubridate::as_date({{init}}) + (dplyr::row_number() - 1)
+      ) %>%
+      dplyr::select(
+        date,
+        est = mean,
+        sd
+      ) %>%
+      dplyr::mutate(
+        party = {{party}}
+      )
+
+
+    # Remove final case to prevent duplication
+
+    mod_sum <- mod_sum[1:(nrow(mod_sum)-1), ]
+
+
   } else if(init == "2019-12-12"){
 
     # Compile Stan model
@@ -127,29 +155,28 @@ fit_model <- function(data, init, final, party, alpha_init, alpha_final, refresh
         max_treedepth = 15
       )
 
+    # Get model summary
+
+    mod_sum <-
+      fit$summary(variables = "alpha") %>%
+      dplyr::filter(stringr::str_detect(variable, "alpha") == T) %>%
+      dplyr::mutate(
+        index =
+          variable %>%
+          stringr::str_remove("alpha\\[") %>%
+          stringr::str_remove("\\]"),
+        date = lubridate::as_date({{init}}) + (dplyr::row_number() - 1)
+      ) %>%
+      dplyr::select(
+        date,
+        est = mean,
+        sd
+      ) %>%
+      dplyr::mutate(
+        party = {{party}}
+      )
+
   }
-
-
-  # Get model summary
-
-  mod_sum <-
-    fit$summary(variables = "alpha") %>%
-    dplyr::filter(stringr::str_detect(variable, "alpha") == T) %>%
-    dplyr::mutate(
-      index =
-        variable %>%
-        stringr::str_remove("alpha\\[") %>%
-        stringr::str_remove("\\]"),
-      date = lubridate::as_date({{init}}) + (dplyr::row_number() - 1)
-    ) %>%
-    dplyr::select(
-      date,
-      est = mean,
-      sd
-    ) %>%
-    dplyr::mutate(
-      party = {{party}}
-    )
 
 
   # Return model summary to user

### 2021-03-17 data-raw/001_samplesizes.R

@@ -6,7 +6,7 @@
 
 # Load packages
 
-library(BritPol)
+library(britpol)
 library(tidyverse)
 library(lubridate)
 library(brms)
@@ -111,7 +111,7 @@ sample_mod <-
     chains = 4,
     threads = threading(3),
     max_treedepth = 20,
-    file = here("models", paste0("sample_mod_", packageVersion("BritPol")))
+    file = here("models", paste0("sample_mod_", packageVersion("britpol")))
   )
 
 

### 2021-03-17 data-raw/002_pollbase.R

@@ -6,7 +6,7 @@
 
 # Load packages
 
-library(BritPol)
+library(britpol)
 library(tidyverse)
 library(magrittr)
 library(lubridate)
@@ -646,12 +646,12 @@ usethis::use_data(
 
 write_dta(
   pollbase,
-  path = here("download", paste0("pollbase_", packageVersion("PollBasePro"), ".dta"))
+  path = here("download", paste0("pollbase_", packageVersion("britpol"), ".dta"))
 )
 
 write_sav(
   pollbase,
-  path = here("download", paste0("pollbase_", packageVersion("PollBasePro"), ".sav")),
+  path = here("download", paste0("pollbase_", packageVersion("britpol"), ".sav")),
   compress = T
 )
 

### 2021-03-17 data-raw/003_pollbasepro.R

@@ -7,7 +7,7 @@
 
 # Load packages
 
-library(BritPol)
+library(britpol)
 library(tidyverse)
 library(lubridate)
 library(labelled)
@@ -403,12 +403,12 @@ usethis::use_data(
 
 write_dta(
   pollbasepro,
-  path = here("download", paste0("pollbasepro_", packageVersion("PollBasePro"), ".dta"))
+  path = here("download", paste0("pollbasepro_", packageVersion("britpol"), ".dta"))
 )
 
 write_sav(
   pollbasepro,
-  path = here("download", paste0("pollbasepro_", packageVersion("PollBasePro"), ".sav")),
+  path = here("download", paste0("pollbasepro_", packageVersion("britpol"), ".sav")),
   compress = T
 )
 

### 2021-03-17 data-raw/004_validation.R

@@ -6,7 +6,7 @@
 
 # Load packages
 
-library(BritPol)
+library(britpol)
 library(tidyverse)
 library(lubridate)
 library(brms)
@@ -95,7 +95,7 @@ cor_con <-
     file =
       here(
         "models",
-        paste0("cor_con_", packageVersion("PollBasePro"))
+        paste0("cor_con_", packageVersion("britpol"))
       )
   )
 
@@ -119,7 +119,7 @@ cor_lab <-
     file =
       here(
         "models",
-        paste0("cor_lab_", packageVersion("PollBasePro"))
+        paste0("cor_lab_", packageVersion("britpol"))
       )
   )
 
@@ -143,7 +143,7 @@ cor_lib <-
     file =
       here(
         "models",
-        paste0("cor_lib_", packageVersion("PollBasePro"))
+        paste0("cor_lib_", packageVersion("britpol"))
       )
   )
 
@@ -175,7 +175,7 @@ cor_all <-
     file =
       here(
         "models",
-        paste0("cor_all_", packageVersion("PollBasePro"))
+        paste0("cor_all_", packageVersion("britpol"))
       )
   )
 

### 2021-03-17 data-raw/005_example.R

@@ -6,7 +6,7 @@
 
 # Load packages
 
-library(BritPol)
+library(britpol)
 library(tidyverse)
 library(lubridate)
 library(brms)

### 2021-03-17 documentation/readme.Rmd
Amended README

@@
 **This puts the `r txt_dta$party[2]` in second place** on `r paste0(txt_dta$share[2], " (95% CI: ", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")` of the vote.
-**The `r txt_dta$party[3]` are in third place** with support from `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")` of voters.
+**The `r txt_dta$party[3]` are in third place** with the support of `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")` of voters.
 

### 2021-03-17 documentation/readme.Rmd
Fixed minor error in README
Add hex sticker to README
Fixed issue with Cabin font and minor formatting issue in README

@@
 
+<img src="https://raw.githubusercontent.com/jackobailey/britpol/master/documentation/_assets/hex.png" alt="The britpol hexlogo" align="right" width="200" style="padding: 0 15px; float: right;"/>
+
 `{britpol}` is an `R` package that makes analysing British political data quick and simple.
@@
 devtools::install_github("jackobailey/britpol")
+```
 
@@
 
-{britpol}, `pollbase`, and `pollbasepro` will change over time as elections come and go.
+`{britpol}`, `pollbase`, and `pollbasepro` will change over time as elections come and go.
 Users should use only the most recent version of the package when conducting their analyses.

### 2021-03-17 documentation/userguide.Rmd
Fixed issue with Cabin font and minor formatting issue in README

@@
 cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("britpol"), ".rds")))
+
+# Create custom ggplot theme
+
+theme_bailey <- function(){
+  theme_minimal() +
+    theme(legend.title = element_text(family = "Cabin", face = "bold", size = rel(1)),
+                   text = element_text(family = "Cabin", color = "black", size = 8),
+                   plot.title = element_text(family = "Cabin", face = "bold", size = rel(1.4), hjust = 0),
+                   plot.subtitle = element_text(family = "Cabin", size = rel(1), hjust = 0, margin = margin(b = 10)),
+                   axis.line = element_line(lineend = "round"),
+                   axis.title.x = element_text(family = "Cabin", face = "bold", margin = margin(t = 10), size = rel(1)),
+                   axis.text.x = element_text(color = "black", size = rel(1)),
+                   axis.ticks.x = element_line(lineend = "round"),
+                   axis.title.y = element_text(family = "Cabin", face = "bold", size = rel(1)),
+                   axis.text.y = element_text(color = "black", size = rel(1)),
+                   strip.text = element_text(family = "Cabin", face = "bold", size = rel(1)),
+                   panel.spacing = unit(.3, "cm"),
+                   panel.grid.major.y = element_line(size = .5, lineend = "round"),
+                   panel.grid.minor.y = element_blank(),
+                   panel.grid.major.x = element_blank(),
+                   panel.grid.minor.x = element_blank()
+    )
+}
 

### 2021-03-17 documentation/readme.Rmd
Added link to license in README
Delete "also".

@@
 The second dataset, `pollbasepro`, provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.
-[Stata and SPSS versions of the data are also available too](https://github.com/jackobailey/britpol/tree/master/download).
+[Stata and SPSS versions of the data are available too](https://github.com/jackobailey/britpol/tree/master/download).
 
@@
 
-You may also use the `{britpol}` codebase for your own purposes in line with our license.
+You may also use the `{britpol}` codebase for your own purposes in line with [our license](https://github.com/jackobailey/britpol/blob/master/LICENSE.md).
 But you must do so *with attribution*.

### 2021-03-17 documentation/readme.Rmd
Change README image size

@@
     y = "Vote Share",
-    caption = "Based on data from PollBasePro, created by @PoliSciJack, @markpack, and @mansillo"
+    caption = "Made using PollBasePro by @PoliSciJack, @markpack, and @mansillo"
   )
@@
   path = here("documentation", "_assets"),
-  width = 6,
+  width = 3.5,
   height = 3.5,
@@
 
-<center><img src="https://raw.githubusercontent.com/jackobailey/britpol/master/documentation/_assets/timeplot_gh.png"></center>
+<img src="https://raw.githubusercontent.com/jackobailey/britpol/master/documentation/_assets/timeplot_gh.png" alt="Recent polling figures" align="right" width="400" style="padding: 0 15px; float: right;"/>
 

### 2021-03-17 documentation/readme.Rmd
Editted poll of polls section

@@
 
-As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "has", "have")` the largest base of support** at around `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")` of the electorate.
+**British Poll of Polls, `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`:**
+
+- **`r txt_dta$party[1]`:** `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")`
+- **`r txt_dta$party[2]`:** `r paste0(txt_dta$share[2], " (95% CI: ", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")`
+- **`r txt_dta$party[3]`:** `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")`
+
+As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party**.
 **They hold a lead over the `r txt_dta$party[2]`** of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`.
-**This puts the `r txt_dta$party[2]` in second place** on `r paste0(txt_dta$share[2], " (95% CI: ", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")` of the vote.
-**The `r txt_dta$party[3]` are in third place** with the support of `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")` of voters.
+**This puts the `r txt_dta$party[2]` in second place** and **the `r txt_dta$party[3]` in third place**.
 

### 2021-03-17 documentation/readme.Rmd
Editted poll of polls section

@@
 
-**British Poll of Polls, `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`:**
+British Poll of Polls, `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`:
 
-- **`r txt_dta$party[1]`:** `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")`
-- **`r txt_dta$party[2]`:** `r paste0(txt_dta$share[2], " (95% CI: ", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")`
-- **`r txt_dta$party[3]`:** `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")`
+- `r txt_dta$party[1]`: `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")`
+- `r txt_dta$party[2]`: `r paste0(txt_dta$share[2], " (95% CI: ", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")`
+- `r txt_dta$party[3]`: `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")`
 

### 2021-03-17 documentation/readme.Rmd
Update README images and text

--- 2021-03-17 documentation/readme.Rmd
@@
     theme(
-      legend.position = "bottom",
+      legend.position = "none",
       legend.title = element_blank(),
       text = element_text(family = "Cabin", color = "black", size = 8),
-      plot.title = element_text(family = "Cabin", face = "bold", size = rel(1.4), hjust = 0),
+      plot.title = element_blank(),
       plot.subtitle = element_text(family = "Cabin", size = rel(1), hjust = 0, margin = margin(b = 10)),
@@
   width = 3.5,
-  height = 3.5,
+  height = 3,
   units = "in",
@@
 
-- **`r txt_dta$party[1]`:** `r paste0(txt_dta$share[1], " (95% CI: ", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")`
-- **`r txt_dta$party[2]`:** `r paste0(txt_dta$share[2], " (95% CI: ", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")`
-- **`r txt_dta$party[3]`:** `r paste0(txt_dta$share[3], " (95% CI: ", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")`
+- **`r txt_dta$party[1]`:** `r paste0(txt_dta$share[1], " (", txt_dta$lower[1], " to ", txt_dta$upper[1], ")")`
+- **`r txt_dta$party[2]`:** `r paste0(txt_dta$share[2], " (", txt_dta$lower[2], " to ", txt_dta$upper[2], ")")`
+- **`r txt_dta$party[3]`:** `r paste0(txt_dta$share[3], " (", txt_dta$lower[3], " to ", txt_dta$upper[3], ")")`
 
-As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party**.
+As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, the `pollbasepro` model suggests that **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party** in Britain.
 **They hold a lead over the `r txt_dta$party[2]`** of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`.

### 2021-03-17 documentation/readme.Rmd
Smaller image
Reduce image height
Minor text edit

@@
   width = 3.5,
-  height = 3,
+  height = 2,
   units = "in",
@@
 
-As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, the `pollbasepro` model suggests that **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party** in Britain.
+As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, `pollbasepro` suggests that **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party** in Britain.
 **They hold a lead over the `r txt_dta$party[2]`** of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`.

### 2021-03-17 documentation/readme.Rmd
Make image a little taller
Remove bold font face

@@
   width = 3.5,
-  height = 2,
+  height = 2.2,
   units = "in",
@@
 
-As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, `pollbasepro` suggests that **the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party** in Britain.
-**They hold a lead over the `r txt_dta$party[2]`** of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`.
-**This puts the `r txt_dta$party[2]` in second place** and **the `r txt_dta$party[3]` in third place**.
+As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, `pollbasepro` suggests that the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party in Britain.
+They hold a lead over the `r txt_dta$party[2]` of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`.
+This puts the `r txt_dta$party[2]` in second place and the `r txt_dta$party[3]` in third place.
 

### 2021-03-17 R_int/fit_model.R
Moved some functions to an internal folder to remove cumbersome dependencies like Stan

@@ -9,7 +9,6 @@
 #' @param alpha_init The party's vote share at the initial election.
 #' @param alpha_final The party's vote share at the final election.
 #' @param refresh How often to report model iterations. Defaults to 0.
-#' @export
 
 fit_model <- function(data, init, final, party, alpha_init, alpha_final, refresh = 0){
 

### 2021-03-17 data-raw/000_compile.R

@@ -10,6 +10,14 @@ library(rmarkdown)
 library(here)
 
 
+# Load internal functions
+
+for(i in dir(here("R_int"))){
+  source(here("R_int", i))
+  rm(i)
+}
+
+
 
 # 2. Compile data and models ----------------------------------------------
 

### 2021-03-17 data-raw/001_samplesizes.R

@@ -26,6 +26,14 @@ timeline <-
   na.omit()
 
 
+# Load internal functions
+
+for(i in dir(here("R_int"))){
+  source(here("R_int", i))
+  rm(i)
+}
+
+
 
 # 2. Transform data -------------------------------------------------------
 

### 2021-03-17 data-raw/002_pollbase.R

@@ -62,6 +62,14 @@ pollbase <-
 load(here("R", "sysdata.rda"))
 
 
+# Load internal functions
+
+for(i in dir(here("R_int"))){
+  source(here("R_int", i))
+  rm(i)
+}
+
+
 
 # 2. Transform PollBase data ----------------------------------------------
 

### 2021-03-17 data-raw/004_validation.R

@@ -65,6 +65,13 @@ lib <-
   na.omit()
 
 
+# Load internal functions
+
+for(i in dir(here("R_int"))){
+  source(here("R_int", i))
+  rm(i)
+}
+
 
 # 3. Fit correlation models -----------------------------------------------
 
@@ -183,15 +190,6 @@ cor_all <-
 # Let's now combine these models into a list
 
 cor_mods <- list(cor_all, cor_con, cor_lab, cor_lib)
-
-
-# We'll now save the files so that we can call them in our unit tests
-
-usethis::use_data(
-  cor_mods,
-  internal = TRUE,
-  overwrite = TRUE
-)
 
 
 # Finally, we'll install and restart the package so that subsequent scripts

### 2021-03-17 data-raw/005_example.R

@@ -32,6 +32,14 @@ pollbasepro <-
   )
 
 
+# Load internal functions
+
+for(i in dir(here("R_int"))){
+  source(here("R_int", i))
+  rm(i)
+}
+
+
 
 # 2. Transform data -------------------------------------------------------
 
@@ -117,7 +125,7 @@ death_mod <-
     file =
       here(
         "models",
-        paste0("death_mod_", packageVersion("BritPol"))
+        paste0("death_mod_", packageVersion("britpol"))
       )
   )
 

### 2021-03-17 tests/testthat/tests.pollbase.R

@@ -7,9 +7,6 @@
 # Load packages
 
 library(britpol)
-library(dplyr)
-library(purrr)
-library(here)
 
 
 

### 2021-03-17 tests/testthat/tests.pollbasepro.R

@@ -7,18 +7,6 @@
 # Load packages
 
 library(britpol)
-library(dplyr)
-library(purrr)
-library(brms)
-library(here)
-
-
-# Load validation/correlation models
-
-cor_all <- britpol:::cor_mods[[1]]
-cor_con <- britpol:::cor_mods[[2]]
-cor_lab <- britpol:::cor_mods[[3]]
-cor_lib <- britpol:::cor_mods[[4]]
 
 
 
@@ -68,15 +56,15 @@ test_that("All voting intention estimates are between 0 and 1", {
 
 test_that("Correlations between voting intention figures are negative", {
   expect_lt(
-    median(pluck(posterior_samples(cor_all, "rescor__libest__conest"), 1)),
+    cor.test(pollbasepro$lib_est, pollbasepro$con_est)$estimate,
     0
   )
   expect_lt(
-    median(pluck(posterior_samples(cor_all, "rescor__libest__labest"), 1)),
+    cor.test(pollbasepro$lib_est, pollbasepro$lab_est)$estimate,
     0
   )
   expect_lt(
-    median(pluck(posterior_samples(cor_all, "rescor__conest__labest"), 1)),
+    cor.test(pollbasepro$con_est, pollbasepro$lab_est)$estimate,
     0
   )
 })
@@ -86,15 +74,15 @@ test_that("Correlations between voting intention figures are negative", {
 
 test_that("Correlations between voting intention figures are negative", {
   expect_gt(
-    median(pluck(posterior_samples(cor_con, "rescor"), 1)),
+    cor.test(pollbasepro$con_est[match(pollbase$end, pollbasepro$date)], pollbase$con)$estimate,
     0.8
   )
   expect_gt(
-    median(pluck(posterior_samples(cor_lab, "rescor"), 1)),
+    cor.test(pollbasepro$lab_est[match(pollbase$end, pollbasepro$date)], pollbase$lab)$estimate,
     0.8
   )
   expect_gt(
-    median(pluck(posterior_samples(cor_lib, "rescor"), 1)),
+    cor.test(pollbasepro$lib_est[match(pollbase$end, pollbasepro$date)], pollbase$lib)$estimate,
     0.8
   )
 })

### 2021-03-17 documentation/readme.Rmd
Image slightly larger
Amended text in README

@@
   width = 3.5,
-  height = 2.2,
+  height = 2.3,
   units = "in",
@@
 As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, `pollbasepro` suggests that the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party in Britain.
-They hold a lead over the `r txt_dta$party[2]` of `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (95% CI: ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`.
+They hold a lead over the `r txt_dta$party[2]` of around `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`.
 This puts the `r txt_dta$party[2]` in second place and the `r txt_dta$party[3]` in third place.

### 2021-03-19 documentation/readme.Rmd
Recompile, remove Stata/SPSS versions, new add functions

@@
 The first dataset, `pollbase`, is a long-format version of Mark Pack's dataset of historic British public opinion polls combined with more recent data from Wikipedia.
-The second dataset, `pollbasepro`, provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.
-[Stata and SPSS versions of the data are available too](https://github.com/jackobailey/britpol/tree/master/download).
+The second dataset, `pollbasepro`, provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties from `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` to `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.
 
@@
 
-You may also use the `{britpol}` codebase for your own purposes in line with [our license](https://github.com/jackobailey/britpol/blob/master/LICENSE.md).
+You may also use the `{britpol}` codebase for your own purposes in line with [its license](https://github.com/jackobailey/britpol/blob/master/LICENSE.md).
 But you must do so *with attribution*.

### 2021-03-19 documentation/userguide.Rmd
Recompile, remove Stata/SPSS versions, new add functions

@@
 
-# About britpol
+# About `britpol`
 
-`britpol` is a data package for the `R` programming language.
-It includes two datasets: `pollbase` and `pollbasepro`.
-The first provides a long-format and ready-to-analyse version of Mark Pack's [-@pack2021] dataset of historic British public opinion polls combined with more recent polling data from Wikipedia.
-The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.
+`britpol` is an `R` package that makes analysing British political data quick and simple.
+It contains two pre-formatted datasets, plus a host of useful functions.
+The first dataset, `pollbase`, is a long-format version of Mark Pack's [-@pack2021] dataset of historic British public opinion polls combined with more recent data from Wikipedia.
+The second dataset, `pollbasepro`, provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.
 
-Both `pollbase` and `pollbasepro` are *living datasets*.
-Thus, users should endeavour to use only the most recent version of the data when conducting their analyses.
-This will become more important in the future, as we intend to add new polls and estimates over time.
-Likewise, we cannot rule out that minor mistakes might have crept into our data processing pipeline.
-To guard against this, we have made all of our materials available for others to inspect.
-If you find an error in the code or wish to make a recommendation for a future update, we invite you to [raise an issue on the `britpol` GitHub repository](https://github.com/jackobailey/britpol/issues).
+`britpol` will change as elections come and go.
+Users should only use the most recent version of the package in their research.
+Like any project, some minor mistakes might have crept into the code.
+If you think that you have found an error, please [raise an issue on the `britpol` GitHub repository](https://github.com/jackobailey/britpol/issues).
 
-# Citing the Data
+# Citing `britpol` and the PollBasePro Data
 
-If you use the `pollbasepro` data, you should also cite it.
-This is good practice and also allows us monitor how the data have been used.
-The `pollbasepro` project comprises three items: the data, this user guide, and a companion paper.
-The citations for each item are as follows:
+You may also use the `britpol` codebase for your own purposes in line with [its license](https://github.com/jackobailey/britpol/blob/master/LICENSE.md).
+But you must do so *with attribution*.
+That is, you may reproduce, reuse, and adapt the code as you see fit, but must state in each case that you used `britpol` to produce your work.
+The relevant citation is as follows:
+
+- Bailey, J. (`r format(Sys.Date(), format = "%Y")`) britpol v`r packageVersion("britpol")`: User Guide and Data Codebook. Retrieved from https://doi.org/10.17605/OSF.IO/2M9GB.
+
+Likewise, if you use the `pollbasepro` dataset, you should cite it too. This project comprises two elements: the dataset itself and a companion paper. The citations for each item are as follows:
 
@@
 
-- **Documentation:** Bailey, J. (`r format(Sys.Date(), format = "%Y")`) britpol v`r packageVersion("britpol")`: User Guide and Data Codebook. Retrieved from https://doi.org/10.17605/OSF.IO/2M9GB.
-
 - **Paper:** Bailey, J., M.
@@
 
-# Using britpol
+# Using `britpol`
 
-Getting started with `britpol` in `R` is simple.
-It requires only three short steps: first, to install the package; second, to load the package; and, third, to load the data.
-Once you have taken these three steps, you can then begin analysing the data.
+Getting started with `britpol` requires only three short steps: first, to install the package; second, to load the package; and, third, to load any data you want to use.
+Once you have taken these three steps, you can then begin your analysis.
 Note that `britpol` is not yet available on CRAN, the service that hosts most `R` packages.
@@
 
-Though `britpol` is first and foremost an `R` data package, we have sought to accommodate those who use Stata and SPSS too.
-To make this as easy as possible, we have made both the `pollbase` and `pollbasepro` datasets available as .dta and .sav files.
-These include all necessary value and variable labels and should work seamlessly with both software packages.
-You can download the latest version of the data by clicking the links below:
+Though `britpol` is first and foremost an `R` data package, the data are available for Stata and SPSS users too.
+To download the `pollbase` and `pollbasepro` datasets in .dta and .sav format [click here](https://github.com/jackobailey/britpol/tree/master/download).
 
-- ``r paste0("pollbase_", packageVersion("britpol"), ".dta")``
-- ``r paste0("pollbasepro_", packageVersion("britpol"), ".dta")``
-- ``r paste0("pollbase_", packageVersion("britpol"), ".sav")``
-- ``r paste0("pollbasepro_", packageVersion("britpol"), ".sav")``
+# Functions
+
+# Data
+
+## `pollbase` (Historical British Election Polls from `r format(min(pollbase$start), "%Y")` to `r format(max(pollbase$end), "%Y")`)
+
+### Variable List
+
+```{r pollbase-details, echo = F}
+
+make_table(pollbase)
+
+```
+
+\pagebreak
+
+## `pollbasepro` (Daily British Voting Intention from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")`)
+
+### Analysing `pollbasepro`
 
@@
 \pagebreak
+
+### Variable List
+
+```{r pollbasepro-details, echo = F}
+
+make_table(pollbasepro)
+
+```
 
@@
 
-# Variable List: PollBase (Historical British Election Polls from `r format(min(pollbase$start), "%Y")` to `r format(max(pollbase$end), "%Y")`)
-
-```{r pollbase-details, echo = F}
-
-make_table(pollbase)
-
-```
-
-\pagebreak
-
-# Variable List: PollBasePro (Daily British Voting Intention from `r format(min(pollbasepro$date), "%Y")` to `r format(max(pollbasepro$date), "%Y")`)
-
-```{r pollbasepro-details, echo = F}
-
-make_table(pollbasepro)
-
-```
-
-\pagebreak
-
 # Change Log

### 2021-03-19 R/add.R

@@ -1,0 +1,338 @@
+#' Add Prime Minister to Dated Datasets
+#'
+#' It's often useful to know who the Prime Minister was at any point in time when analysing political data. This function takes a dataset that includes a dated variable and adds to it a new column that shows who the Prime Minister was at each moment in time.
+#'
+#' @param data A dataset that includes a date variable.
+#' @param date The name of your date variable in your data.
+#' @param name What to call the new column of Prime Ministers. Defaults to "prime_minister".
+#' @return A tibble of data.
+#' @examples
+#' dta <- data.frame(date = seq.Date(as.Date("2000-01-01"), as.Date("2020-01-01"), by = "year"))
+#' add_pm(data = dta, date = "date", name = "prime_minister")
+#' @export
+
+add_pm <- function(data = NULL, date = "date", name = "prime_minister"){
+
+  # Return an error if the user provided no data
+
+  if(is.null(data) == T){
+    stop("You didn't provide any data! Use the 'data' argument (e.g. 'data = pollbase').")
+  }
+
+
+  # Return an error if the user didn't provide a date column
+
+  if(is.null(date) == T){
+    stop("You didn't provide a date column to use! Try the 'date' argument (e.g. date = 'date').")
+  }
+
+
+  # Return error if there is no date column based on the name they supplied
+
+  if(length(names(data)[names(data) == date]) == 0){
+    stop(
+      paste0(
+        "It doesn't look like your data contains a column called '",
+        date,
+        "'. Did you mean to use a different column? If so, try using the 'date' argument (e.g. date = 'end_point')."
+      )
+    )
+  }
+
+
+  # Return an error if the user provide a non-character name
+
+  if(is.character(name) == F){
+    stop("The name needs to be a character vector! I.e. it should be in quotation marks!")
+  }
+
+
+  # Call default data in case the user has editted them
+
+  data("prime_ministers")
+
+
+  # If everything's ok, return the relevant PM for each date
+
+  data <-
+    cbind(
+      data,
+      lookup_interval(
+        lookup_date = data[[date]],
+        interval_data = prime_ministers,
+        variable = "prime_minister"
+      )
+    ) %>%
+    tibble::tibble()
+
+
+  # Rename the column
+
+  names(data)[names(data) == "prime_minister"] <- name
+
+
+  # Return to user
+
+  return(data)
+
+}
+
+
+#' Add Prime Minister's Party to Dated Datasets
+#'
[…]

### 2021-03-19 R/data.R

@@ -1,0 +1,98 @@
+#' Raw PollBase data in long-format
+#'
+#' A dataset containing Mark Pack's raw pollbase figures for each of Britain's three main parties, tidied and converted to long-format for easy analysis.
+#'
+#' @format A data frame:
+#' \describe{
+#'   \item{id}{Unique poll identification number}
+#'   \item{election}{Date of last general election}
+#'   \item{govt}{Largest party in government after the last general election}
+#'   \item{start}{First day of fieldwork}
+#'   \item{end}{Last day of fieldwork}
+#'   \item{pollster}{Polling company that conducted the poll}
+#'   \item{n}{Sample size}
+#'   \item{con}{Voting intention: Conservative}
+#'   \item{lab}{Voting intention: Labour}
+#'   \item{lib}{Voting intention: Liberal}
+#'   \item{con_ldr}{Leader of the Conservative Party}
+#'   \item{lab_ldr}{Leader of the Labour Party}
+#'   \item{lib_ldr}{Leader of the Liberals (various forms)}
+#' }
+"pollbase"
+
+
+#' Daily Estimates of British Voting Intention, 1955 to Present
+#'
+#' A dataset containing daily estimates of aggregate voting intention in Britain for each of the country's three largest parties between 1955 and the present.
+#'
+#' @format A data frame:
+#' \describe{
+#'   \item{date}{Date}
+#'   \item{election}{Date of last general election}
+#'   \item{govt}{Largest party in government after the last general election}
+#'   \item{con_est}{Posterior mean: Conservative voting intention}
+#'   \item{con_err}{Posterior error: Conservative voting intention}
+#'   \item{lab_est}{Posterior mean: Labour voting intention}
+#'   \item{lab_err}{Posterior error: Labour voting intention}
+#'   \item{lib_est}{Posterior mean: Liberal voting intention}
+#'   \item{lib_err}{Posterior error: Liberal voting intention}
+#'   \item{con_ldr}{Leader of the Conservative Party}
+#'   \item{lab_ldr}{Leader of the Labour Party}
+#'   \item{lib_ldr}{Leader of the Liberals (various forms)}
+#'   \item{week}{Weekly subset indicator}
+#'   \item{month}{Monthly subset indicator}
+#'   \item{quarter}{Quarterly subset indicator}
+#'   \item{year}{Yearly subset indicator}
+#' }
+"pollbasepro"
+
+
+#'  List of "Red Wall" Constituencies
+#'
[…]

### 2021-03-19 R/pollbase.R

@@ -1,21 +1,0 @@
-#' Raw PollBase data in long-format
-#'
-#' A dataset containing Mark Pack's raw pollbase figures for each of Britain's three main parties, tidied and converted to long-format for easy analysis.
-#'
-#' @format A data frame:
-#' \describe{
-#'   \item{id}{Unique poll identification number}
-#'   \item{election}{Date of last general election}
-#'   \item{govt}{Largest party in government after the last general election}
-#'   \item{start}{First day of fieldwork}
-#'   \item{end}{Last day of fieldwork}
-#'   \item{pollster}{Polling company that conducted the poll}
-#'   \item{n}{Sample size}
-#'   \item{con}{Voting intention: Conservative}
-#'   \item{lab}{Voting intention: Labour}
-#'   \item{lib}{Voting intention: Liberal}
-#'   \item{con_ldr}{Leader of the Conservative Party}
-#'   \item{lab_ldr}{Leader of the Labour Party}
-#'   \item{lib_ldr}{Leader of the Liberals (various forms)}
-#' }
-"pollbase"

### 2021-03-19 R/utils.R

@@ -1,0 +1,1644 @@
+#' Jack Bailey's Colour Palette.
+#'
+#' This is a convenience function that makes it easier for me to make plots that use colours I like.
+#' @param ... The name of the colour you want.
+#'
+
+bailey_colours <- function(...) {
+
+  choice <- c(...)
+
+  cols <- c(
+    `red` = "#D10B0C",
+    `red2` = "#D52122",
+    `red3` = "#D93738",
+    `red4` = "#DD4D4E",
+    `red5` = "#E16364",
+    `red6` = "#E5797A",
+    `red7` = "#EA9090",
+    `red8` = "#EEA6A6",
+    `red9` = "#F2BCBC",
+    `red10` = "#F6D2D2",
+    `blue` = "#0D68C3",
+    `blue2` = "#2375C8",
+    `blue3` = "#3983CD",
+    `blue4` = "#4F91D3",
+    `blue5` = "#659ED8",
+    `blue6` = "#7BACDE",
+    `blue7` = "#91BAE3",
+    `blue8` = "#A7C8E9",
+    `blue9` = "#BDD5EE",
+    `blue10` = "#D3E3F4",
+    `grey` = "#5C5C5C",
+    `grey2` = "#6A6A6A",
+    `grey3` = "#797979",
+    `grey4` = "#888888",
+    `grey5` = "#979797",
+    `grey6` = "#A6A6A6",
+    `grey7` = "#B4B4B4",
+    `grey8` = "#C3C3C3",
+    `grey9` = "#D2D2D2",
+    `grey10` = "#E1E1E1",
+    `black` = "#000000",
+    `white` = "#FFFFFF"
+  )
+
+  if (is.null(choice)) return(cols)
+
+  `names<-`(cols[choice], NULL)
+}
+
+
+#' Fit Poll Pooling Model
+#'
+#' This function provides a simple way to fit a variant of Simon Jackman's "polling the polls" model.
+#'
+#' @param data Raw pollbase data.
+#' @param init Initial election date.
+#' @param final Final election date.
+#' @param party A string reflecting a party. Either "con", "lab", or "lib".
+#' @param alpha_init The party's vote share at the initial election.
+#' @param alpha_final The party's vote share at the final election.
+#' @param refresh How often to report model iterations. Defaults to 0.
+
+fit_model <- function(data, init, final, party, alpha_init, alpha_final, refresh = 0){
+
+  # Get pipe from Magrittr
+
[…]

### 2021-03-19 R_int/fit_model.R

@@ -1,185 +1,0 @@
-#' Fit Poll Pooling Model
-#'
-#' This function provides a simple way to fit a variant of Simon Jackman's "polling the polls" model.
-#'
-#' @param data Raw pollbase data.
-#' @param init Initial election date.
-#' @param final Final election date.
-#' @param party A string reflecting a party. Either "con", "lab", or "lib".
-#' @param alpha_init The party's vote share at the initial election.
-#' @param alpha_final The party's vote share at the final election.
-#' @param refresh How often to report model iterations. Defaults to 0.
-
-fit_model <- function(data, init, final, party, alpha_init, alpha_final, refresh = 0){
-
-  # Get pipe from Magrittr
-
-  `%>%` <- magrittr::`%>%`
-
-
-  # Print party and election
-
-  print(paste0("Fitting model: ", party, " ", init))
-
-
-  # Subset data
-
-  data <- data[data$election == init, ]
-
-
-  # Run model
-
-  if(init < "2019-12-12"){
-
-    # Compile Stan model
-
-    model <-
-      cmdstanr::cmdstan_model(
-        here::here("models", "model_2anchors.stan"),
-        cpp_options = list(stan_threads = TRUE)
-      )
-
-
-    # Create data for Stan
-
-    stan_data <-
-      list(
-        N = nrow(data),
-        T = (lubridate::interval(init, final)/lubridate::days(1)) + 1,
-        P = length(unique(data$pollster)),
-        y = data[[party]],
-        s = sqrt((data[[party]]*(1 - data[[party]]))/(ifelse(is.na(data$n) == T, data$n_est, data$n)/data$days)),
-        index = data$index,
-        pollster = as.numeric(factor(data$pollster)),
-        alpha_init = alpha_init,
-        alpha_final = alpha_final
-      )
-
-
-    # Sample from model
-
-    fit <-
-      model$sample(
-        data = stan_data,
-        seed = 666,
-        chains = 4,
-        parallel_chains = 4,
-        threads_per_chain = 3,
-        refresh = refresh,
-        show_messages = FALSE,
-        init =
-          list(
-            list(alpha = rep(alpha_init, nrow(data))),
-            list(alpha = rep(alpha_init, nrow(data))),
-            list(alpha = rep(alpha_init, nrow(data))),
-            list(alpha = rep(alpha_init, nrow(data)))
-          ),
[…]

### 2021-03-19 R_int/get_2015_polls.R

@@ -1,212 +1,0 @@
-#' Get Voting Intention Polls, 2010-2015
-#'
-#' This function downloads and tidies polling data for the 2010 to 2015 period from Wikipedia.
-#'
-#' @export
-
-get_2015_polls <- function(){
-
-  # Get pipe from Magrittr
-
-  `%>%` <- magrittr::`%>%`
-
-
-  # We'll get the data we need from Wikipedia. This is useful because there
-  # are a whole host of people who keep these pages up to date and it means
-  # that we don't have to manage data collection ourselves.
-
-  url1 <- "https://w.wiki/365k"
-  url2 <- "https://w.wiki/365o"
-
-
-  # Now, we'll use the htmltab() function to scrape the contents of the tables
-  # on the page.
-
-  dta_10 <-
-    htmltab::htmltab(url1, 3) %>%
-    dplyr::select(
-      date = `Date(s)conducted`,
-      pollster = `Polling organisation/client`,
-      n = `Sample size`,
-      con = Con,
-      lab = Lab,
-      lib = `Lib Dem`
-    ) %>%
-    dplyr::mutate(date = paste(date, "2010"))
-
-  dta_11 <-
-    htmltab::htmltab(url1, 2) %>%
-    dplyr::select(
-      date = `Date(s)conducted`,
-      pollster = `Polling organisation/client`,
-      n = `Sample size`,
-      con = Con,
-      lab = Lab,
-      lib = `Lib Dem`
-    ) %>%
-    dplyr::mutate(date = paste(date, "2011"))
-
-  dta_12 <-
-    htmltab::htmltab(url1, 1) %>%
-    dplyr::select(
-      date = `Date(s)conducted`,
-      pollster = `Polling organisation/client`,
-      n = `Sample size`,
-      con = Con,
-      lab = Lab,
-      lib = `Lib Dem`
-    ) %>%
-    dplyr::mutate(date = paste(date, "2012"))
-
-  dta_13 <-
-    htmltab::htmltab(url2, 5) %>%
-    dplyr::select(
-      date = `Date(s)conducted`,
-      pollster = `Polling organisation/client`,
-      n = `Sample size`,
-      con = Con,
-      lab = Lab,
-      lib = `Lib Dem`
-    ) %>%
-    dplyr::mutate(date = paste(date, "2013"))
-
-  dta_14 <-
-    htmltab::htmltab(url2, 4) %>%
-    dplyr::select(
-      date = `Date(s)conducted`,
[…]

### 2021-03-19 R_int/get_2017_polls.R

@@ -1,175 +1,0 @@
-#' Get Voting Intention Polls, 2015-2017
-#'
-#' This function downloads and tidies polling data for the 2015 to 2017 period from Wikipedia.
-#'
-#' @export
-
-get_2017_polls <- function(){
-
-  # Get pipe from Magrittr
-
-  `%>%` <- magrittr::`%>%`
-
-
-  # We'll get the data we need from Wikipedia. This is useful because there
-  # are a whole host of people who keep these pages up to date and it means
-  # that we don't have to manage data collection ourselves.
-
-  url <- "https://w.wiki/365p"
-
-
-  # Now, we'll use the htmltab() function to scrape the contents of the tables
-  # on the page.
-
-  dta_15 <-
-    htmltab::htmltab(url, 4) %>%
-    dplyr::select(
-      date = `Date(s)conducted`,
-      pollster = `Polling organisation/client`,
-      n = `Sample size`,
-      con = Con,
-      lab = Lab,
-      lib = `Lib Dem`
-    ) %>%
-    dplyr::mutate(date = paste(date, "2015"))
-
-  dta_16 <-
-    htmltab::htmltab(url, 3) %>%
-    dplyr::select(
-      date = `Date(s)conducted`,
-      pollster = `Polling organisation/client`,
-      n = `Sample size`,
-      con = Con,
-      lab = Lab,
-      lib = `Lib Dem`
-    ) %>%
-    dplyr::mutate(date = paste(date, "2016"))
-
-  dta_17 <-
-    htmltab::htmltab(url, 2) %>%
-    dplyr::select(
-      date = `Date(s)conducted`,
-      pollster = `Polling organisation/client`,
-      n = `Sample size`,
-      con = Con,
-      lab = Lab,
-      lib = `Lib Dem`
-    ) %>%
-    dplyr::mutate(date = paste(date, "2017"))
-
-
-  # Now we'll merge the data together
-
-  dta <- rbind(dta_15, dta_16, dta_17)
-
-
-  # At the moment, the data contain rows that include only information on the
-  # events that came to pass in UK politics. We don't need these, so we will
-  # remove them from the data.
-
-  dta <-
-    dta %>%
-    dplyr::filter(!(pollster == con))
-
-
-  # We'll also remove the actual election results themselves.
-
-  dta <-
-    dta %>%
-    dplyr::filter(stringr::str_detect(pollster, "election|Election") == F)
-
-
[…]

### 2021-03-19 R_int/get_2019_polls.R

@@ -1,175 +1,0 @@
-#' Get Voting Intention Polls, 2017-2019
-#'
-#' This function downloads and tidies polling data for the 2017 to 2019 period from Wikipedia.
-#'
-#' @export
-
-get_2019_polls <- function(){
-
-  # Get pipe from Magrittr
-
-  `%>%` <- magrittr::`%>%`
-
-
-  # We'll get the data we need from Wikipedia. This is useful because there
-  # are a whole host of people who keep these pages up to date and it means
-  # that we don't have to manage data collection ourselves.
-
-  url <- "https://w.wiki/35RK"
-
-
-  # Now, we'll use the htmltab() function to scrape the contents of the tables
-  # on the page.
-
-  dta_17 <-
-    htmltab::htmltab(url, 4) %>%
-    dplyr::select(
-      date = `Date(s)conducted`,
-      pollster = `Pollster/client(s)`,
-      n = `Samplesize`,
-      con = Con,
-      lab = Lab,
-      lib = `Lib Dem`
-    ) %>%
-    dplyr::mutate(date = paste(date, "2017"))
-
-  dta_18 <-
-    htmltab::htmltab(url, 3) %>%
-    dplyr::select(
-      date = `Date(s)conducted`,
-      pollster = `Pollster/client(s)`,
-      n = `Samplesize`,
-      con = Con,
-      lab = Lab,
-      lib = `Lib Dem`
-    ) %>%
-    dplyr::mutate(date = paste(date, "2018"))
-
-  dta_19 <-
-    htmltab::htmltab(url, 2) %>%
-    dplyr::select(
-      date = `Date(s)conducted`,
-      pollster = `Pollster/client(s)`,
-      n = `Samplesize`,
-      con = Con,
-      lab = Lab,
-      lib = `Lib Dem`
-    ) %>%
-    dplyr::mutate(date = paste(date, "2019"))
-
-
-  # Now we'll merge the data together
-
-  dta <- rbind(dta_17, dta_18, dta_19)
-
-
-  # At the moment, the data contain rows that include only information on the
-  # events that came to pass in UK politics. We don't need these, so we will
-  # remove them from the data.
-
-  dta <-
-    dta %>%
-    dplyr::filter(!(pollster == con))
-
-
-  # We'll also remove the actual election results themselves.
-
-  dta <-
-    dta %>%
-    dplyr::filter(stringr::str_detect(pollster, "election|Election") == F)
-
-
[…]

### 2021-03-19 R_int/get_new_polls.R

@@ -1,163 +1,0 @@
-#' Get Voting Intention Polls, 2019-Present
-#'
-#' This function downloads and tidies polling data for the 2019-Present period from Wikipedia.
-#'
-#' @export
-
-get_new_polls <- function(){
-
-  # Get pipe from Magrittr
-
-  `%>%` <- magrittr::`%>%`
-
-
-  # We'll get the data we need from Wikipedia. This is useful because there
-  # are a whole host of people who keep these pages up to date and it means
-  # that we don't have to manage data collection ourselves.
-
-  url <- "https://w.wiki/365q"
-
-
-  # Now, we'll use the htmltab() function to scrape the contents of the tables
-  # on the page.
-
-  dta_20 <-
-    htmltab::htmltab(url, 3) %>%
-    dplyr::select(
-      date = Datesconducted,
-      pollster = Pollster,
-      n = Samplesize,
-      con = Con,
-      lab = Lab,
-      lib = `Lib Dem`
-    ) %>%
-    dplyr::mutate(date = paste(date, "2020"))
-
-  dta_21 <-
-    htmltab::htmltab(url, 2) %>%
-    dplyr::select(
-      date = Datesconducted,
-      pollster = Pollster,
-      n = Samplesize,
-      con = Con,
-      lab = Lab,
-      lib = `Lib Dem`
-    ) %>%
-    dplyr::mutate(date = paste(date, "2021"))
-
-
-  # Now we'll merge the data together
-
-  dta <- rbind(dta_20, dta_21)
-
-
-  # At the moment, the data contain rows that include only information on the
-  # events that came to pass in UK politics. We don't need these, so we will
-  # remove them from the data.
-
-  dta <-
-    dta %>%
-    dplyr::filter(!(pollster == con))
-
-
-  # We'll also remove the actual election results themselves.
-
-  dta <-
-    dta %>%
-    dplyr::filter(stringr::str_detect(pollster, "election|Election") == F)
-
-
-  # The date column includes non-ASCII chaaracters. Let's sub them out.
-
-  dta <-
-    dta %>%
-    dplyr::mutate(
-      date = iconv(date, "latin1", "ASCII", sub="-"),
-      pollster = iconv(pollster, "latin1", "ASCII", sub="-")
-    )
-
-
-  # Likewise we'll remove the clients from the pollster column and
-  # convert the pollsters to lower case
-
-  dta <-
-    dta %>%
-    dplyr::mutate(
-      pollster =
[…]

### 2021-03-19 R_int/in_text.R

@@ -1,68 +1,0 @@
-#' In-Text Summary Statistics
-#'
-#' Generate in-text summary statistics for posterior distributions from Bayesian models. Most useful when used in Rmarkdown documents.
-#'
-#' @param x The distribution to summarise
-#' @param text A character string that follows and describes the point estimate.
-#' @param suffix A character string that follows each estimate.
-#' @param inside Should the median be inside or outside the brackets? Defaults to T.
-#' @param probs The level at which to compute the lower and upper bounds. Defaults to 0.95.
-#' @param digits How many digits to round the summary statistics to. Defaults to 1.
-#' @return A text string.
-#' @examples
-#' in_text(rnorm(1e3, 0.5, .1))
-#' @export
-
-in_text <- function(x, text = NULL, suffix = NULL, inside = T, probs = .95, digits = 1){
-
-  # Get median of the distribution and round to
-  # desired number of digits
-
-  m <- stats::median(x)
-  m <- round(m, digits = digits)
-  m <- format(m, nsmall = digits)
-
-
-  # Get lower bound and round to desired digits
-
-  l <- stats::quantile(x, probs = (1 - probs)/2)
-  l <- round(l, digits = digits)
-  l <- format(l, nsmall = digits)
-
-
-  # Get upper bound and round to desired digits
-
-  u <- stats::quantile(x, probs = probs + ((1 - probs)/2))
-  u <- round(u, digits = digits)
-  u <- format(u, nsmall = digits)
-
-
-  # Add suffix if necessary
-
-  if(is.null(suffix) == F){
-    m <- paste0(m, suffix)
-    l <- paste0(l, suffix)
-    u <- paste0(u, suffix)
-  }
-
-
-  # Add in text if necessary
-
-  if(is.null(text) == F){
-    m <- paste0(m, text)
-  }
-
-
-  # Return in-text version
-
-  if(inside == T){
-
-    paste0("(", m, ", ", probs*100, "% ", "CI: ", l, " to ", u, ")")
-
-  } else {
-
-    paste0(m, " (", probs*100, "% ", "CI: ", l, " to ", u, ")")
-
-  }
-
-}

### 2021-03-19 R_int/load_timeline.R

@@ -1,25 +1,0 @@
-#' Load Jennings and Wlezien's "Timeline of Elections" Dataset
-#'
-#' This function downloads and loads the Timeline data.
-#'
-#' @examples
-#' \dontrun{
-#' load_timeline()
-#' }
-#' @export
-
-load_timeline <- function(){
-
-  # Download and extract CSES IMD data
-
-  temp <- tempfile()
-  utils::download.file("https://utexas.box.com/shared/static/6fevlf9v9s25ciky4vqdhj05rnk3d5ri.zip", temp)
-  data <- utils::read.table(unz(temp, "Dataset-20180111.tab"), sep = "\t", header = T)
-  unlink(temp)
-
-
-  # Return data to user
-
-  return(data)
-
-}

### 2021-03-19 R_int/mae.R

@@ -1,13 +1,0 @@
-#' Mean Absolute Error
-#'
-#' This function provides a simple way to compute MAE.
-#'
-#' @param y1 A numeric vector.
-#' @param y2 A numeric vector.
-#'
-#' @export
-
-mae <- function(y1, y2){
-  mean(abs(y1 - y2))
-}
-

### 2021-03-19 R_int/make_table.R

@@ -1,61 +1,0 @@
-#' Generate Variable Tables
-#'
-#' Provided a data frame of labelled vectors, this function returns a formatted summary table.
-#'
-#' @param data A data frame of labelled vectors
-#' @export
-
-make_table <- function(data = NULL){
-
-  # Get pipe from Magrittr
-
-  `%>%` <- magrittr::`%>%`
-
-
-  # Get list of variable names
-
-  var_names <- paste0("\\texttt{" , stringr::str_replace(names(data), "_", "\\\\_"), "}")
-
-
-  # Get list of variable labels
-
-  var_labels <- paste0(unlist(labelled::var_label(data)))
-
-
-  # Convert to a data frame
-
-  var_dta <-
-    data.frame(
-      `Name` = var_names,
-      `Description` = var_labels
-    )
-
-
-  # Make data frame names use sans font
-
-  names(var_dta) <- paste0("\\textsf{\\textbf{" , names(var_dta), "}}")
-
-
-  # Convert to latex table
-
-  var_tab <-
-    kableExtra::kable(
-      var_dta,
-      align = "ll",
-      format = "latex",
-      booktabs = TRUE,
-      escape = FALSE,
-      linesep = ""
-    ) %>%
-    kableExtra::kable_styling(
-      position = "center",
-      latex_options = "hold_position"
-    )
-
-
-  # Return table to user
-
-  return(var_tab)
-
-}
-

### 2021-03-19 R_int/rmse.R

@@ -1,13 +1,0 @@
-#' Root-Mean-Square Error
-#'
-#' This function provides a simple way to compute RMSE.
-#'
-#' @param y1 A numeric vector.
-#' @param y2 A numeric vector.
-#'
-#' @export
-
-rmse <- function(y1, y2){
-  sqrt(sum(((y1 - y2)^2)/length(y1)))
-}
-

### 2021-03-19 R_int/save_info.R

@@ -1,20 +1,0 @@
-#' Quicky and Easy Session Info .txt Files
-#'
-#' This function provides a simple way to export session information.
-#'
-#' @param path The file path to where you would like to save your session information.
-#' @examples
-#' \dontrun{
-#' save_info()
-#' }
-#' @export
-
-save_info <- function(path = "session_info.txt"){
-
-  sink(file = path)
-  cat(paste0("Analysis completed: ", Sys.time(), "\n\n"))
-  print(utils::sessionInfo())
-  sink()
-
-}
-

### 2021-03-19 R_int/update_pollbasepro.R

@@ -1,501 +1,0 @@
-#' Update Voting Intention Polls, 2019-Present
-#'
-#' This function updates the pollbasepro data to include the latest polling data and outputs Twitter content.
-#'
-#'
-#' @export
-
-update_pollbasepro <- function(){
-
-  # Get pipe from Magrittr
-
-  `%>%` <- magrittr::`%>%`
-
-
-  # Make list object
-
-  dta <-
-    tibble::tibble(
-      init = "2019-12-12",
-      final = NA,
-      con = NA,
-      lab = NA,
-      lib = NA
-    ) %>%
-    tidyr::pivot_longer(
-      cols = c(con, lab, lib),
-      names_to = "party",
-      values_to = "estimates"
-    ) %>%
-    dplyr::mutate(
-      alpha_init = britpol::get_result(election = init, party = party),
-      alpha_final = NA,
-      estimates = as.list(rep(NA, dplyr::n()))
-    )
-
-
-  # Get wiki data and mutate
-
-  wiki <-
-    britpol::get_new_polls() %>%
-    dplyr::mutate(
-      election = "2019-12-12",
-      id =
-        paste0(
-          "poll-",
-          seq(
-            as.numeric(
-              stringr::str_remove(
-                britpol::pollbase$id[britpol::pollbase$end > "2019-12-12"][1], ".*-"
-              )
-            ),
-            as.numeric(
-              stringr::str_remove(
-                britpol::pollbase$id[britpol::pollbase$end > "2019-12-12"][1], ".*-"
-              )
-            ) + nrow(.) - 1,
-            by = 1
-          )
-        ),
-      days =
-        lubridate::interval(start, end) %>%
-        magrittr::divide_by(lubridate::days(1)) %>%
-        magrittr::add(1)
-    ) %>%
-    tidyr::uncount(days) %>%
-    dplyr::group_by(id) %>%
-    dplyr::mutate(
-      date = lubridate::`%m+%`(start, lubridate::days(dplyr::row_number() - 1)),
-      days = dplyr::n()
-    ) %>%
-    dplyr::ungroup() %>%
-    dplyr::select(-start, -end) %>%
-    dplyr::mutate(
-      index = (lubridate::interval(election, date)/lubridate::days(1)) + 1
-    ) %>%
-    dplyr::select(
-      id,
-      days,
-      election,
-      date,
-      pollster,
-      n,
-      con,
-      lab,
-      lib,
[…]

### 2021-03-19 data-raw/000_compile.R

@@ -10,16 +10,13 @@ library(rmarkdown)
 library(here)
 
 
-# Load internal functions
-
-for(i in dir(here("R_int"))){
-  source(here("R_int", i))
-  rm(i)
-}
-
-
 
 # 2. Compile data and models ----------------------------------------------
+
+# Create mini datasets
+
+source(here("data-raw", "006_mini_data.R"))
+
 
 # Fit sample size imputation model
 
@@ -53,7 +50,7 @@ source(here("data-raw", "005_example.R"))
 
 render(
   input = here("documentation", "paper.Rmd"),
-  output_file = here("download", "paper.pdf")
+  output_file = here("documentation", "paper.pdf")
 )
 
 
@@ -66,7 +63,7 @@ source(here("documentation", "_assets", "cover.R"))
 
 render(
   input = here("documentation", "userguide.Rmd"),
-  output_file = here("download", "userguide.pdf")
+  output_file = here("documentation", "userguide.pdf")
 )
 
 

### 2021-03-19 data-raw/001_samplesizes.R

@@ -16,7 +16,7 @@ library(here)
 # Load timeline of elections data
 
 timeline <-
-  load_timeline() %>%
+  britpol:::load_timeline() %>%
   select(
     polldate,
     elecdate,
@@ -24,14 +24,6 @@ timeline <-
     sample
   ) %>%
   na.omit()
-
-
-# Load internal functions
-
-for(i in dir(here("R_int"))){
-  source(here("R_int", i))
-  rm(i)
-}
 
 
 
@@ -133,15 +125,15 @@ samplesizes <-
     sample_mod,
     newdata =
       tibble(
-        date = seq.Date(as_date("1945-01-01"), as_date(Sys.Date()), "day"),
-        time = interval(as_date("1945-01-01"), date)/years(10),
+        date = seq.Date(as_date("1955-01-01"), as_date("2013-01-01"), "day"),
+        time = interval(as_date("1955-01-01"), date)/years(10),
         country = "United Kingdom"
       ),
     re_formula = NULL
   ) %>%
   data.frame() %>%
   tibble() %>%
-  mutate(date = seq.Date(as_date("1945-01-01"), as_date(Sys.Date()), "day")) %>%
+  mutate(date = seq.Date(as_date("1955-01-01"), as_date("2013-01-01"), "day")) %>%
   select(
     date,
     n_est = Estimate

### 2021-03-19 data-raw/002_pollbase.R

@@ -59,15 +59,7 @@ pollbase <-
 
 # Load sample size data
 
-load(here("R", "sysdata.rda"))
-
-
-# Load internal functions
-
-for(i in dir(here("R_int"))){
-  source(here("R_int", i))
-  rm(i)
-}
+data("samplesizes")
 
 
 
@@ -647,20 +639,6 @@ usethis::use_data(
   pollbase,
   internal = FALSE,
   overwrite = TRUE
-)
-
-
-# And we'll also save the file as a .dta and .sav file for easy use
-
-write_dta(
-  pollbase,
-  path = here("download", paste0("pollbase_", packageVersion("britpol"), ".dta"))
-)
-
-write_sav(
-  pollbase,
-  path = here("download", paste0("pollbase_", packageVersion("britpol"), ".sav")),
-  compress = T
 )
 
 

### 2021-03-19 data-raw/003_pollbasepro.R

@@ -52,13 +52,6 @@ elec_dates <-
   )
 
 
-# Load internal functions
-
-for(i in dir(here("R_int"))){
-  source(here("R_int", i))
-  rm(i)
-}
-
 
 # 2. Transform data -------------------------------------------------------
 
@@ -403,20 +396,6 @@ usethis::use_data(
   pollbasepro,
   internal = FALSE,
   overwrite = TRUE
-)
-
-
-# And we'll also save the file as a .dta and .sav file for easy use
-
-write_dta(
-  pollbasepro,
-  path = here("download", paste0("pollbasepro_", packageVersion("britpol"), ".dta"))
-)
-
-write_sav(
-  pollbasepro,
-  path = here("download", paste0("pollbasepro_", packageVersion("britpol"), ".sav")),
-  compress = T
 )
 
 

### 2021-03-19 data-raw/004_validation.R

@@ -21,7 +21,7 @@ data("pollbasepro")
 # Load Timeline data, filter to include only UK cases, and split by party
 
 timeline <-
-  load_timeline() %>%
+  britpol:::load_timeline() %>%
   select(
     date = polldate,
     elecdate,
@@ -65,14 +65,6 @@ lib <-
   na.omit()
 
 
-# Load internal functions
-
-for(i in dir(here("R_int"))){
-  source(here("R_int", i))
-  rm(i)
-}
-
-
 # 3. Fit correlation models -----------------------------------------------
 
 # We're going to validate the PollBasePro data by calculating the correlation
@@ -99,11 +91,7 @@ cor_con <-
     seed = 666,
     chains = 4,
     cores = 4,
-    file =
-      here(
-        "models",
-        paste0("cor_con_", packageVersion("britpol"))
-      )
+    thin = 4 # Thin to save memory
   )
 
 cor_lab <-
@@ -123,11 +111,7 @@ cor_lab <-
     seed = 666,
     chains = 4,
     cores = 4,
-    file =
-      here(
-        "models",
-        paste0("cor_lab_", packageVersion("britpol"))
-      )
+    thin = 4 # Thin to save memory
   )
 
 cor_lib <-
@@ -147,11 +131,7 @@ cor_lib <-
     seed = 666,
     chains = 4,
     cores = 4,
-    file =
-      here(
-        "models",
-        paste0("cor_lib_", packageVersion("britpol"))
-      )
+    thin = 4 # Thin to save memory
   )
 
 
@@ -179,17 +159,30 @@ cor_all <-
     seed = 666,
     chains = 4,
     cores = 4,
-    file =
-      here(
-        "models",
-        paste0("cor_all_", packageVersion("britpol"))
-      )
+    thin = 4 # Thin to save memory
   )
 
 
-# Let's now combine these models into a list
+# Let's now combine the residual correlations into a list
 
-cor_mods <- list(cor_all, cor_con, cor_lab, cor_lib)
+cor_mods <-
+  list(
+    posterior_samples(cor_all, pars = ""),
+    posterior_samples(cor_all, pars = ""),
+    posterior_samples(cor_all, pars = ""),
+    posterior_samples(cor_con, pars = ""),
+    posterior_samples(cor_lab, pars = ""),
+    posterior_samples(cor_lib, pars = "")
+  )
+
+
+# Then we'll save them as system data
+
+usethis::use_data(
+  cor_mods,
[…]

### 2021-03-19 data-raw/006_mini_data.R

@@ -1,0 +1,442 @@
+
+# Create mini datasets
+
+# 1. Housekeeping ---------------------------------------------------------
+
+# Load packages
+
+library(tidyverse)
+library(lubridate)
+library(htmltab)
+library(haven)
+library(here)
+
+
+
+# 2. Get election dates ---------------------------------------------------
+
+# First, we'll get the data from Wikipedia
+
+election_dates <-
+  rbind(
+    htmltab(
+      doc = "https://w.wiki/36xA",
+      which = 2
+    ) %>%
+      select(date = 2),
+    htmltab(
+      doc = "https://w.wiki/36xA",
+      which = 3
+    ) %>%
+      select(date = 2)
+  )
+
+
+# Next, we'll sort out the dates and remove all cases before universal
+# suffrage was introduced in 1928
+
+election_dates <-
+  election_dates %>%
+  mutate(
+    date =
+      date %>%
+      dmy()
+  ) %>%
+  na.omit() %>%
+  filter(date > "1928-01-01") %>%
+  arrange(date) %>%
+  tibble()
+
+
+# Finally, we'll save the data to use later
+
+usethis::use_data(
+  election_dates,
+  internal = FALSE,
+  overwrite = TRUE
+)
+
+
+
+# 3. Create list of prime ministers ---------------------------------------
+
+# Now, we'll get the list of British prime minister from Wikipedia then do
+# some light editing.
+
+prime_ministers <-
+  htmltab(
+    doc = "https://w.wiki/36wN",
+    which = 2,
+    header = 1:2
+  ) %>%
+  select(
+    prime_minister = 1,
+    pm_party = 6,
+    start = 2,
+    end = 3
+  ) %>%
+  tibble() %>%
+  distinct()
+
+
+# These data are terribly formatted, so we'll start by dealing with the
+# dates so that we can filter out some of the crap.
+
+prime_ministers <-
+  prime_ministers %>%
+  filter(
+    !str_detect(start, "year|years|day|days"),
+    !str_detect(start, "See also"),
+    str_detect(start, "[:digit:]")
+  ) %>%
+  mutate(
+    start = dmy(start),
+    end =
+      ifelse(
+        end == "Incumbent",
+        format(
+          Sys.Date(),
+          format = "%d %b%Y"
+        ),
+        end
+      ) %>%
+      dmy()
+  )
+
+
[…]

### 2021-03-19 documentation/_assets/cover.R

@@ -1,112 +1,0 @@
-
-# Create user guide cover image
-
-
-# 1. Housekeeping ---------------------------------------------------------
-
-# Load packages
-
-library(tidyverse)
-library(magrittr)
-library(ggimage)
-library(here)
-
-
-# Load pollbasepro data
-
-data("pollbasepro")
-
-
-
-# 2. Create plot ----------------------------------------------------------
-
-# We're going to create a simple plot to use as the user guide cover. The
-# neat thing about it is that we can use randomisation to make the cover be
-# different each day. We'll set it up so that the proportion of blue, red,
-# and orange graphics on the cover are roughly proportional to the normalised
-# vote shares of the Conservatives, Labour, and the Liberals according to
-# our most recent estimate.
-
-# First, we'll get today's date and convert to numeric
-
-date_now <- as.numeric(Sys.Date())
-
-
-# Second, we'll use the date to set the random seed
-
-set.seed(date_now)
-
-
-# Next, we'll get the most recent estimates from pollbasepro and normalise
-# them to sum to 1.
-
-props <-
-  pollbasepro %>%
-  filter(date == max(date)) %>%
-  select(matches("_est")) %>%
-  mutate_all(function(x) x/rowSums(.)) %>%
-  t() %>%
-  rep(5) %>%
-  divide_by(5)
-
-
-# Next, we'll get  icon file paths and shuffle them according to the different
-# normalised proportions that we estimated.
-
-paths <- dir(here("documentation", "_assets", "icons"), full.names = T)
-paths <- sample(paths, size = 169, replace = T, prob = props)
-
-
-# Then, we'll generate some basic data
-
-dta <-
-  tibble(
-    x = rep(seq(0, 6, by = .5), each = 13),
-    y = rep(seq(0, 6, by = .5), 13),
-    image = paths
-  )
-
-
-# And, finally, we'll generate today's cover plot
-
-cover <-
-  dta %>%
-  ggplot(
-    aes(
-      x = x,
-      y = y
-    )
-  ) +
-  geom_image(
-    aes(
-      x = x,
-      y = y,
-      image = paths
-    ),
-    size = 0.04,
-    by = "width",
-    asp = 1
-  ) +
-  coord_cartesian(
-    xlim = c(0, 6),
-    ylim = c(0, 6)
-  ) +
-  theme_void() +
-  theme(legend.position = "none")
-
-
-
-# 3. Render plot ----------------------------------------------------------
-
[…]

### 2021-03-21 documentation/paper.Rmd
Fixed issue with Cabin font and minor formatting issue in README
Moved some functions to an internal folder to remove cumbersome dependencies like Stan
Various fixes

@@
   pivot_longer(
-    cols = c(-date, -election, -govt, -week, -month, -quarter, -year, -con_ldr, -lab_ldr, -lib_ldr),
+    cols = -date,
     names_to = c("party", ".value"),
@@
 timeline <-
-  load_timeline() %>%
+  britpol:::load_timeline() %>%
   select(
@@
 
-death_mod <- readRDS(here("models", paste0("death_mod_", packageVersion("britpol"), ".rds")))
-
-# Load correlation models
-
-cor_all <- readRDS(here("models", paste0("cor_all_", packageVersion("britpol"), ".rds")))
-cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("britpol"), ".rds")))
-cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("britpol"), ".rds")))
-cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("britpol"), ".rds")))
+death_mod <- 
+  readRDS(
+    here(
+        "documentation",
+        "_assets",
+        paste0("death_mod_", packageVersion("britpol"), ".rds")
+      )
+  )
 
@@
 tl <-
-  load_timeline() %>%
+  britpol:::load_timeline() %>%
   select(
@@
   #         paste0(
-  #           in_text(pluck(posterior_samples(cor_con, "rescor"), 1)*100, suffix = "%", inside = F),
+  #           britpol:::in_text(pluck(posterior_samples(cor_con, "rescor"), 1)*100, suffix = "%", inside = F),
   #           "\n",
@@
   #         paste0(
-  #           in_text(pluck(posterior_samples(cor_lab, "rescor"), 1)*100, suffix = "%", inside = F),
+  #           britpol:::in_text(pluck(posterior_samples(cor_lab, "rescor"), 1)*100, suffix = "%", inside = F),
   #           "\n",
@@
   #         paste0(
-  #           in_text(pluck(posterior_samples(cor_lib, "rescor"), 1)*100, suffix = "%", inside = F),
+  #           britpol:::in_text(pluck(posterior_samples(cor_lib, "rescor"), 1)*100, suffix = "%", inside = F),
   #           "\n",
@@
 Their mean absolute error (MAE) and root-mean-square error (RMSE) are also low in all cases.
-The Conservatives showed a correlation of `r in_text(pluck(posterior_samples(cor_con, "rescor"), 1)*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(mae(cor_con$data$con_est*100, cor_con$data$vote*100), 2), " percentage points")`, and an RMSE of `r round(rmse(cor_con$data$con_est, cor_con$data$vote), 2)`; Labour, a correlation of `r in_text(pluck(posterior_samples(cor_lab, "rescor"), 1)*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(mae(cor_lab$data$lab_est*100, cor_lab$data$vote*100), 2), " points")`, and an RMSE of `r round(rmse(cor_lab$data$lab_est, cor_lab$data$vote), 2)`; and the Liberals, a correlation of `r in_text(pluck(posterior_samples(cor_lib, "rescor"), 1)*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(mae(cor_lib$data$lib_est*100, cor_lib$data$vote*100), 2), " points")`, and an RMSE of `r round(rmse(cor_lib$data$lib_est, cor_lib$data$vote), 2)`.
+The Conservatives showed a correlation of `r britpol:::in_text(cor_mods$tl_con*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(cor_mods$mae_con, 2), " percentage points")`, and an RMSE of `r round(cor_mods$rmse_con, 2)`; Labour, a correlation of `r britpol:::in_text(cor_mods$tl_lab*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(cor_mods$mae_lab, 2), " points")`, and an RMSE of `r round(cor_mods$rmse_lab, 2)`; and the Liberals, a correlation of `r britpol:::in_text(cor_mods$tl_lib*100, suffix = "%", inside = F)`, an MAE of `r paste0(round(cor_mods$mae_lib, 2), " points")`, and an RMSE of `r round(cor_mods$rmse_lib, 2)`.
 
@@
 Consider the effect of rising Liberal support on the Conservatives and Labour.
-The correlation between the Liberals and the Conservatives is `r in_text(pluck(posterior_samples(cor_all, "rescor__libest__conest"), 1)*100, suffix = "%", inside = F)` and between the Liberals and Labour `r in_text(pluck(posterior_samples(cor_all, "rescor__libest__labest"), 1)*100, suffix = "%", inside = F)`.
+The correlation between the Liberals and the Conservatives is `r britpol:::in_text(cor_mods$lib_con*100, suffix = "%", inside = F)` and between the Liberals and Labour `r britpol:::in_text(cor_mods$lib_lab*100, suffix = "%", inside = F)`.
 Contrary to popular arguments that the Liberals serve to split the centre-left vote [e.g.
 @jenkins2019], our figures suggest that rising Liberal support has tended to hurt the Conservatives more than Labour.
-Interestingly, the correlation between Labour and the Conservatives is also the smallest, at `r in_text(pluck(posterior_samples(cor_all, "rescor__conest__labest"), 1)*100, suffix = "%", inside = F)`.
+Interestingly, the correlation between Labour and the Conservatives is also the smallest, at `r britpol:::in_text(cor_mods$con_lab*100, suffix = "%", inside = F)`.
 This is perhaps unsurprising, given that the two parties represent different sides of the left-right spectrum.
@@
 For example, we can assert with a reasonable degree of certainty that the `r pbp_long$party[which.max(pbp_long$est)]` received the largest degree of support of any party in Britain between `r format(min(pollbasepro$date), "%Y")` and `r format(max(pollbasepro$date), "%Y")` on `r str_remove(format(pbp_long$date[which.max(pbp_long$est)], "%d %B %Y"), "^0")` when our estimates show that `r scales::percent(pbp_long$est[which.max(pbp_long$est)], accuracy = 0.1)` (95% CI: `r paste(scales::percent(pbp_long$est[which.max(pbp_long$est)] - qnorm(0.975)*pbp_long$err[which.max(pbp_long$est)], accuracy = 0.1), "to", scales::percent(pbp_long$est[which.max(pbp_long$est)] + qnorm(0.975)*pbp_long$err[which.max(pbp_long$est)], accuracy = 0.1))`) of the electorate would vote for them at the next election.
-Similarly, we can assert that Labour's peak in the polls came on `r str_remove(format(pollbasepro$date[which.max(pollbasepro$lab_est)], "%d %B %Y"), "^0")` when `r scales::percent(max(pollbasepro$lab_est), accuracy = .1)` (95% CI: `r paste(scales::percent(max(pollbasepro$lab_est) - qnorm(0.975)*pollbasepro$lab_err[which.max(pollbasepro$lab_est)], accuracy = 0.1), "to", scales::percent(max(pollbasepro$lab_est) + qnorm(0.975)*pollbasepro$lab_err[which.max(pollbasepro$lab_est)], accuracy = 0.1))`) of the electorate intended to back them.
+Similarly, we can assert that the Conservative's peak in the polls came on `r str_remove(format(pollbasepro$date[which.max(pollbasepro$con_est)], "%d %B %Y"), "^0")` when `r scales::percent(max(pollbasepro$con_est), accuracy = .1)` (95% CI: `r paste(scales::percent(max(pollbasepro$con_est) - qnorm(0.975)*pollbasepro$con_err[which.max(pollbasepro$con_est)], accuracy = 0.1), "to", scales::percent(max(pollbasepro$con_est) + qnorm(0.975)*pollbasepro$con_err[which.max(pollbasepro$con_est)], accuracy = 0.1))`) of the electorate intended to back them.
 
 These data and their summaries raise an interesting question: if Labour and the Conservatives have tended to be so well-matched in the polls, why have the Conservatives done so much better at election time?
-Despite leading in the polls `r str_remove(lead$Leader[2], " of days")` of the time, Labour has gained the highest share of the vote in only `r pbp_long %>% filter(err == 0) %>% group_by(election) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% summarise(lab = length(winner[winner == "Labour Party"]), .groups = "drop") %>% pluck(1)` of the period's `r pbp_long %>% filter(err == 0) %>% group_by(election) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% nrow()` general elections (`r scales::percent((pbp_long %>% filter(err == 0) %>% group_by(election) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% summarise(lab = length(winner[winner == "Labour Party"]), .groups = "drop") %>% pluck(1))/(pbp_long %>% filter(err == 0) %>% group_by(election) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% nrow()))`).
+Despite leading in the polls `r str_remove(lead$Leader[2], " of days")` of the time, Labour has gained the highest share of the vote in only `r pbp_long %>% filter(err == 0) %>% add_elections() %>% group_by(last_elec) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% summarise(lab = length(winner[winner == "Labour Party"]), .groups = "drop") %>% pluck(1)` of the period's `r pbp_long %>% filter(err == 0) %>% add_elections() %>%  group_by(last_elec) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% nrow()` general elections (`r scales::percent((pbp_long %>% filter(err == 0) %>% add_elections() %>% group_by(last_elec) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% summarise(lab = length(winner[winner == "Labour Party"]), .groups = "drop") %>% pluck(1))/(pbp_long %>% filter(err == 0) %>% add_elections() %>% group_by(last_elec) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% nrow()))`).
 This phenomenon is not entirely unprecedented.
@@
   geom_density_2d(
-    colour = bailey_colours("grey4"),
+    colour = britpol:::bailey_colours("grey4"),
     alpha = .4
@@
     formula = "y ~ x",
-    colour = bailey_colours("black"),
+    colour = britpol:::bailey_colours("black"),
     se = TRUE
@@
     "text",
-    label = 
-      in_text(pluck(posterior_samples(cor_all, "rescor__libest__conest"), 1)*100, suffix = "%", inside = F),
+    label = britpol:::in_text(cor_mods$lib_con*100, suffix = "%", inside = F),
     x = .6, y = .1,
@@
     "text",
-    label = 
-      in_text(pluck(posterior_samples(cor_all, "rescor__libest__labest"), 1)*100, suffix = "%", inside = F),
+    label = britpol:::in_text(cor_mods$lib_lab*100, suffix = "%", inside = F),
     x = .6, y = .1,
@@
     "text",
-    label = 
-    in_text(pluck(posterior_samples(cor_all, "rescor__conest__labest"), 1)*100, suffix = "%", inside = F),
+    label = britpol:::in_text(cor_mods$con_lab*100, suffix = "%", inside = F),
     x = .6, y = .1,
@@
 In March 2020, when the pandemic started to gain pace in Britain, there was a strong positive relationship between change in the number of deaths attributable to COVID-19 and change in support for the governing Conservative Party.
-For every 100 extra COVID-related deaths over the past 4 weeks, Conservative support over the same period increased on average by `r in_text((pluck(posterior_samples(death_mod, "b_deaths"), 1) + pluck(posterior_samples(death_mod, "b_time:deaths"), 1)*2)*100, inside = F, text = " points")`.
+For every 100 extra COVID-related deaths over the past 4 weeks, Conservative support over the same period increased on average by `r britpol:::in_text((pluck(posterior_samples(death_mod, "b_deaths"), 1) + pluck(posterior_samples(death_mod, "b_time:deaths"), 1)*2)*100, inside = F, text = " points")`.
 Six months later, in September 2020, this relationship had weakened markedly.
-Though still positive, it had fallen to only `r in_text((pluck(posterior_samples(death_mod, "b_deaths"), 1) + pluck(posterior_samples(death_mod, "b_time:deaths"), 1)*8)*100, inside = F, text = " points")`.
+Though still positive, it had fallen to only `r britpol:::in_text((pluck(posterior_samples(death_mod, "b_deaths"), 1) + pluck(posterior_samples(death_mod, "b_time:deaths"), 1)*8)*100, inside = F, text = " points")`.
 A year after the pandemic began, the relationship had reversed.
-In March 2021, every 100 additional COVID-related deaths over the past 4 weeks led Conservative support to fall on average by `r in_text((pluck(posterior_samples(death_mod, "b_deaths"), 1) + pluck(posterior_samples(death_mod, "b_time:deaths"), 1)*14)*100, inside = F, text = " points")`.
+In March 2021, every 100 additional COVID-related deaths over the past 4 weeks led Conservative support to fall on average by `r britpol:::in_text((pluck(posterior_samples(death_mod, "b_deaths"), 1) + pluck(posterior_samples(death_mod, "b_time:deaths"), 1)*14)*100, inside = F, text = " points")`.
 
@@
     xintercept = 0,
-    colour = bailey_colours("grey4"),
+    colour = britpol:::bailey_colours("grey4"),
     linetype = "dotted"
@@
     colour = NA,
-    fill = bailey_colours("red"),
+    fill = britpol:::bailey_colours("red"),
     alpha = .2) +
-  geom_line(colour = bailey_colours("red")) +
+  geom_line(colour = britpol:::bailey_colours("red")) +
   scale_y_continuous(
@@
 
-save_info(path = here("sessions", "006_paper.txt"))
+britpol:::save_info(path = here("sessions", "007_paper.txt"))
 

### 2021-03-21 documentation/readme.Rmd
Various fixes

@@
 
-`{britpol}` is an `R` package that makes analysing British political data quick and simple.
+The `{britpol}` package makes analysing British political data quick and simple.
 It contains two pre-formatted datasets, plus a host of useful functions.
 The first dataset, `pollbase`, is a long-format version of Mark Pack's dataset of historic British public opinion polls combined with more recent data from Wikipedia.
-The second dataset, `pollbasepro`, provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties from `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` to `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.
+The second, `pollbasepro`, provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties from `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` to `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.
 
@@
 
-As of `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`, `pollbasepro` suggests that the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party in Britain.
+The `pollbasepro` data suggest that the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party in Britain.
 They hold a lead over the `r txt_dta$party[2]` of around `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`.

### 2021-03-21 documentation/userguide.Rmd
Various fixes

@@
 data("pollbasepro")
+data("samplesizes")
 
-# Load imputed sample sizes
+# Load correlations
 
@@
   na.omit()
-
-# Load correlation models
-
-cor_con <- readRDS(here("models", paste0("cor_con_", packageVersion("britpol"), ".rds")))
-cor_lab <- readRDS(here("models", paste0("cor_lab_", packageVersion("britpol"), ".rds")))
-cor_lib <- readRDS(here("models", paste0("cor_lib_", packageVersion("britpol"), ".rds")))
 
@@
 
-make_table(pollbase)
+britpol:::make_table(pollbase)
 
@@
 
-make_table(pollbasepro)
+britpol:::make_table(pollbasepro)
 
@@
 
-save_info(path = here("sessions", "007_codebook.txt"))
+britpol:::save_info(path = here("sessions", "008_codebook.txt"))
 

### 2021-03-21 R/utils.R

@@ -1023,6 +1023,25 @@ load_timeline <- function(){
 
 }
 
+
+#' Load historic election results from the House of Commons library
+#'
+#' This function downloads and loads historic elections data.
+
+load_results <- function(){
+
+  # Download csv
+
+  data <- utils::read.csv("https://researchbriefings.files.parliament.uk/documents/CBP-8647/1918_2019election_results.csv")
+
+
+  # Return data to user
+
+  return(data)
+
+}
+
+
 #' Mean Absolute Error
 #'
 #' This function provides a simple way to compute MAE.
@@ -1191,6 +1210,7 @@ update_pollbasepro <- function(){
       id,
       days,
       date,
+      election,
       pollster,
       n,
       con,
@@ -1226,11 +1246,6 @@ update_pollbasepro <- function(){
 
   dta <-
     do.call("rbind.data.frame", dta$estimates) %>%
-    dplyr::mutate(
-      election =
-        date %>%
-        get_last_election()
-    ) %>%
     dplyr::distinct() %>%
     tidyr::pivot_wider(
       names_from = party,
@@ -1238,7 +1253,6 @@ update_pollbasepro <- function(){
     ) %>%
     dplyr::select(
       date,
-      election,
       con_est = est_con,
       con_err = sd_con,
       lab_est = est_lab,
@@ -1254,8 +1268,6 @@ update_pollbasepro <- function(){
   labelled::var_label(dta) <-
     list(
       date = "Date",
-      election = "Date of last general election",
-      govt = "Largest party in government after the last  general election",
       con_est = "Posterior mean: Conservative voting intention",
       con_err = "Posterior error: Conservative voting intention",
       lab_est = "Posterior mean: Labour voting intention",
@@ -1283,23 +1295,9 @@ update_pollbasepro <- function(){
   )
 
 
-  # And we'll also save the file as a .dta and .sav file for easy use
-
-  haven::write_dta(
-    pollbasepro,
-    path = here::here("download", paste0("pollbasepro_", utils::packageVersion("britpol"), ".dta"))
-  )
-
-  haven::write_sav(
-    pollbasepro,
-    path = here::here("download", paste0("pollbasepro_", utils::packageVersion("britpol"), ".sav")),
-    compress = T
-  )
-
-
   # Finally, we'll update the replication information
 
-  save_info(here::here("sessions", "003_pollbasepro.txt"))
+  save_info(here::here("sessions", "004_pollbasepro.txt"))
 
 
 }

### 2021-03-21 data-raw/000_compile.R

@@ -81,7 +81,7 @@ render(
 
 # We'll save session information to the "sessions" folder
 
-save_info(path = here("sessions", "000_compile.txt"))
+britpol:::save_info(path = here("sessions", "000_compile.txt"))
 
 
 # Now, we'll run our unit tests to check that nothing weird is happening or

### 2021-03-21 data-raw/003_pollbase.R

@@ -438,6 +438,20 @@ pollbase <-
     lib
   )
 
+# Then we'll add variable labels
+
+var_label(pollbase) <-
+  list(
+    id = "Unique poll ID number",
+    start = "Date of first day of fieldwork",
+    end = "Date of last day of fieldwork",
+    pollster = "Polling company",
+    n = "Sample size",
+    con = "Conservative Party vote share",
+    lab = "Labour Party vote share",
+    lib = "Liberal (various forms) vote share"
+  )
+
 
 
 # 3. Save data ------------------------------------------------------------

### 2021-03-21 data-raw/005_validation.R

@@ -173,7 +173,13 @@ cor_mods <-
     "con_lab" = posterior_samples(cor_all, pars = "rescor__conest__labest")[[1]],
     "tl_con" = posterior_samples(cor_con, pars = "rescor__vote__conest")[[1]],
     "tl_lab" = posterior_samples(cor_lab, pars = "rescor__vote__labest")[[1]],
-    "tl_lib" = posterior_samples(cor_lib, pars = "rescor__vote__libest")[[1]]
+    "tl_lib" = posterior_samples(cor_lib, pars = "rescor__vote__libest")[[1]],
+    "mae_con" = britpol:::mae(cor_con$data$con_est*100, cor_con$data$vote*100),
+    "mae_lab" = britpol:::mae(cor_lab$data$lab_est*100, cor_lab$data$vote*100),
+    "mae_lib" = britpol:::mae(cor_lib$data$lib_est*100, cor_lib$data$vote*100),
+    "rmse_con" = britpol:::rmse(cor_con$data$con_est, cor_con$data$vote),
+    "rmse_lab" = britpol:::rmse(cor_lab$data$lab_est, cor_lab$data$vote),
+    "rmse_lib" = britpol:::rmse(cor_lib$data$lib_est, cor_lib$data$vote)
   )
 
 

### 2021-03-21 documentation/readme.Rmd
Updated README

@@
   pivot_longer(
-    cols = c(-date, -election, -govt, -matches("_ldr"), -week, -month, -quarter, -year),
+    cols = -date,
     names_to = c("party", ".value"),

### 2021-03-21 documentation/paper.Rmd
Thank Hannah Willis

@@
 We owe particular thanks to Chris Hanretty, who inspired this project and provided much useful feedback.
-We would also like to thank X, Y, and Z for offering their time to review the manuscript.
+We would also like to thank Hannah Willis, Y, and Z for offering their time to review our manuscript.
 Finally, we would like to extend a special thanks to all of the volunteers who work to maintain such a comprehensive list of British opinion polling data on Wikipedia.}
@@
 \delta_{j} &\sim \mathrm{Normal}(0, 0.05) \text{ for } j \text{ in } 1, ..., J \srlab{Prior on house effects, $\delta$} \\
-\omega_{t} &\sim \mathrm{Normal}(0, 0.1) \text{ for } t \text{ in } 1, ..., T-1 \srlab{Prior on random shocks, $\omega$} \\
+\omega_{t} &\sim \mathrm{Normal}(0, 0.025) \text{ for } t \text{ in } 1, ..., T-1 \srlab{Prior on random shocks, $\omega$} \\
 \tau &\sim \mathrm{Normal}(0, 0.05)^{+} \srlab{Positive prior on scale of innovations, $\tau$} \\

### 2021-03-21 documentation/readme.Rmd
Minor edit to READMe
Update README

@@
 
-The `pollbasepro` data suggest that the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party in Britain.
+`pollbasepro` suggests that the `r txt_dta$party[1]` `r ifelse(txt_dta$party[1] %in% c("Conservative Party", "Labour Party"), "is", "are")` the largest party in Britain.
 They hold a lead over the `r txt_dta$party[2]` of around `r paste0(scales::percent(txt_dta$est[1] - txt_dta$est[2]), " (", scales::percent((txt_dta$est[1] - txt_dta$est[2]) - qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), " to ", scales::percent((txt_dta$est[1] - txt_dta$est[2]) + qnorm(.975)*sqrt(txt_dta$err[1]^2 + txt_dta$err[2]^2)), ")")`.
-This puts the `r txt_dta$party[2]` in second place and the `r txt_dta$party[3]` in third place.
+This puts the `r txt_dta$party[2]` in second and the `r txt_dta$party[3]` in third.
 

### 2021-03-25 documentation/paper.Rmd
Fixed errant citation
Thank Chris Wlezien

@@
 We owe particular thanks to Chris Hanretty, who inspired this project and provided much useful feedback.
-We would also like to thank Hannah Willis, Y, and Z for offering their time to review our manuscript.
+We would also like to thank Hannah Willis, Chris Wlezien, and Z for offering their time to review our manuscript.
 Finally, we would like to extend a special thanks to all of the volunteers who work to maintain such a comprehensive list of British opinion polling data on Wikipedia.}
@@
 At the 2015 UK general election, most polls suggested that Labour had a good chance of becoming the largest party.
-But, on the night, the Conservatives won a small majority instead [@sturgis2018; @prosser2018c, @mellon2017a].
+But, on the night, the Conservatives won a small majority instead [@sturgis2018; @prosser2018c; @mellon2017a].
 These biases were even more serious at the 2019 Australian Federal Election.

### 2021-03-26 R/clean_party_names.R
Combined results and constituencies files

@@ -22,7 +22,7 @@ clean_party_names <- function(x, party_names = list("^con|^tor" = "Conservatives
     stringr::str_remove_all("[[:punct:]]") %>%
     stringr::str_replace_all("[[:space:]]", "") %>%
     iconv(from = "UTF-8", to = "ASCII//TRANSLIT") %>%
-    stringr::str_remove("the")
+    stringr::str_remove("^the")
 
 
   # Get regular expressions
@@ -58,14 +58,14 @@ clean_party_names <- function(x, party_names = list("^con|^tor" = "Conservatives
 
     x <-
       ifelse(
-        stringr::str_detect(x, "dk|dontknow|refused|skip|prefernot|miss|na"),
+        stringr::str_detect(x, "^dk|^dontknow|^refused|^skip|^prefernot|^miss|^na"),
         NA,
         x
       )
 
   } else {
 
-    x[stringr::str_detect(x, "dk|dontknow|refused|skip|prefernot|miss|na")] <- "Other"
+    x[stringr::str_detect(x, "^dk|^dontknow|^refused|^skip|^prefernot|^miss|^na")] <- "Other"
 
   }
 

### 2021-03-26 R/clean_pcon_names.R

@@ -33,7 +33,7 @@ clean_pcon_names <- function(x){
   # Simplify reference names and remove remove punctuation, etc.
 
   ref <-
-    britpol::constituencies$name %>%
+    britpol::constituency_results$constituency %>%
     tolower() %>%
     stringr::str_replace("&", "and") %>%
     stringr::str_remove_all("[[:punct:]]") %>%
@@ -53,7 +53,7 @@ clean_pcon_names <- function(x){
   # (let me know if you know how to speed this up)
 
   for(i in 1:length(ref)){
-    x[x == ref[i]] <- britpol::constituencies$name[i]
+    x[x == ref[i]] <- britpol::constituency_results$constituency[i]
   }
 
 

### 2021-03-26 R/data.R

@@ -103,29 +103,20 @@
 #' @format A data frame:
 #' \describe{
 #'   \item{date}{Election date}
-#'   \item{constituency}{Name of constituency}
 #'   \item{seats}{Number of seats in constituency}
+#'   \item{constituency}{Name of constituency}
+#'   \item{pano}{Press Association code}
+#'   \item{nomis}{NOMIS code}
+#'   \item{pca}{PCA code}
+#'   \item{ons}{ONS GSS code}
+#'   \item{county}{County}
 #'   \item{region}{Region or country}
 #'   \item{electorate}{Size of constituency electorate}
-#'   \item{con_votes}{Number of Conservative votes}
-#'   \item{lab_votes}{Number of Labour votes}
-#'   \item{lib_votes}{Number of Liberal votes}
-#'   \item{nat_votes}{Number of Nationalist votes in Scotland and Wales}
-#'   \item{oth_votes}{Number of votes for any other party}
+#'   \item{con}{Number of Conservative votes}
+#'   \item{lab}{Number of Labour votes}
+#'   \item{lib}{Number of Liberal votes}
+#'   \item{nat}{Number of Nationalist votes in Scotland and Wales}
+#'   \item{oth}{Number of votes for any other party}
 #' }
-"election_results"
-
-
-#' Historic Parliamentary Constituencies
-#'
-#' A dataset containing the names and GSS codes of all historic constituencies since 1918.
-#'
-#' @format A data frame:
-#' \describe{
-#'   \item{name}{Name of parliamentary constituency}
-#'   \item{gss_code}{Government Statistical Service code}
-#'   \item{start}{Date constituency was introduced}
-#'   \item{end}{Date constituency was retired}
-#' }
-"constituencies"
+"constituency_results"
 

### 2021-03-26 R/utils.R

@@ -1029,24 +1029,6 @@ load_timeline <- function(){
 }
 
 
-#' Load historic election results from the House of Commons library
-#'
-#' This function downloads and loads historic elections data.
-
-load_results <- function(){
-
-  # Download csv
-
-  data <- utils::read.csv("https://researchbriefings.files.parliament.uk/documents/CBP-8647/1918_2019election_results.csv")
-
-
-  # Return data to user
-
-  return(data)
-
-}
-
-
 #' Mean Absolute Error
 #'
 #' This function provides a simple way to compute MAE.

### 2021-03-26 data-raw/001_mini_data.R

@@ -8,8 +8,10 @@
 library(tidyverse)
 library(lubridate)
 library(labelled)
+library(janitor)
 library(hansard)
 library(htmltab)
+library(readxl)
 library(haven)
 library(here)
 
@@ -356,172 +358,218 @@ usethis::use_data(
 
 # 5. Get historic constituency results ------------------------------------
 
-# First, let's download the historic election results
+# Get index of first sheet post-1928
 
-election_results <- britpol:::load_results()
-
-
-# Next, we'll filter out any pre-1928 cases
-
-election_results <-
-  election_results %>%
-  filter(election >= 1928)
+start <-
+  here("inst", "extdata", "1918-2019election_results_by_pcon.xlsx") %>%
+  excel_sheets() %>%
+  str_detect("1929") %>%
+  which()
 
 
-# And then we'll select the variables we need and convert to a tibble
+# Get number of sheets
 
-election_results <-
-  election_results %>%
-  select(
-    constituency,
-    seats,
-    region = country.region,
-    election,
-    electorate,
-    con_votes,
-    lab_votes,
-    lib_votes,
-    nat_votes = natSW_votes,
-    oth_votes
+sheets <-
+  here("inst", "extdata", "1918-2019election_results_by_pcon.xlsx") %>%
+  excel_sheets() %>%
+  length()
+
+
+# Load raw data from Mark Pack's website
+
+constituency_results <-
+  tibble(
+    date = election_dates$date,
+    n = start:sheets
   ) %>%
-  tibble()
-
-
-# Now, we'll convert the constituency names to title case
-
-election_results <-
-  election_results %>%
   mutate(
-    constituency =
-      constituency %>%
-      snakecase::to_title_case()
+    data =
+      map2(
+        .x = n,
+        .y = date,
+        .f = function(x, y){
+
+          # Read data
+
+          dta <-
+            read_xlsx(
+              here("inst", "extdata", "1918-2019election_results_by_pcon.xlsx"),
+              sheet = x,
+              col_types = "text",
+              .name_repair = "minimal",
+              skip = 2
+            )
+
+
+          # Rename headers and drop first row
+
+          names(dta) <-
+            paste0(dta[1, ], names(dta)) %>%
+            str_remove("^Votes") %>%
+            tolower() %>%
+            str_remove("^na") %>%
+            str_remove("^ons ")
+          dta <- dta[-1, ]
+
+
+          # Clean data set
+
+          dta <-
+            dta %>%
+            drop_na(id) %>%
[…]

### 2021-04-12 documentation/paper.Rmd
Combined results and constituencies files
Full recompilation

--- 2021-03-21 documentation/paper.Rmd
@@
   | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(britpol::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback.
-We owe particular thanks to Chris Hanretty, who inspired this project and provided much useful feedback.
-We would also like to thank Hannah Willis, Y, and Z for offering their time to review our manuscript.
+We owe particular thanks Chris Hanretty, who inspired this project and provided much useful feedback.
+We would also like to thank Hannah Willis, Chris Wlezien, and Patrick English for offering their time to review our manuscript.
 Finally, we would like to extend a special thanks to all of the volunteers who work to maintain such a comprehensive list of British opinion polling data on Wikipedia.}
@@
 It includes voting intention estimates for each of Britain's three largest parties on each day between the 1955 general election and the present.
-Given that the dataset covers `r format(nrow(britpol::pollbasepro), big.mark = ",")` days in total, it is more comprehensive than any existing time series of public opinion in Britain.
-As a result, we expect PollBasePro to be an important resource for students of British politics in the years to come.
+As the dataset covers `r format(nrow(britpol::pollbasepro), big.mark = ",")` days in total, it is perhaps more comprehensive than any other existing time series of British political opinion.
+We then use our estimates to test a question of pressing importance: how daily deaths attributable to COVID-19 have influenced support for the governing Conservative Party.
   |
@@
 Like much that politicians say, this is not true.
-Though elections decide who governs, public opinion polls are important too: they let us track how popular parties are in the time between elections.
+Though elections decide who governs, public opinion polls are important too: they tell us how popular parties are in the time between elections.
 Polling is especially important in Britain.
-Unlike in many countries, British governments have some control over scheduling elections.
-As a result, the governing party's standing is often one of the only factors that decides when it will hold an election [@smith2003].
+Unlike in some countries, British governments can control the election schedule.
+As a result, the governing party's standing is often one of the only factors that decides when an election will occur [@smith2003].
 
@@
 
-In this paper, we introduce a new dataset---*PollBasePro*---that overcomes these issues.
-It includes `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of aggregate voting intention for each of Britain's three largest parties on each day between `r format(min(pollbasepro$date), "%d %B %Y")` and `r format(max(pollbasepro$date), "%d %B %Y")`.
-Covering `r format(nrow(pollbasepro), big.mark = ",")` days in total, PollBasePro permits a degree of specificity and flexibility beyond that of any existing time series data.
+We introduce a new dataset---*PollBasePro*---that overcomes these issues.
+It includes daily estimates of aggregate voting intention for each of Britain's three largest parties on each day between `r format(min(pollbasepro$date), "%d %B %Y")` and `r format(max(pollbasepro$date), "%d %B %Y")`.
+Covering `r format(nrow(pollbasepro), big.mark = ",")` days in total, PollBasePro permits a degree of specificity and flexibility beyond that of any existing time series.
 In the sections that follow, we elaborate on the dataset.
 First, we describe the methods and the data that we use to derive our estimates.
-Next, we consider what PollBasePro reveals about British politics since 1955 and show how to use it to test hypotheses.
-We then provide some initial conclusions and remark on how we might develop PollBasePro in the future.
+Next, we consider what PollBasePro reveals about British politics since 1955 and show how to use it to test answer a question of pressing concern: how do deaths related to COVID-19 affect public support for the governing Conservative Party?
+We show that COVID-related deaths have led to a "rally 'round the flag" effect that has boosted Conservative support, though that this relationship has weakened, then reversed, as the pandemic has progressed.
+Finally, we provide some initial conclusions and then remark on how we might develop PollBasePro over the coming years.
 
@@
 
-Polling data have long informed political science research.
-For example, @goodhart1970 used Gallup and NOP polls to show that changes in the economy affect support for the incumbent party, thereby launching economic voting research.
-Though plentiful, these data come with some problems.
-As we mention above, three are most important.
+Polls have long informed political science.
+@goodhart1970, for instance, used Gallup and NOP polls to show that economic change affects incumbent party support, launching the economic vote.
+Yet though plentiful, these data have three important problems.
 
@@
 Rather, they represent draws from a distribution of *possible* estimates of public opinion.
-This noise is a type of measurement error, and failing to account for it can have important consequences.
+Once introduced into formal statistical models, this sampling error becomes a form of measurement error.
+And failing to account for it can have serious consequences.
 Where we use polls as an outcome, it reduces our statistical power.
@@
 
-Second, polling data occur at irregular intervals.
-What's more, they can cover any period of time from a single day to several weeks.
+Second, polling data occur at irregular intervals, covering any period of time from a single day to several weeks.
 Political scientists often assume that these figures measure public opinion on the poll's last day in the field.
-Of course, this is almost never true.
+Of course, that is almost never true.
 It can also be a problem when major events occur partway through the data collection process.
@@
 
-Third, polls do not only measure changes in aggregate preferences.
-They also include systematic biases due to the design choices of the companies that run them.
+Third, polls do not only measure changes in aggregate political preferences.
+They also measure systematic biases that arise due to the design choices of the companies that run them.
 In the past, these biases have been so large that they have cast doubt on the efficacy of the polling industry.
 At the 2015 UK general election, most polls suggested that Labour had a good chance of becoming the largest party.
-But, on the night, the Conservatives won a small majority instead [@sturgis2018; @prosser2018c, @mellon2017a].
+But, on the night, the Conservatives won a small majority instead [@sturgis2018; @prosser2018b; @mellon2017].
 These biases were even more serious at the 2019 Australian Federal Election.
 As in the British case, Labor had a healthy lead in the polls.
-Yet, again, the Coalition beat them by around 8 percentage points [@mansillo2020].
+Yet, again, the conservative Coalition beat them by around 8 percentage points [@mansillo2020].
 
@@
 Jackman and Mansillo [-@mansillo2020; -@jackman2016] have used the model to track voting intention in Australia and @louwerse2016 have used it to estimate aggregate voting intention in Ireland.
-The full model specification is as follows^[Note that we provide a more in-depth explanation of how the model works and the steps that we have taken to produce our estimates in the user guide that accompanies the data.]:
+The full model specification is as follows, though note that we also provide a more complete explanation of how the model works and the steps that we have taken to produce our estimates in the accompanying appendix:
 
@@
 
-The PollBase data come from a range of sources.
-This includes books published after each general election, polling almanacs, data shared amongst academics and pollsters, contemporary media reports, and figures from polling company websites.
-The data since the 1983 general election are complete, baring any individual errors.
-Likewise, data are complete for every general election campaign before 1979.
-The coverage between elections is more comprehensive for some pollsters than others^[We encourage any readers who might know of polls missing from the PollBase dataset to contact its author via his website (https://www.markpack.org.uk)].
-Gallup and NOP data, in particular, are well-covered as the two companies have collated and published their results.
-The PollBase data start on `r format(min(pollbase$start), "%d %B %Y")`.
-Yet, consistent polling began only after the 1955 general election.
-Thus, we take it as our starting point.
-
 ```{r val-plot, fig.cap = "In all cases, estimates from PollBasePro appear well-validated when compared to raw polling data from Jennings and Wlezien's 'Timeline of Elections' dataset (2016).", fig.width = 6, fig.height = 2.5, fig.align = "centre", echo = F}
@@
     colour = pty_cols[1],
-    alpha = .4
+    alpha = .7
   ) +
@@
 
+The PollBase data come from a range of sources.
+This includes books published after each general election, polling almanacs, data shared amongst academics and pollsters, contemporary media reports, and figures from polling company websites.
+The data since the 1983 general election are complete, baring any individual errors.
+Likewise, data are complete for every general election campaign before 1979.
+The coverage between elections is more comprehensive for some pollsters than others^[We encourage any readers who might know of polls missing from the PollBase dataset to contact its author via his website (https://www.markpack.org.uk)].
+Gallup and NOP data, in particular, are well-covered as the two companies have collated and published their results.
+The PollBase data start on `r format(min(pollbase$start), "%d %B %Y")`.
+Yet, consistent polling began only after the 1955 general election.
+Thus, we take it as our starting point.
+
 We use the Wikipedia data to cover the period from 2010 onwards.
@@
 This is important as our model assumes that we know the sampling error present in each estimate.
-For the PollBase data, we impute likely sample sizes to allow us to estimate these errors^[Again, see the user guide that accompanies the data for more information on this process.].
+For the PollBase data, we impute likely sample sizes to allow us to estimate these errors^[Again, see the appendix for more information on this process.].
 But as the Wikipedia data include sample sizes, imputation is not necessary.
@@
 Given that our data are so comprehensive, it is likely that most polls appear in both datasets.
-Still, the Timeline data provide a good test as Jennings and Wlezien compiled them independently.
+Even so, the Timeline data provide a good test as Jennings and Wlezien compiled them independently.
 As figure \@ref(fig:val-plot) shows, our estimates are well validated.
@@
 
-Figure \@ref(fig:time-plot) shows that our estimates track British political history very well.
-Between 1955 and 1980, we observe the heyday of the two-party system.
-Here, around `r scales::percent(median(pollbasepro$lab_est[pollbasepro$date %in% seq.Date(as_date("1955-01-01"), as_date("1980-01-01"), "days")]), accuracy = .1)` of the electorate supported Labour and another `r scales::percent(median(pollbasepro$con_est[pollbasepro$date %in% seq.Date(as_date("1955-01-01"), as_date("1980-01-01"), "days")]), accuracy = .1)` the Conservatives.
+Figure \@ref(fig:time-plot) shows that our estimates track British political history well.
+From 1955 to 1980, we see the heyday of the two-party system.
+Here, around `r scales::percent(median(pollbasepro$lab_est[pollbasepro$date %in% seq.Date(as_date("1955-01-01"), as_date("1980-01-01"), "days")]), accuracy = 1)` of the electorate supported Labour and another `r scales::percent(median(pollbasepro$con_est[pollbasepro$date %in% seq.Date(as_date("1955-01-01"), as_date("1980-01-01"), "days")]), accuracy = 1)` the Conservatives.
 In the 1980s, we see the rise and fall of the SDP-Liberal alliance.
 Labour’s slow rise to power in 1997 soon follows, as does their loss of support over the next decade and a half.
-More recently, the data show a brief “blip” in Liberal support to coincide with “Cleggmania” in 2010, Labour’s surprise surge in 2017, and the Conservative's landslide support in 2019.
+More recently, the data show a “blip” in Liberal support that coincides with “Cleggmania” in 2010, Labour’s surge in 2017, and the Conservative landslide in 2019.
 
@@
 
-\newpage
+```{r vitals-table, echo = F}
+
+# Compute vital statistics
+
+vitals <- 
+  pbp_long %>% 
+  mutate(party = str_remove(party, " .*|s .*")) %>% 
+  group_by(party) %>% 
+  summarise(
+    Median = paste0(format(round(median(est)*100, 1), nsmall = 1), "\\%"),
+    Mean = paste0(format(round(mean(est)*100, 1), nsmall = 1), "\\%"),
+    Error = paste0(format(round(sd(est)*100, 1), nsmall = 1), "\\%"),
+    Lowest = paste0(format(round(min(est)*100, 1), nsmall = 1), "\\%"),
+    Highest = paste0(format(round(max(est)*100, 1), nsmall = 1), "\\%"),
+    .groups = "drop"
+  ) %>% 
+  rename(Party = party)
+
+# Merge vital and lead statistics
+
+vitals <- 
+  left_join(
+    vitals,
+    lead,
+    by = "Party"
+  )
+
+# Add latex code to header names
+
+names(vitals) <- paste0("\\textsf{\\textbf{" ,names(vitals), "}}")
+
+# Output table
+
+kable(
+  vitals,
+  align = "lrrrrrr",
+  format = "latex",
+  label = "vitals-tab",
+  booktabs = TRUE,
+  escape = FALSE,
+  caption = paste0("Overall summary of daily voting intention estimates, ", format(min(pollbasepro$date), "%Y"), " to ", format(max(pollbasepro$date), "%Y"))
+  ) %>% 
+  kable_styling(position = "center")
+
+```
+
+We can also use our estimates to make specific claims about British politics.
+For example, we can assert with a reasonable degree of certainty that the `r pbp_long$party[which.max(pbp_long$est)]` received the largest degree of support of any party in Britain between `r format(min(pollbasepro$date), "%Y")` and `r format(max(pollbasepro$date), "%Y")` on `r str_remove(format(pbp_long$date[which.max(pbp_long$est)], "%d %B %Y"), "^0")` when our estimates show that `r scales::percent(pbp_long$est[which.max(pbp_long$est)], accuracy = 0.1)` (95% CI: `r paste(scales::percent(pbp_long$est[which.max(pbp_long$est)] - qnorm(0.975)*pbp_long$err[which.max(pbp_long$est)], accuracy = 0.1), "to", scales::percent(pbp_long$est[which.max(pbp_long$est)] + qnorm(0.975)*pbp_long$err[which.max(pbp_long$est)], accuracy = 0.1))`) of the electorate would vote for them at the next election.
+Similarly, we can assert that the Conservative's peak in the polls came on `r str_remove(format(pollbasepro$date[which.max(pollbasepro$con_est)], "%d %B %Y"), "^0")` when `r scales::percent(max(pollbasepro$con_est), accuracy = .1)` (95% CI: `r paste(scales::percent(max(pollbasepro$con_est) - qnorm(0.975)*pollbasepro$con_err[which.max(pollbasepro$con_est)], accuracy = 0.1), "to", scales::percent(max(pollbasepro$con_est) + qnorm(0.975)*pollbasepro$con_err[which.max(pollbasepro$con_est)], accuracy = 0.1))`) of the electorate intended to back them.
+
+These data and their summaries raise an interesting question: if Labour and the Conservatives have tended to be so well-matched in the polls, why have the Conservatives done so much better at election time?
+Despite leading in the polls `r str_remove(lead$Leader[2], " of days")` of the time, Labour has gained the highest share of the vote in only `r pbp_long %>% filter(err == 0) %>% add_elections() %>% group_by(last_elec) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% summarise(lab = length(winner[winner == "Labour Party"]), .groups = "drop") %>% pluck(1)` of the period's `r pbp_long %>% filter(err == 0) %>% add_elections() %>%  group_by(last_elec) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% nrow()` general elections (`r scales::percent((pbp_long %>% filter(err == 0) %>% add_elections() %>% group_by(last_elec) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% summarise(lab = length(winner[winner == "Labour Party"]), .groups = "drop") %>% pluck(1))/(pbp_long %>% filter(err == 0) %>% add_elections() %>% group_by(last_elec) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% nrow()))`).
+This phenomenon is not entirely unprecedented.
+@jackman1994 shows that the Australian Labor Party has suffered at elections due to pervasive electoral bias.
+Though this might also be the case in Britain, our figures reflect *vote* shares, not *seat* shares.
+As such, electoral bias should be a concern only insofar as it affects the parties' overall popularity.
+Other factors likely explain Labour's poor performance: Britain's press leans right and tends to support the Conservatives; successive Conservative governments could have scheduled elections to maximise their chances; partisan non-response could have led Conservative voters to drop out of polls in the period between elections; or, most simply, the Conservatives might just be better at campaigning.
+
 \begin{landscape}
@@
 
-```{r vitals-table, echo = F}
-
-# Compute vital statistics
-
-vitals <- 
-  pbp_long %>% 
-  mutate(party = str_remove(party, " .*|s .*")) %>% 
-  group_by(party) %>% 
-  summarise(
-    Median = paste0(format(round(median(est)*100, 1), nsmall = 1), "\\%"),
-    Mean = paste0(format(round(mean(est)*100, 1), nsmall = 1), "\\%"),
-    Error = paste0(format(round(sd(est)*100, 1), nsmall = 1), "\\%"),
-    Lowest = paste0(format(round(min(est)*100, 1), nsmall = 1), "\\%"),
-    Highest = paste0(format(round(max(est)*100, 1), nsmall = 1), "\\%"),
-    .groups = "drop"
-  ) %>% 
-  rename(Party = party)
-
-# Merge vital and lead statistics
-
-vitals <- 
-  left_join(
-    vitals,
-    lead,
-    by = "Party"
-  )
-
-# Add latex code to header names
-
-names(vitals) <- paste0("\\textsf{\\textbf{" ,names(vitals), "}}")
-
-# Output table
-
-kable(
-  vitals,
-  align = "lrrrrrr",
-  format = "latex",
-  label = "vitals-tab",
-  booktabs = TRUE,
-  escape = FALSE,
-  caption = paste0("Overall summary of voting intention estimates, ", format(min(pollbasepro$date), "%Y"), " to ", format(max(pollbasepro$date), "%Y"))
-  ) %>% 
-  kable_styling(position = "center")
-
-```
-
-We can also use our estimates to make specific claims about British politics.
-For example, we can assert with a reasonable degree of certainty that the `r pbp_long$party[which.max(pbp_long$est)]` received the largest degree of support of any party in Britain between `r format(min(pollbasepro$date), "%Y")` and `r format(max(pollbasepro$date), "%Y")` on `r str_remove(format(pbp_long$date[which.max(pbp_long$est)], "%d %B %Y"), "^0")` when our estimates show that `r scales::percent(pbp_long$est[which.max(pbp_long$est)], accuracy = 0.1)` (95% CI: `r paste(scales::percent(pbp_long$est[which.max(pbp_long$est)] - qnorm(0.975)*pbp_long$err[which.max(pbp_long$est)], accuracy = 0.1), "to", scales::percent(pbp_long$est[which.max(pbp_long$est)] + qnorm(0.975)*pbp_long$err[which.max(pbp_long$est)], accuracy = 0.1))`) of the electorate would vote for them at the next election.
-Similarly, we can assert that the Conservative's peak in the polls came on `r str_remove(format(pollbasepro$date[which.max(pollbasepro$con_est)], "%d %B %Y"), "^0")` when `r scales::percent(max(pollbasepro$con_est), accuracy = .1)` (95% CI: `r paste(scales::percent(max(pollbasepro$con_est) - qnorm(0.975)*pollbasepro$con_err[which.max(pollbasepro$con_est)], accuracy = 0.1), "to", scales::percent(max(pollbasepro$con_est) + qnorm(0.975)*pollbasepro$con_err[which.max(pollbasepro$con_est)], accuracy = 0.1))`) of the electorate intended to back them.
-
-These data and their summaries raise an interesting question: if Labour and the Conservatives have tended to be so well-matched in the polls, why have the Conservatives done so much better at election time?
-Despite leading in the polls `r str_remove(lead$Leader[2], " of days")` of the time, Labour has gained the highest share of the vote in only `r pbp_long %>% filter(err == 0) %>% add_elections() %>% group_by(last_elec) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% summarise(lab = length(winner[winner == "Labour Party"]), .groups = "drop") %>% pluck(1)` of the period's `r pbp_long %>% filter(err == 0) %>% add_elections() %>%  group_by(last_elec) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% nrow()` general elections (`r scales::percent((pbp_long %>% filter(err == 0) %>% add_elections() %>% group_by(last_elec) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% summarise(lab = length(winner[winner == "Labour Party"]), .groups = "drop") %>% pluck(1))/(pbp_long %>% filter(err == 0) %>% add_elections() %>% group_by(last_elec) %>% summarise(winner = party[which.max(est)], .groups = "drop") %>% nrow()))`).
-This phenomenon is not entirely unprecedented.
-@jackman1994 shows that the Australian Labor Party has suffered at elections due to pervasive electoral bias.
-Though this might also be the case in Britain, our figures reflect *vote* shares, not *seat* shares.
-As such, electoral bias should be a concern only insofar as it affects the parties' overall popularity.
-Other factors likely explain Labour's poor performance: Britain's press leans right and tends to support the Conservatives; successive Conservative governments could have scheduled elections to maximise their chances; partisan non-response could have led Conservative voters to drop out of polls in the period between elections; or, most simply, the Conservatives might just be better at campaigning.
-
 ```{r cor-plot, fig.cap = paste0("Historic correlations between each of Britain's three largest parties, ", format(min(pollbasepro$date), "%Y"), " to ", format(max(pollbasepro$date), "%Y")), fig.width = 6, fig.height = 2.5, fig.align = "centre", echo = F}
@@
 
+It is possible to propagate this error forward because PollBasePro includes *two* estimates for each party for each day that the data covers: estimates of public support for each party *and* an estimate of the standard error of this estimate.
+Table \@ref(tab:head-tab) shows the first 5 rows of the PollBasePro dataset.
+Variables ending "_est" show estimated voting intention and those ending "_err" their associated error.
+Notice that the error on the first date is zero.
+This is because this is the date of the 1955 general election, so we have absolute certainty what the result really was.
+As the days pass, this error gradually increases, reflecting our own epistemic uncertainty.
+These errors provide useful information in their own right, so it is prudent to also include them in our analysis.
+
+```{r head-table, echo = F}
+
+# Get table head
+
+pbp_head <- 
+  head(
+    pollbasepro,
+    n = 5
+    ) %>% 
+  mutate_if(
+    is.numeric,
+    function(x) round(x, 3)
+  )
+
+# Add latex code to variable names
+
+names(pbp_head) <- paste0("\\textsf{\\textbf{" ,names(pbp_head), "}}")
+names(pbp_head) <- str_replace(names(pbp_head), "_", "\\\\_")
+
+# Output table
+
+kable(
+  pbp_head,
+  align = "ccccccc",
+  format = "latex",
+  label = "head-tab",
+  booktabs = TRUE,
+  escape = FALSE,
+  caption = paste0("The first 5 rows of the PollBasePro dataset")
+  ) %>% 
+  kable_styling(position = "center")
+
+```
+
 According to the literature, there are good reasons why the relationship between the two variables might be positive and good reasons why it might be negative.
@@
 The literature on retrospective voting [@healy2013; @fiorina1981], instead, would favour a *negative* relationship.
-It holds that voters reward governments for positive policy outcomes and punish them for negative ones.
+It holds that voters reward governments for positive policy outcomes and punish them for negative ones (i.e.
+for avoidable deaths).
 
@@
 It is clear then that PollBasePro has allowed us to reveal an important---if surprising---answer to the question that we posed above: despite Britain having one of the world's highest levels of COVID-related deaths per capita [@ritchie2021], these untimely deaths appear to have *benefited* the fortunes of the governing Conservative Party.
-Still, the relationship has changed over time and, a year into the pandemic, has reversed direction.
+Yet this relationship has changed over time and, a year into the pandemic, has reversed direction.
 We might, thus, expect any further deaths attributable to COVID-19 to erode the Conservative's ample base of support.
-Yet given the pace of Britain's vaccination programme [@ukgovernment2021a], it is possible that the Conservatives have reaped the rewards without facing any punishment.
+Yet given the pace of Britain's vaccination programme [@ukgovernment2021a], it is possible that the Conservatives have reaped the electoral rewards of the crisis without risk of punishment.
 
@@
 Furthermore, our data are well validated and follow the course of British political history.
-We therefore expect PollBasePro to become a valuable resource for students of British politics in the years to come.
 
@@
 
+No matter how PollBasePro develops in the future, we are clear that it provides many opportunities in the present.
+We have discussed many of the academic opportunities that the data provide above.
+But our estimates might stand to improve the quality of polling reporting too.
+The stories that we tell ourselves to explain the polls often come to shape our politics [@barnfield2020].
+And many of these stories emerge from the simple averages that many commentators use to make sense of the polls.
+As we mention above, our estimates account for shortcomings that these simple rolling averages do not.
+PollBasePro might, therefore, stand to benefit not only academic researchers, but also the quality of political debate in Britain too.
+As such, we expect PollBasePro to become a valuable resource for students of British politics in the years to come.
+
 \pagebreak
@@
 ```
+
+\pagebreak
+
+# Appendix: Estimating Daily Voting Intention
+
+We adapt Jackman's [-@jackman2005] method to derive our daily estimates. Still, there are issues specific to our case that we must first overcome. We elaborate on our choices below.
+
+## Imputating Missing Sample Sizes
+
+Our data do not include sample sizes before the 2010 general election.
+This is a problem, as our model requires that we know this information.
+To solve this problem, we use data from Jennings and Wlezien's [-@jennings2016a] "Timeline of Elections" dataset.
+Though less comprehensive than PollBase, these data do include information on sample sizes.
+What's more, they also include data from countries other than Britain.
+This lets us pool all available information to improve our estimates.
+
+Sample sizes are count data. As such, we use the following multilevel Poisson regression model to impute likely sample sizes for all of our pre-2010 polling data:
+
+\begin{align*}
+n_{i} &\sim \mathrm{Poisson}(\lambda_{i}) \srlab{Likelihood function} \\
+log(\lambda_{i}) &= \alpha_{Country[i]} + \beta_{Country[i]} T_{i} \srlab{Linear model on $\lambda$} \\
+\begin{bmatrix} \alpha_{Country} \\ \beta_{Country} \end{bmatrix} &\sim \mathrm{MVNormal}(\begin{bmatrix} \alpha \\ \beta \end{bmatrix}, \textbf{S}) \srlab{Multivariate prior on varying effects} \\
+\textbf{S} &= \begin{pmatrix} \sigma_{\alpha} & 0 \\ 0 & \sigma_{\beta} \end{pmatrix} \textbf{R} \begin{pmatrix} \sigma_{\alpha} & 0 \\ 0 & \sigma_{\beta} \end{pmatrix} \srlab{Covariance matrix on varying effects} \\
+\alpha &\sim \mathrm{Normal}(7, 0.5) \srlab{Prior on average intercept, $\alpha$} \\
+\beta &\sim \mathrm{Normal}(0, 0.1) \srlab{Prior on average slope, $\beta$} \\
+\sigma_{\alpha} &\sim \mathrm{Exponential}(10) \srlab{Prior on uncertainty in the intercepts, $\sigma_{\alpha}$} \\
+\sigma_{\beta} &\sim \mathrm{Exponential}(10) \srlab{Prior on uncertainty in the slopes, $\sigma_{\beta}$} \\
+\textbf{R} &\sim \mathrm{LKJ}(2) \srlab{Prior on correlation matrix, $\textbf{\textrm{R}}$} \\
+\end{align*}
+
+```{r n-plot, fig.cap = paste0("Imputed sample sizes in Britain between ", format(min(samplesizes$date), "%Y"), " and ", format(max(samplesizes$date), "%Y"), ", estimated using sample size data from Jennings and Wlezien's \"Timeline of Elections\" dataset (2016)."), fig.width = 6, fig.height = 3, fig.align = "centre", echo = F}
+
+# Create sample size plot
+
+samplesizes %>%
+  ggplot(
+    aes(
+      x = date,
+      y = n_est,
+      ymin = qpois(0.025, n_est),
+      ymax = qpois(0.975, n_est)
+    )
+  ) +
+  geom_ribbon(alpha = .3, colour = NA) +
+  geom_line() +
+  scale_y_continuous(breaks = seq(0, 2500, by = 500)) +
+  scale_x_date(
+    breaks = seq.Date(as.Date("1945-01-01"), as.Date("2020-01-01"), by = "5 years"),
+    labels = year(seq.Date(as.Date("1945-01-01"), as.Date("2020-01-01"), by = "5 years"))
+    ) +
+  coord_cartesian(ylim = c(0, 2600)) +
+  theme_minimal() +
+    theme(legend.title = element_text(family = "Cabin", face = "bold", size = rel(1)),
+                   text = element_text(family = "Cabin", color = "black", size = 8),
+                   plot.title = element_text(family = "Cabin", face = "bold", size = rel(1.4), hjust = 0),
+                   plot.subtitle = element_text(family = "Cabin", size = rel(1), hjust = 0, margin = margin(b = 10)),
+                   axis.line = element_line(lineend = "round"),
+                   axis.title.x = element_blank(),
+                   axis.text.x = element_text(color = "black", size = rel(1)),
+                   axis.ticks.x = element_line(lineend = "round"),
+                   axis.title.y = element_text(family = "Cabin", face = "bold", size = rel(1)),
+                   axis.text.y = element_text(color = "black", size = rel(1)),
+                   strip.text = element_text(family = "Cabin", face = "bold", size = rel(1)),
+                   panel.spacing = unit(.3, "cm"),
+                   panel.grid.major.y = element_line(size = .5, lineend = "round"),
+                   panel.grid.minor.y = element_blank(),
+                   panel.grid.major.x = element_blank(),
+                   panel.grid.minor.x = element_blank()
+    ) +
+  labs(
+    y = "Imputed Sample Size"
+  )
+
+```
+
+We assume that the sample size associated with poll $i$ in the Timeline data, $n_{i}$, is distributed as Poisson according to some rate parameter, $\lambda_{i}$.
+We then model the logarithm of this parameter using a simple linear function that includes an intercept, $\alpha_{Country}$, and a slope on the effect of time, $\beta_{Country}$, which we allow to vary over countries.
+We then relate these two parameters to one another by modelling them as though they come from a multivariate normal distribution.
+In effect, this allows the parameters to be correlated and, thus, to share information.
+
+While our data concern Britain alone, we use all available data in the Timeline dataset.
+This is for good reason.
+The dataset does not contain reliable sample size values for British polls conducted before the early 1960s.
+But it does contain reliable values for other countries as early as the mid-1940s.
+Pooling all available information for all countries across the entire time series, thus, allows us to impute reliable estimates of likely sample sizes in Britain across the full range of dates by drawing on persistent differences between British polls and those from other countries.
+
+Figure \@ref(fig:n-plot) shows the model's best estimate of the likely sample size of the average British voting intention poll between `r year(min(samplesizes$date))` and `r year(max(samplesizes$date))`.
+These imputed values seem sensible and conform to our expection that sample sizes should increase over time.
+The model estimates that the average British voting intention poll included around `r format(round(samplesizes$n_est[samplesizes$date == min(samplesizes$date)], 0), big.mark = ",")` respondents in `r year(min(samplesizes$date))`.
+By `r year(max(samplesizes$date))`, the model suggests that this value had increased by `r format(round(samplesizes$n_est[samplesizes$date == max(samplesizes$date)] - samplesizes$n_est[samplesizes$date == min(samplesizes$date)], 0), big.mark = ",")` to `r format(round(samplesizes$n_est[samplesizes$date == max(samplesizes$date)], 0), big.mark = ",")` respondents per poll on average.
+
+We use the model to produce a time series of estimates sample sizes between `r year(min(samplesizes$date))` and `r year(max(samplesizes$date))`.
+This includes all dates for which we intend to produce a voting intention estimate.
+Where our polling data come from before the 2010 general election, or are otherwise missing, will fill in the gaps with these imputed values.
+To do so we match our polling data to the imputed values from the model based on their respective dates.
+
+## Estimating Daily Voting Intention Figures
+
+As we mention above and in the accompanying paper, we adapt the model in @jackman2005 to compute our daily British voting intention estimates.
+The model is complex and has many moving parts, so we will build it up step by step.
+
+We assume that each poll in our underlying data, $Poll_{i}$, is generated from some normal distribution.
+This distribution has two parameters.
+The first is some mean, $\mu_{i}$.
+The second is some error that leads the estimates to be higher or lower than the expected value, $\mu_{i}$.
+In many models with a normal likelihood function, this error parameter would measure only random residual error and be represented by the Greek letter $\sigma$.
+But, in our case, we have additional information that we can use.
+We know that each poll is a proportion and represents a draw from some random distribution.
+Thus, we can use the equation for the standard error of a proportion to calculate the uncertainty in each estimate, where $S_{i} = \sqrt{\frac{Poll_{i} (1 - Poll_{i})}{\nu_{i}}}$.
+Note that $\nu_{i}$ is the sample size of $Poll_{i}$, $n_{i}$, divided by the number of days the poll spent in the field, $k_{i}$.
+In effect, this implies that we assume an equal number of people were polled on each day that the model was in the field.
+We can then include both in our model to account for any known error, $S_{i}$, and any random residual error, $\sigma$.
+So far, our model is as follows:
+
+\begin{align*}
+Poll_{i} &\sim \mathrm{Normal}(\mu_{i}, \sqrt{\sigma^2 + S_{i}^2}) \srlab{Likelihood function} \\
+\end{align*}
+
+The next step is to fit a model to $\mu_{i}$.
+This will be a measurement model, as it will allow us to produce an estimate of the electorate's *latent* voting intention on each day.
+We assume that $\mu_{i}$ is a linear function of two variables: $\alpha_{Day[i]}$, the electorate's latent voting intention for $Poll_{i}$ on the day that it was fielded, and $\delta_{Pollster[i]}$, the persistent "house effects" that arise due to the methodological and design choices that inform how the company that ran the poll collected its data.
+If we update our model specification to include these assumptions, we get the following:
+
+\begin{align*}
+Poll_{i} &\sim \mathrm{Normal}(\mu_{i}, \sqrt{\sigma^2 + S_{i}^2}) \srlab{Likelihood function} \\
+\mu_{i} &= \alpha_{Day[i]} + \delta_{Pollster[i]} \srlab{Measurement model on $\mu$} \\
+\end{align*}
+
+At present, all values of $\alpha_{Day}$ are independent.
+This is a problem.
+First, we want estimates closer together to be more similar.
+Second, some days have no polling data to inform them.
+To address this problem, we constrain $\alpha_{1}$ to be equal to the vote share that a given party received at a given election.
+We also constrain $\alpha_{T}$ to be equal to the vote share that the same party received at the following election.
+Next, we fit a dynamic model to $\alpha_{t}$ for all days in our time series except for the first and last.
+This acts as a sort of "chain" that links together all values of $\alpha$.
+Because these values are now linked, they can then share information amongst themselves.
+This means that when the value of one estimate changes during the model estimation process, so too do the values of all others.
+The model assumes that $\alpha_{t}$ is equal to $\alpha_{t-1}$, plus any random shocks that take place between the two days, $\omega_{t-1}$.
+These random shock parameters are themselves scaled according to $\tau$, the scale of innovations parameter.
+Updating our model specification again, we get:
+
+\begin{align*}
+Poll_{i} &\sim \mathrm{Normal}(\mu_{i}, \sqrt{\sigma^2 + S_{i}^2}) \srlab{Likelihood function} \\
+\mu_{i} &= \alpha_{Day[i]} + \delta_{Pollster[i]} \srlab{Measurement model on $\mu$} \\
+\alpha_{t} &= \alpha_{t-1} + \tau \omega_{t-1} \text{ for } t \text{ in } 2, ..., T-1 \srlab{Dynamic model on $\alpha_{t}$} \\
+\end{align*}
+
+As we rely on Bayesian methods, our final step in building the model is to provide a set of conservative and weakly-informative prior distributions^[In this case our priors serve only to regularise our parameter estimates.
+For example, our prior on the pollster house effects allows for a large---indeed, improbable---10 point house effect.
+They are unlikely, therefore, to constrain our estimates in such a way as to affect our inferences.].
+
+\begin{align*}
+Poll_{i} &\sim \mathrm{Normal}(\mu_{i}, \sqrt{\sigma^2 + S_{i}^2}) \srlab{Likelihood function} \\
+\mu_{i} &= \alpha_{Day[i]} + \delta_{Pollster[i]} \srlab{Measurement model on $\mu$} \\
+\alpha_{t} &= \alpha_{t-1} + \tau \omega_{t-1} \text{ for } t \text{ in } 2, ..., T-1 \srlab{Dynamic model on $\alpha_{t}$} \\
+\alpha_{T} &\sim \mathrm{Normal}(\alpha_{T-1}, \tau) \srlab{Adaptive prior on $\alpha_{T}$} \\
+\delta_{j} &\sim \mathrm{Normal}(0, 0.05) \text{ for } j \text{ in } 1, ..., J \srlab{Prior on house effects, $\delta$} \\
+\omega_{t} &\sim \mathrm{Normal}(0, 0.025) \text{ for } t \text{ in } 1, ..., T-1 \srlab{Prior on random shocks, $\omega$} \\
+\tau &\sim \mathrm{Normal}(0, 0.05)^{+} \srlab{Positive prior on scale of innovations, $\tau$} \\
+\sigma &\sim \mathrm{Exponential}(20) \srlab{Prior on residual error, $\sigma$} \\
+\end{align*}
+
+After specifying our model, we loop over our data and fit the model to each election pair for each party.
+As we know with almost absolute certainty what the electorate's voting intention was on election days, we use this to our advantage and constrain $\alpha_{1}$ to equal a given party's vote share at the first election and $\alpha_{T}$ to equal the same party's vote share at the following election.
+We do this for every election pair between 1955 and the present for each party.
+Note that the most recent election by definition has no subsequent election.
+In this case, we leave $\alpha_{T}$ unconstrained and estimate its value from the data.

### 2021-04-16 documentation/paper.Rmd
Recompiled pollbasepro

@@
   |
-  | \textbf{\textsf{Keywords:}} Opinion polls; public opinion; British politics; Bayesian methods.
+  | \textbf{\textsf{Keywords:}} Opinion polls; public opinion; British politics; Coronavirus; COVID-19; Bayesian methods.
 indent: yes
@@
 Consider the effect of rising Liberal support on the Conservatives and Labour.
-The correlation between the Liberals and the Conservatives is `r britpol:::in_text(cor_mods$lib_con*100, suffix = "%", inside = F)` and between the Liberals and Labour `r britpol:::in_text(cor_mods$lib_lab*100, suffix = "%", inside = F)`.
+The correlation between the Liberals and the Conservatives is strong at `r britpol:::in_text(cor_mods$lib_con*100, suffix = "%", inside = F)` and between the Liberals and Labour `r britpol:::in_text(cor_mods$lib_lab*100, suffix = "%", inside = F)`.
 Contrary to popular arguments that the Liberals serve to split the centre-left vote [e.g.
 @jenkins2019], our figures suggest that rising Liberal support has tended to hurt the Conservatives more than Labour.
-Interestingly, the correlation between Labour and the Conservatives is also the smallest, at `r britpol:::in_text(cor_mods$con_lab*100, suffix = "%", inside = F)`.
-This is perhaps unsurprising, given that the two parties represent different sides of the left-right spectrum.
-Even so, that both parties have tended to target the other's vote still makes strategic sense: each party's pool of potential voters is almost always larger than the pool of potential Liberal voters.
+The correlation between Labour and the Conservatives is also sizeable, at `r britpol:::in_text(cor_mods$con_lab*100, suffix = "%", inside = F)`.
+Given that they are Britain's two main parties, this is perhaps unsurprising: Labour and the Conservatives are the only parties likely to form a government after any election and punishing one often requires voting for the other.
 
@@
 These random shock parameters are themselves scaled according to $\tau$, the scale of innovations parameter.
-Updating our model specification again, we get:
+Updating the model again, we get:
 

### 2021-04-16 R/global.R

@@ -47,6 +47,9 @@ utils::globalVariables(
     "nat",
     "oth",
     "region",
-    "total"
+    "total",
+    "lib_err",
+    "lib_est",
+    "n_est"
     )
 )

### 2021-04-16 R/polling_multiverse.R

@@ -7,23 +7,6 @@
 #' @return A tibble of polling data.
 #' @examples
 #' pollingverse <- polling_multiverse(start = "2017-06-18", end = "2019-12-12")
-#' # Plot the result
-#' pollingverse_long <- pivot_longer(pollingverse,
-#'                                  cols = c(con, lab, lib),
-#'                                  names_to = "party",
-#'                                  values_to = "share")
-#' ggplot2::ggplot(data = pollingverse_long, mapping = aes(x = date, y = share, colour = party)) +
-#'   geom_point() +
-#'   geom_smooth() +
-#'   scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
-#'   # override party colours
-#'   scale_colour_manual(values = c("con" = britpol::party_colours("con"),
-#'                                  "lab" = britpol::party_colours("lab"),
-#'                                  "lib" = britpol::party_colours("lib"))) +
-#'   # cosmetic changes
-#'   theme(legend.position = "none") +
-#'   labs(x = "",
-#'        y = "")
 #' @export
 
 polling_multiverse <- function(start = NULL, end = NULL){
@@ -34,11 +17,13 @@ polling_multiverse <- function(start = NULL, end = NULL){
     stop("Please provide a valid date range of the form YYYY-MM-DD using the start and end arguments.")
   }
 
+
   # Warning if dates seem implausible or suggest YMD mixed up
   if(as.Date(start) < as.Date("0032-01-01") ||
      as.Date(end) < as.Date("0032-01-01")){
     warning("Make sure you specified your start and end dates in YYYY-MM-DD format.")
   }
+
 
   # Error if end date before start date
   if(as.Date(end) < as.Date(start)){
@@ -51,8 +36,6 @@ polling_multiverse <- function(start = NULL, end = NULL){
      as.Date(start) > max(britpol::pollbasepro$date)){
     stop("The date range you have specified is outside of the range covered by available polling data.")
   }
-
-
 
 
   # Convert start and end to dates
@@ -116,7 +99,7 @@ polling_multiverse <- function(start = NULL, end = NULL){
       britpol::pollbasepro,
       "date"
     ) %>%
-    na.omit()
+    stats::na.omit()
 
 
   # Sample each row once from a binomial distribution
[…]

### 2021-04-16 R/utils.R

@@ -1233,7 +1233,7 @@ update_pollbasepro <- function(){
 
   # Use hotdeck imputation to fill in missing sample sizes
 
-  wiki$n[is.na(wiki$n) == T] <- round(median(wiki$n, na.rm = T), 0)
+  wiki$n[is.na(wiki$n) == T] <- round(stats::median(wiki$n, na.rm = T), 0)
 
 
   # Fit model

### 2021-04-16 data-raw/005_validation.R

@@ -81,12 +81,14 @@ cor_con <-
       bf(vote ~ 1) +
       bf(con_est | se(con_err, sigma = TRUE) ~ 1) +
       set_rescor(rescor = TRUE),
+    family = student(),
     prior =
       prior(normal(0.4, 0.07), class = "Intercept", resp = "vote") +
       prior(exponential(5), class = "sigma", resp = "vote") +
       prior(normal(0.4, 0.07), class = "Intercept", resp = "conest") +
       prior(exponential(5), class = "sigma", resp = "conest") +
-      prior(lkj(2), class = "rescor"),
+      prior(lkj(2), class = "rescor") +
+      prior(gamma(2, .1), class = "nu"),
     data = con,
     backend = "cmdstanr",
     seed = 666,
@@ -101,12 +103,14 @@ cor_lab <-
       bf(vote ~ 1) +
       bf(lab_est | se(lab_err, sigma = TRUE) ~ 1) +
       set_rescor(rescor = TRUE),
+    family = student(),
     prior =
       prior(normal(0.4, 0.07), class = "Intercept", resp = "vote") +
       prior(exponential(5), class = "sigma", resp = "vote") +
       prior(normal(0.4, 0.07), class = "Intercept", resp = "labest") +
       prior(exponential(5), class = "sigma", resp = "labest") +
-      prior(lkj(2), class = "rescor"),
+      prior(lkj(2), class = "rescor") +
+      prior(gamma(2, .1), class = "nu"),
     data = lab,
     backend = "cmdstanr",
     seed = 666,
@@ -121,12 +125,14 @@ cor_lib <-
       bf(vote ~ 1) +
       bf(lib_est | se(lib_err, sigma = TRUE) ~ 1) +
       set_rescor(rescor = TRUE),
+    family = student(),
     prior =
       prior(normal(0.15, 0.06), class = "Intercept", resp = "vote") +
       prior(exponential(5), class = "sigma", resp = "vote") +
       prior(normal(0.15, 0.06), class = "Intercept", resp = "libest") +
       prior(exponential(5), class = "sigma", resp = "libest") +
-      prior(lkj(2), class = "rescor"),
+      prior(lkj(2), class = "rescor") +
+      prior(gamma(2, .1), class = "nu"),
     data = lib,
     backend = "cmdstanr",
     seed = 666,
@@ -147,6 +153,7 @@ cor_all <-
       bf(con_est | se(con_err, sigma = TRUE) ~ 1) +
[…]

### 2021-05-03 documentation/paper.Rmd
Added Mark's suggested revision on data

@@
 
-The PollBase data come from a range of sources.
+The PollBase data come from a wide range of sources.
 This includes books published after each general election, polling almanacs, data shared amongst academics and pollsters, contemporary media reports, and figures from polling company websites.
-The data since the 1983 general election are complete, baring any individual errors.
-Likewise, data are complete for every general election campaign before 1979.
-The coverage between elections is more comprehensive for some pollsters than others^[We encourage any readers who might know of polls missing from the PollBase dataset to contact its author via his website (https://www.markpack.org.uk)].
+The data since the 1983 general election are complete, baring possible but rare individual errors.
+Prior to 1983, the data is likewise complete for each general election campaign period.
+For periods between general elections prior to 1983, coverage is more comprehensive for some pollsters than others^[We encourage any readers who might know of polls missing from the PollBase dataset to contact its author via his website (https://www.markpack.org.uk)].
 Gallup and NOP data, in particular, are well-covered as the two companies have collated and published their results.
-The PollBase data start on `r format(min(pollbase$start), "%d %B %Y")`.
-Yet, consistent polling began only after the 1955 general election.
-Thus, we take it as our starting point.
+The PollBase data start in `r format(min(pollbase$start), "%B %Y")`.
+However, we take as our starting point the 1955 Parliament given the gaps in the earlier data.
 
@@
   escape = FALSE,
+  linesep = "",
   caption = paste0("The first 5 rows of the PollBasePro dataset")

### 2021-06-22 documentation/paper.Rmd
Fix add_pm and add_pm_party functions, recompile mini data and recompile paper

@@
 
-# Get conditional effects
-
 cond_fx <- 
@@
       tibble(
-        time = seq(2, 14, by = 6),
-        cond__ = c("Mar. 2020", "Sep. 2020", "Mar. 2021")
+        time = round(seq(3, 18, length.out = 3), 0),
+        cond__ = 
+          as_date("2019-12-12") %m+%
+          months(time) %>% 
+          format("%b. %Y")
       )
@@
   theme_bailey()
+
 ```
